\documentclass[../../../main.tex]{subfiles}
\begin{document}
\subsection{First Postulate}
As the following
\begin{quotation}
    The state of the particle is represented by a vector $\ket{\psi(t)}$ in a Hilbert space.
\end{quotation}
Compare it with the classical mechanics postulate via Hamiltonian formalism
\begin{quotation}
    The state of a particle at any given time is specified by the two variables $x(t)$ and $p(t)$, i.e., as a point in a two-dimensional phase space.
\end{quotation}

\subsubsection{Discussion: general discussion.}
The first three tell us how the system is depicted at a given time, and the fourth specifies how this picture changes with time.
The first postulate states that a particle is described by a ket $\ket{\psi} $ in a Hilbert space which, you will recall, contains proper vectors normalizable to unity as well as improper vectors, normalizable only to the Dirac delta functions.

Now, a ket in a Hilbert space has in general an infinite number of components in a given basis.
A classical particle has, at any given time, a definite position.
One simply has to give this value of $x$ in specifying the state.
A quantum particle, on the other hand, can take on any value of $x$ upon measurement and one must give the relative probabilities for all possible outcomes.

\subsection{Second Postulate}
As the following
\begin{quotation}
    The independent variables $x$ and $p$ of classical mechanics are represented by Hermitian operators $X$ and $P$ with the following matrix elements in the eigenbasis of $X$
    \begin{align*}
        \braket{x|X|x'} & =x\delta(x-x')         \\
        \braket{x|P|x'} & =-i\hbar \delta'(x-x')
    \end{align*}

    The operators corresponding to dependent variables $\omega=\omega(x,p)$ are given Hermitian operators
    \begin{equation*}
        \Omega(X,P)=\omega \left( x\rightarrow X, p\rightarrow P \right)
    \end{equation*}
    where it is understood that $\Omega$ is a function of $X$ and $P$ just like $\omega$ is a function of $x$ and $p$.
\end{quotation}
Compare it with the classical mechanics postulate via Hamiltonian formalism
\begin{quotation}
    Every dynamical variable $\omega$ is a function of $x$ and $p$, that is $\omega=\omega(x,p)$.
\end{quotation}

\subsubsection{Discussion: ambiguity of operator.}
The definition $        \Omega(X,P)=\omega \left( x\rightarrow X, p\rightarrow P \right) $ is ambiguous.
Suppose $\omega=xp$.
We do not know $\Omega=PX$ or $\Omega=XP$ since $px=xp$ classically.
The rule is to use symmetric sum
\begin{equation*}
    \Omega=\frac{XP+PX }{2}
\end{equation*}
which also render $\Omega$ Hermitian.

\subsubsection{Discussion: continuous spectrum of operator.}
In the case of continuous eigenvalues of $\Omega$, ket $\ket{\psi}$ expands as
\begin{equation*}
    \ket{\psi}=\int \ket{\omega}\braket{\omega|\psi}\;d\omega=\int \ket{\omega}\psi(\omega)\;d\omega
\end{equation*}
Since $\omega$ varies continuously, so will $\braket{\omega|\psi}=\psi(\omega)$, which imply that $\psi(\omega)$ is a smooth function.

$P(\omega)$ in this case refer to the probability density, in particular $P(\omega)\;d\omega$ is the probability of obtaining $\omega$ between $\omega$ and $\omega+d\omega$.
This definition must meet the unity definition
\begin{equation*}
    \int P(\omega)\;d\omega=\int \braket{\psi|\omega}\braket{\omega|\psi}\;d\omega=\braket{\psi|I|\psi}=1
\end{equation*}

\subsection{Third Postulate}
As the following
\begin{quotation}
    If the particle is in a state $\ket{\psi}$, measurement of the variable corresponding to $\Omega$ will yield one of the eigenvalues $\omega$ with probability $P(\omega)\propto |\braket{\omega|\psi}|^2$. The state of the system will change from $\ket{\psi}$ to $\ket{\omega}$ as a result of the measurement.
\end{quotation}
Compare it with the classical mechanics postulate via Hamiltonian formalism
\begin{quotation}
    If the particle is in a state given by $x$ and $p$, the measurement of the variable $\omega$ will yield a value $\omega(x,p)$. The state will remain unaffected.
\end{quotation}

\subsubsection{Discussion: probability.}
The theory makes only probabilistic predictions for the result of a measurement of $\Omega$, which only have the possible values of its eigenvalues, which also all real by the postulate.
The postulate also state the relative probabilities, to get the absolute probability, we divide by the sum of all relative probabilities
\begin{equation*}
    P(\omega_i)=\frac{|\braket{\omega_i|\psi}|^2 }{\sum_j \braket{\omega_j | \psi}^2}=\frac{|\braket{\omega_i|\psi}|^2}{\braket{\psi|\psi}}
\end{equation*}
As a side note, the probability interpretation breaks down if $\ket{\psi}$ is an improper vector.

Suppose there exist state described by
\begin{equation*}
    \ket{\psi}=\frac{\alpha \ket{\omega_1 }+\ket{\omega_2}}{\left( |\alpha|^2+|\beta|^2 \right)^{1/2} }
\end{equation*}
Measurement can either yield $\omega_1$ or $\omega_2$ with the probabilities $|\alpha^2|/(\alpha^2+\beta^2)$ and $|\beta^2|/(\alpha^2+\beta^2)$ respectively.

\subsubsection{Discussion: probability for degenerate operator.}
Say that we have degenerate operator $\Omega$ with degenerate eigenvalues $\omega_1=\omega_2=\omega$ with orthonormal basis $\ket{\omega,1}$ and $\ket{\omega,2}$.
Then the probability is
\begin{equation*}
    P(\omega)=|\braket{\omega,1|\psi}|^2+|\braket{\omega,2|\psi}|^2
\end{equation*}
In terms of projection operator in this eigenspace
\begin{equation*}
    \mathbb{P }_\omega=\ket{\omega,1}\bra{\omega,1}+\ket{\omega,2}\bra{\omega,2}
\end{equation*}
we have
\begin{equation*}
    P(\omega)=\braket{\psi|\mathbb{P}_\omega|\psi}=\braket{\mathbb{P}_\omega \psi|\mathbb{P}_\omega \psi}
\end{equation*}

\subsubsection{Discussion: change of basis.}
Suppose our interest switch to measuring $\Lambda$ from the measurement of $\Omega$--note that this does not mean a successive measurement.
Recall that to obtain the probability of $\omega$, we need to project $\ket{\psi}$ in the $\Omega$ basis.
To obtain the probability of $\lambda$, then, we can do the same; but there is no need to expand $\ket{\psi}$ in $\Lambda$ given we already expanded $\ket{\psi}$ in $\Omega$ basis.
Working in $\Omega$ basis, we have
\begin{equation*}
    \ket{\psi }=\sum_i \ket{\omega_i } \braket{\omega_i |\psi}\qquad\text{and}\quad P(\omega_i)=|\braket{\omega_i|\psi}|^2
\end{equation*}
If we wanted the probability of $\lambda$, we can simply project $\ket{\psi}$ in the eigenvectors $\ket{\lambda}$
\begin{equation*}
    \braket{\lambda_i|\psi}=\sum_j \braket{\lambda_i|\omega_j}\braket{\omega_j|\psi}
\end{equation*}


\subsection{Fourth Postulate: Schrödinger equation}
As the following
\begin{quotation}
    The state vector $\ket{\psi}$ obeys the Schrödinger equation
    \begin{equation*}
        i\hbar \frac{d }{dt }\ket{\psi(t )}= H \ket{\psi(t)}
    \end{equation*}
    where $H(X,P)=\mathcal{H }(x\rightarrow X, p\rightarrow P  )$ is the quantum Hamiltonian operator and $\mathcal{H }$ is the Hamiltonian for the corresponding classical problem
\end{quotation}
Compare it with the classical mechanics postulate via Hamiltonian formalism
\begin{quotation}
    The state variables change with time according to Hamilton's equations
    \begin{equation*}
        \dot{x}=\frac{\partial \mathcal{H }}{\partial p}\qquad \dot{p }=-\frac{\partial \mathcal{H }}{\partial x}
    \end{equation*}
\end{quotation}

\subsubsection{Discussion: The propagator equation.}
Let us first assume that $H$ has no explicit $t$ dependence. In this case
\begin{equation*}
    i \hbar \ket{\dot{\psi}(t)}=H \ket{\psi(t)}
\end{equation*}
On using the propagator, the time evolution of the solution is written as
\begin{equation*}
    \ket{\psi(t)}=U(t)\ket{\psi(0)}
\end{equation*}

Since the energy operator $H$ is Hermitian
\begin{equation*}
    H=H ^\dagger
\end{equation*}
it follows that the propagator $U(t)=\exp(-i Ht/\hbar)$ is unitary.
\begin{equation*}
    U ^\dagger(t)=\left[\exp(-i Ht/\hbar)\right]^\dagger=\exp(-i H ^\dagger t/\hbar)=\exp(-i Ht/\hbar)
\end{equation*}
One consequence is the norm of state vector is invariant
\begin{equation*}
    \braket{\psi(t)|\psi(t)}=\braket{\psi(0)|U ^\dagger(t)U(t)|\psi(0)}=\braket{\psi(0)|\psi(0)}
\end{equation*}
This meant that once normalized, state stays normalized.

\subsubsection{Discussion: The propagator expression.}
The propagator for time independent Hamiltonian can be constructed as
\begin{equation*}
    U(t)=\sum_E \ket{E } \bra{E }e^{-iEt/\hbar}=\int \ket{E} \bra{E}e^{-iEt/\hbar}\;dE
\end{equation*}
Another expression is
\begin{equation*}
    U(t)=e^{-iHt/\hbar}
\end{equation*}

The expression is derived as follows.
First consider the time independent Schrödinger equation that describe the action of Hamilton operator on energy eigenstate
\begin{equation*}
    H \ket{E}=E \ket{E}
\end{equation*}
We can expand the state in this basis
\begin{equation*}
    \ket{\psi(t)}=\sum \ket{E }\braket{E|\psi(t)}=\sum a_E(t)\ket{E}
\end{equation*}
Operate both $\ket{\psi(t)}$ with $i \hbar d/dt-H$ to obtain the Schrödinger equation and more
\begin{align*}
    \left( i \hbar \frac{\partial }{\partial t }-H  \right) \ket{\psi(t)} & = i \hbar \ket{\dot{\psi}(t)}-H \ket{\psi(y)}          \\
                                                                          & = i \hbar \sum \dot{a}_E \ket{E }- H\sum a_E \ket{E }  \\
                                                                          & = i \hbar \sum \dot{a}_E \ket{E }- \sum a_E E\ket{E }  \\
    0                                                                     & = \sum \left( i \hbar \dot{a }_E-a_EE  \right) \ket{E}
\end{align*}
which imply
\begin{equation*}
    i \hbar \dot{a }_E=a_EE
\end{equation*}
A simple differential equation
\begin{align*}
    \frac{d a_E }{dt } & = i \frac{E }{\hbar }a_E \\
    \ln a_E            & = -i \frac{E }{\hbar }+C \\
    a_E(t)             & = C e^{-i E t/\hbar}
\end{align*}
with $a_E(0)=0$, this makes
\begin{equation*}
    a_E(t)= a_E(0)e^{-i E t/\hbar}
\end{equation*}

With the expression for $a_E(t)$, we can now expand
\begin{equation*}
    \ket{\psi(t)}=\sum a_E(0)e^{-i E t/\hbar}\ket{E}
\end{equation*}
Now we project it onto $\bra{E }$ at $t=t$ and $t=0$
\begin{align*}
    \braket{E|\psi(t)} & = \bra{E }\sum a_E(0)e^{-i E t/\hbar}\ket{E}=a_E(0)e^{-i Et/\hbar} \\
    \braket{E|\psi(0)} & = \bra{E }\sum a_E(0)\ket{E}=a_E(0)
\end{align*}
or
\begin{equation*}
    \braket{E|\psi(t)}=a_E(0)e^{-i Et/\hbar}=\braket{E|\psi(t)}e^{-iEt/\hbar}
\end{equation*}
Thus
\begin{equation*}
    \ket{\psi(t)}=\ket{\psi(0)}e^{-iEt/\hbar}
\end{equation*}
On comparing this with the propagator equation
\begin{equation*}
    \ket{\psi(t)}=U(t)\ket{\psi(0)}
\end{equation*}
We can be written the propagator as
\begin{equation*}
    U(t)=\sum_E \ket{E }\bra{E }e^{-iE/\hbar}=e^{-iEt/\hbar}
\end{equation*}

\subsubsection{Discussion: Basis.}
Barring a few exceptions, the Schrödinger equation is always solved in a particular basis.
Since $H=H(X,P)$, the $x$ and $p$ basis is recommended.
In the $x$ basis, the operators takes the form
\begin{equation*}
    X \rightarrow x \quad P \rightarrow -i \hbar \frac{d }{dx}
\end{equation*}
while in $P$ basis
\begin{equation*}
    X \rightarrow i \hbar \frac{d }{dp}\quad P \rightarrow p
\end{equation*}

For example, consider the Hamiltonian in the form
\begin{equation*}
    H=T+V=\frac{P^2 }{2m }+\frac{1 }{\cosh^2 X}
\end{equation*}
where the $V(X)$ understood as more complicated than $T$.
In the $X$ basis the time independent Schrödinger equation takes the form
\begin{equation*}
    \left( -\frac{\hbar^2 }{2m }\frac{d^2 }{dx^2 }+\frac{1 }{\cosh^2 x} \right) \psi_E(x)=E\psi_E(x)
\end{equation*}
Had we gone to $P$ basis, we obtain the much more complicated equation
\begin{equation*}
    \left( \frac{p^2 }{2m }+\frac{1 }{\cosh^2 (i \hbar d/dp)} \right) \psi_E(p)=E\psi_E(p)
\end{equation*}

On the other hand, consider the Hamiltonian of a particle in the constant force field $f$
\begin{equation*}
    H=\frac{P^2 }{2m }-fX
\end{equation*}
In the $X$ basis, the Schrödinger equation takes the much more complicated form
\begin{equation*}
    \left( -\frac{\hbar^2}{2m }\frac{d^2 }{dx^2}-fx \right)\psi_E(x)=E\psi_E(x)
\end{equation*}
While in the $P$ basis it takes the form of first order differential equation
\begin{equation*}
    \left( \frac{p^2 }{2m }-i \hbar f \frac{d }{dp }     \right)\psi_E (p)=E\psi_E(p)
\end{equation*}

\subsection{Measurement}
Given state $(x,p)$, we can say that dynamical value has the value $\omega(x,p)$ in classical mechanics.
In quantum mechanics, when a particle is in a state $\ket{\psi } $ the particle can have the value of $\omega$ for the quantum operator $\Omega$ with probability $P(\omega)\propto|\braket{\omega|\psi}  |^2$.
This value is obtained by the following method.
\begin{enumerate}
    \item Construct the corresponding quantum operator $\Omega=\omega(x \rightarrow ,p \rightarrow P)$ where $X$ and $P$ are the operators defined in postulate II.
    \item Find the orthonormal eigenvectors $\ket{\omega} $ and eigenvalues $\omega_i$ of $\Omega$.
    \item Expand $\ket{\psi } $ in this basis
          \begin{equation*}
              \ket{\psi }=\sum_i  \ket{\omega_i } \braket{\omega_i |\psi}
          \end{equation*}
    \item The probability $P(\omega_i)$ that the result $\omega_i$ will be obtained is $P(\omega)\propto|\braket{\omega|\psi}  |^2$, or in terms of projection vector
          \begin{equation*}
              P(\omega)\propto \braket{\psi|\omega } \braket{\omega|\psi}=\braket{\psi|\mathbb{P}_\omega|\psi  }=\braket{\psi|\mathbb{P } _\omega \mathbb{P } _\omega |\psi   }=\braket{\mathbb{P } _\omega \psi| \mathbb{P } _\omega \psi  }
          \end{equation*}
\end{enumerate}

This method can be expressed in density matrix formalism as follows.
\begin{enumerate}
    \item Let the observable $\Omega$ be a self-adjoint operator with spectral decomposition $\Omega = \sum_i \omega_i \, \mathbb{P}_i$, where $\mathbb{P}_i = \ket{\omega_i}\bra{\omega_i}$ are orthogonal projection operators, satisfying $\mathbb{P}_i \mathbb{P}_j = \delta_{ij}\mathbb{P}_i,$ and $\sum_i \mathbb{P}_i = I$.
    \item Prepare the mixed state written as an ensemble of pure state
          \begin{equation*}
              \rho = \sum_k p_k \ket{\psi_k}\bra{\psi_k},
              \qquad \sum_k p_k = 1,
          \end{equation*}
    \item The probability of obtaining the outcome $\omega_i$ is
          \begin{equation*}
              P(\omega_i) = \mathrm{Tr}(\rho\,\mathbb{P}_i)
              = \sum_k p_k \, |\braket{\omega_i|\psi_k}|^2
          \end{equation*}
          For a pure state $\rho = \ket{\psi}\bra{\psi}$, this obviously reduces to
          \begin{equation*}
              P(\omega_i)
              = \mathrm{Tr}(\ket{\psi}\bra{\psi}\mathbb{P}_i)
              = \bra{\psi}\mathbb{P}_i\ket{\psi}
              = |\braket{\omega_i|\psi}|^2
          \end{equation*}
\end{enumerate}

\subsubsection{Collapse.}
Measurement by the operator $\Omega$ changes the state vector $\ket{\psi}$, which on this basis expands as
\begin{equation*}
    \ket{\psi}=\sum_\omega \ket{\omega}\braket{\omega|\psi}
\end{equation*}
into the eigenstate $\ket{\omega}$ corresponding to the eigenvalue of $\omega$  obtained in measurement.

The effect of the measurement, then, can be represented as
\begin{equation*}
    \ket{\psi}\xrightarrow{\Omega\text{ measured, }\omega\text{ obtained}}\frac{\mathbb{P}_\omega \ket{\psi }}{\braket{\mathbb{P}_\omega\psi|\mathbb{P }_\omega \psi}^{1/2}}
\end{equation*}
with $\mathbb{P }_\omega$ as the projection operator to $\ket{\omega}$.
If the eigenvalues $\omega$ is degenerate, the $\mathbb{P }_\omega$ is the projection operator for the eigenspace $\mathbb{V}_\omega$.
The same can be said for the density matrix formalism
\begin{equation*}
    \rho  \xrightarrow{\omega_i\text{ obtained}}\rho_i
    = \frac{\mathbb{P}_i \rho \mathbb{P}_i}{\operatorname{Tr}(\rho\,\mathbb{P}_i)}
\end{equation*}
where $\mathbb{P}_i = \ket{\omega_i}\bra{\omega_i}$.


\subsubsection{Testing quantum theory.}
Unlike classical mechanics, quantum mechanics does not make deterministic predictions but statistical predictions.
To test the predictions of the quantum mechanics, we must be able to create well-defined state $\ket{\psi}$ and check the probabilistic predictions at any time.
The procedure are as follows.
\begin{enumerate}
    \item Begin with particle in an arbitrary state $\ket{\psi}$ and measure a variable $\Omega$.
    \item If we get nondegenerate value $\omega$, we have the state $\ket{\omega}$.
    \item We immediately thereafter measure variable $\Lambda$ next so that the state could not change form $\ket{\omega}$.
          If say the theory state
          \begin{equation*}
              \ket{\omega}=\alpha \ket{\lambda_1}+\beta \ket{\lambda_2}
          \end{equation*}
          then the theory predict that $\lambda_1$ and $\lambda_2$ will be obtained with probability $\alpha^2$ and $\beta^2$ respectively.
\end{enumerate}
If the measurement give any other eigenvalue $\lambda_i$ or other noneigenvalue value, that is the end of the theory.
Suppose the resulting measurement give the correct eigenvalue, we can repeat the measurement with quantum ensemble of $N$ particles all in this same state $\ket{\omega}$.
The measurement should match with the predictions $N/\alpha^2$ particle in $\ket{\lambda_1}$ and $N/\beta^2$ in $\ket{\lambda_2}$.

\subsection{Information Inside Abstract State}
\subsubsection{Probabilities.}
The probability for obtaining $\omega$ for variable $\Omega$ is
\begin{equation*}
    P(\omega)=|\braket{\omega|\psi}|^2
\end{equation*}
or continuous eigenvalues, the probability $\omega$ between $a$ and $b$.
\begin{equation*}
    P(a,b)=\int_{a }^{b }|\braket{\omega|\psi}|^2\;d\omega
\end{equation*}

\subsubsection{Expectation value.}
The expectation value is the mean value defined in statistics
\begin{equation*}
    \braket{\Omega}=\sum_i P(\omega_i)\omega_i=\braket{\psi|\Omega|\psi}
\end{equation*}
If the particle is an eigenstate of $\Omega$, that is $\Omega \ket{\psi}=\omega \ket{\psi}$, the $\braket{\Omega}=\omega$.

To see how the third term comes to be, we can expand the statistical definition as follows.
\begin{align*}
    \braket{\Omega } & = \sum_i \braket{\psi|\omega_i }\braket{\omega_i|\psi}\omega_i =\sum_i \bra{\psi}\omega_i \ket{\omega_i }\braket{\omega_i|\psi}=\sum_i \braket{\psi|\Omega|\omega_i}\braket{\omega_i|\psi} \\
    \braket{\Omega}  & = \braket{\psi|\Omega|\psi}
\end{align*}
where we have used the completion relation $\sum_i \ket{\omega_i}\bra{\omega_i }$.

For continuous variable, we write
\begin{equation*}
    \braket{\Omega}=\int P(\omega)\omega\;d \omega=\int \braket{\psi|\omega}\omega \braket{\omega|\psi}\; d\omega
\end{equation*}

\subsubsection{Uncertainty.}
The uncertainty is the standard deviation defined in statistics, which measure the average fluctuation around the mean
\begin{equation*}
    \Delta\Omega=\left(\sum_i P(\omega_i)\left( \omega_i -\braket{\Omega} \right)^2 \right)^{1/2}=\left\langle \left( \Omega-\braket{\Omega} \right)^2 \right\rangle  ^{1/2}
\end{equation*}
Another expression for the uncertainty is
\begin{equation*}
    \Delta\Omega=\left( \braket{\Omega^2}-\braket{\Omega}^2 \right) ^{1/2}
\end{equation*}
This expression is related to the definition of standard deviation by expanding the square term
\begin{align*}
    \Delta\Omega=\left\langle \left( \Omega-\braket{\Omega} \right)^2 \right\rangle  ^{1/2} &
    = \left\langle \Omega^2+\braket{\Omega}^2-2\Omega \braket{\Omega } \right\rangle^{1/2}    \\
                                                                                            &
    = \left( \braket{\Omega^2}+\braket{\Omega}^2-2 \braket{\Omega}^2 \right) ^{1/2}           \\
    \Delta\Omega                                                                            &
    = \left( \braket{\Omega^2}-\braket{\Omega}^2 \right) ^{1/2}
\end{align*}

As it the case with the expectation value, the uncertainty for continuous variable is
\begin{equation*}
    \Delta\Omega=\left( \int P(\omega)\left( \omega-\braket{\Omega}^2 \right)^2  \;d \omega\right) ^{1/2}
\end{equation*}

\subsection{Density Operator}
A system is in a pure state if it is completely described by a single normalized state vector $ \ket{\psi}$ in its Hilbert space.
This means that, in principle, all expectation values of observable can be computed from that single vector.
A system is in a mixed state when it cannot be described by a single state vector, but only by a probability distribution over several possible pure states.
One way of representing a general mixed state on $n$ qubits is as the ensemble
\begin{equation*}
    \left\{ \left( \ket{\psi_1}, p_1 \right), \left( \ket{\psi_2}, p_2 \right), \ldots, \left( \ket{\psi_k}, p_k \right) \right\}
\end{equation*}
which means that the system is in the pure $n$-qubit state \(\ket{\psi_i}\) with probability \(p_i\), for \(i = 1, 2, \ldots, k\).

Another method is using density operator for an ensemble of pure states
\begin{equation*}
    \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \langle \psi_i|
\end{equation*}
This appears diagonal in $\left\{ \ket{\psi_i} \right\} $ representation, for different basis, say $\left\{ \ket{i } \right\} $, off-diagonal term may appears
\begin{equation*}
    \rho =\sum_{i,j } \rho_{ij} \ket{i }\bra{j}
\end{equation*}
with $\rho_{ij}=\braket{i  | \rho|j}$.
Here the diagonal $\rho_{ii}$ give the probabilities the of finding the system in $\ket{i}$ if measured in that basis, while the off-diagonal $\rho_{ij}$ encodes the coherence of state $\ket{i }$ with $\ket{j}$.

This captures all the relevant information about the state of the system.
We can determine the outcome of measuring state $\ket{\phi}$ using density operator
\begin{equation*}
    P(\phi)= \braket{\phi  | \rho|\phi}= \mathrm{Tr } \left( \ket{\phi }\bra{\phi }\rho \right)
\end{equation*}

\subsubsection{Partial trace.}
Consider a pure state $|\psi\rangle_{AB} \in \mathcal{H}_A \otimes \mathcal{H}_B$ of two qubits.
It may not be possible to factor out the state vector $|\psi\rangle_A \in \mathcal{H}_A$ for the state of the first qubit, however the state of the first qubit can in general be described as a mixed state.
This means that it can be described by a density operator $\rho^A$ on $\mathcal{H}_A$, sometimes called a reduced density operator.
The mathematical operation for calculating the reduced density operator is the partial trace.

The reduced density operator $\rho_A$ is defined in terms of the density operator $\rho^{AB}$ for the full 2-qubit system by
\begin{equation*}
    \rho^A \equiv \mathrm{Tr}_B \left( \rho^{AB} \right)
\end{equation*}
where $\mathrm{Tr}_B$ is the partial trace over system $B$, defined as the linear extension of the operator deﬁned on basis states by
\begin{equation*}
    \mathrm{Tr}_B \left(\ket{a_1}\bra{a_2}\otimes \ket{b_1} \bra{b_2}  \right) = \ket{a_1}\bra{a_2} \mathrm{Tr}\left( \ket{b_1}\bra{b_2} \right) = \ket{a_1}\bra{a_2} \braket{b_2|b_1}
\end{equation*}
since $\mathrm{Tr}\left( \ket{b_1} \bra{b_2} \right) =\braket{b_2|b_1} $.
Generally,
\begin{equation*}
    \mathrm{Tr}_B \left(A \otimes B  \right) = A \mathrm{Tr }(B)
\end{equation*}

For general case $n$-qubit composite system with Hilbert space
\begin{equation*}
    \mathcal{H} = \bigotimes_{i=1}^{n} \mathcal{H}_{i}
\end{equation*}
the reduced density operator on $A$ is defined by the partial trace over the complementary subsystem, ${A}'$ of $A \subset \{1, \ldots, n\}$
\begin{equation*}
    \rho^{A} \equiv \mathrm{Tr}_{{A}'}(\rho)
\end{equation*}
where $\rho$ denote the density operator acting on $\mathcal{H}$.

\subsubsection{Derivation.}
Suppose we measure in the probability of obtaining the outcome $\ket{\phi}$,
\begin{align*}
    P(\phi)
     & =  \sum_{i=1}^{k} p_i | \braket{\phi  | \psi_i}|^2
    =  \sum_{i=1}^{k} p_i \braket{\phi|\psi_i}\braket{\psi_i|\phi}                             \\
     & = \bra{\phi} \left( \sum_{i=1}^{k} p_i \ket{\psi_i} \langle \psi_i | \right) \ket{\phi} \\
    P(\phi)
     & =  \bra{\phi}\rho \ket{\phi}
\end{align*}

We can also write the probability of the measurement giving result $\phi$ as
\begin{equation*}
    P(\phi)
    =   \sum_{i=1}^{k} p_i \mathrm{Tr} ( \ket{\phi} \langle \phi| \psi_{i} \rangle \langle \psi_{i}| )
\end{equation*}
where we have used $\mathrm{Tr} (\ket{a }\bra{b})=\braket{b  | a} $.
Not very enlightening, but we can write is as
\begin{align*}
    P(\phi)
     & = \sum_{i} p_{i} \mathrm{Tr} ( \ket{\phi} \langle \phi| \psi_{i} \rangle \langle \psi_{i}| )                \\
     & = \mathrm{Tr} \left( |\phi\rangle \langle \phi| \sum_{i} p_{i} | \psi_{i} \rangle \langle \psi_{i}| \right) \\
     & = \mathrm{Tr} ( |\phi\rangle \langle \phi| \rho )
\end{align*}
where we have used the cyclicity of trace $\mathrm{Tr}(ABC) = \mathrm{Tr}(BCA) = \mathrm{Tr}(CAB)$.

We move to proving few identities.
First, writing scalar as trace
\begin{equation*}
    \mathrm{Tr}(|a\rangle\langle b|) = \sum_{n} \braket{n  | a }\braket{b  | n}= \langle b | \left( \sum_{n} | n \rangle \langle n | \right) | a \rangle = \langle b | a \rangle
\end{equation*}
Then, the cyclicity of trace
\begin{equation*}
    \mathrm{Tr}(ABC) = \sum_{n,m,k} \langle n|A|m\rangle \langle m|B|k\rangle \langle k|C|n\rangle.
\end{equation*}
Now relabel dummy indices cyclically
\begin{equation*}
    n \rightarrow m, \quad m \rightarrow k, \quad k \rightarrow n.
\end{equation*}
Since all indices are summed independently over the same set, this relabelling does not change the value.
The expression becomes
\begin{equation*}
    \sum_{n,m,k} \langle n|B|m\rangle \langle m|C|k\rangle \langle k|A|n\rangle \mathrm{Tr}(BCA)
\end{equation*}
Repeating the same argument yields that trace is invariant under cyclic permutations
\begin{equation*}
    \mathrm{Tr}(ABC) = \mathrm{Tr}(BCA) = \mathrm{Tr}(CAB).
\end{equation*}

\subsection{Coherence}
Let a system have basis $\left\{ \ket{i } \right\} $, the density operator is written
\begin{equation*}
    \rho = \sum_{i,j} \rho_{ij} \ket{i }\bra{j}
\end{equation*}
A system is coherent in that basis if at least one off-diagonal term $\rho_{ij}$ is nonzero.
Interference phenomena arise from these off-diagonal terms.

Suppose we measure an observable $X$ with eigenstates $|x\rangle$.
The probability to observe outcome $x$ is
\begin{equation*}
    P(x) = \mathrm{Tr}(\rho |x\rangle \langle x|) = \langle x | \rho | x \rangle
\end{equation*}
Expanding in the $|i\rangle$ basis
\begin{equation*}
    P(x) = \sum_{i,j} \rho_{ij} \langle x | i \rangle \langle j | x \rangle = \sum_{i,j} \rho_{ij} \psi_i(x) \psi_j^*(x),
\end{equation*}
where $\psi_i(x) \equiv \langle x | i \rangle$ are the wavefunctions in the measurement basis.
The sum can be split into diagonal ($i = j$) and off-diagonal ($i \neq j$) terms
\begin{equation*}
    P(x) = \sum_{i} \rho_{ii} |\psi_{i}(x)|^{2} + \sum_{i \neq j} \rho_{ij} \psi_{i}(x) \psi_{j}^{*}(x)
\end{equation*}
To obtain the more familiar expression, note that the second term can be written as
\[
    \sum_{i \neq j} \rho_{ij} \psi_i(x) \psi_j^*(x) = \sum_{i < j} \rho_{ij} \psi_i(x) \psi_j^*(x) + \sum_{j<i} \rho_{ij} \psi_i(x) \psi_j^*(x)
\]
The $j<i$ sum can be rewritten by swapping indices \( i \leftrightarrow j \)
\[
    \sum_{j < i} \rho_{ij} \psi_i(x) \psi_j^*(x) = \sum_{i < j} \rho_{ji} \psi_j(x) \psi_i^*(x) = \sum_{i < j} \rho_{ji} (\psi_i(x) \psi_j^*(x))^*
\]
Combining both sums gives:
\begin{align*}
    \sum_{i \neq j} \rho_{ij} \psi_i(x) \psi_j^*(x)
     & =  \sum_{i < j} \left( \rho_{ij} \psi_i(x) \psi_j^*(x) + \rho_{ji} \psi_j(x) \psi_i^*(x) \right) \\
    \sum_{i \neq j} \rho_{ij} \psi_i(x) \psi_j^*(x)
     & =  \sum_{i < j} 2 \text{Re} \left[ \rho_{ij} \psi_i^*(x) \psi_j(x) \right]
\end{align*}
\[
\]
Thus, the familiar expression can be obtained as
\begin{equation*}
    P(x) = \sum_{i} \rho_{ii} |\psi_{i}(x)|^{2} +  \sum_{i < j} 2 \text{Re} \left[ \rho_{ij} \psi_i^*(x) \psi_j(x) \right]
\end{equation*}
Here the diagonal terms contribute like classical probabilities and cause no interference, while the off-diagonal terms contribute to cross terms and responsible for interference.

\subsection{Compatibility}
The compatibility measure the degree of incompatibility between two observables; it is defined by the commutator
\begin{equation*}
    [\Omega\Lambda]=\Omega\Lambda-\Lambda\Omega
\end{equation*}

\subsubsection{Procedure.}
Here are the scheme by which the compatibility of two operators is measured.
Let us first measure $\Omega$ on the ensemble described by $\ket{\psi}$ and take the particles that yield a result $\omega$.
We immediately measure $\Lambda$ and pick those particles that give a result $\lambda$.
\begin{equation*}
    \ket{\psi}\xrightarrow{\Omega=\omega}\ket{\omega}\xrightarrow{\Lambda=\lambda}\ket{\lambda}
\end{equation*}
Here the two operator are said to be incompatible since the second measurement change the state produced by the first measurement.

Opposite case occur if the first eigenstate $\ket{\omega }$ is also an eigenstate of the second operator $\Lambda$.
We denote this simultaneous eigenstates as $\ket{\omega\lambda}$.
\begin{equation*}
    \ket{\psi}\xrightarrow{\Omega=\omega}\ket{\omega\lambda}\xrightarrow{\Lambda=\lambda}\ket{\omega\lambda}
\end{equation*}
This eigenstate obey the following equations
\begin{align*}
    \Omega \ket{\omega\lambda} & = \omega \ket{\omega\lambda}  \\
    \Lambda\ket{\omega\lambda} & = \lambda \ket{\omega\lambda}
\end{align*}
Now operate the first $\Lambda$ and the second by $\Omega$
\begin{align*}
    \Lambda\Omega \ket{\omega\lambda} & = \omega\lambda \ket{\omega\lambda} \\
    \Omega\Lambda\ket{\omega\lambda}  & = \omega\lambda \ket{\omega\lambda}
\end{align*}
then subtract the second with the first
\begin{align*}
    (\Omega\Lambda-\Lambda\Omega)\ket{\omega\lambda} & = (\omega\lambda-\omega\lambda)\ket{\omega\lambda} \\
    [\Omega,\Lambda]\ket{\omega\lambda}              & = 0 \ket{\omega\lambda}
\end{align*}
Thus $[\Omega,\Lambda]$ must have eigenkets with zero eigenvalue if simultaneous eigenkets are to exist.

\subsection{Hamiltonian}
\subsubsection{Constructing Hamiltonian.}
Hamiltonian is constructed by making the substitution $\mathcal{H}(x,p) \rightarrow H(X,P)$, where $\mathcal{H }$ is the classical Hamiltonian for the same case.

Consider a harmonic oscillator.
The classical Hamiltonian is
\begin{equation*}
    \mathcal{H }=\frac{p^2 }{2m }+\frac{1 }{2 }m\omega^2x^2
\end{equation*}
Thus the Hamiltonian for quantum harmonic oscillator is
\begin{equation*}
    H=\frac{P^2 }{2m }+\frac{1 }{2 }m\omega^2X^2
\end{equation*}
or in three dimension
\begin{equation*}
    H=\frac{P_x^2+P_y^2+P_z^2}{2m  }+\frac{1 }{2}m\omega \left[ X^2+Y^2+Z^2 \right]
\end{equation*}
assuming the force constant is the same in all directions.
It is the isotropic harmonic oscillator, meaning the restoring force has the same frequency $\omega$ in every spatial direction.
This is derived from the potential
\begin{equation*}
    V(x,y,z) = \frac{1}{2} m \omega^2 (x^2 + y^2 + z^2)
\end{equation*}
which generate the isotropic force
\begin{equation*}
    \mathbf{F }= -m \omega^2 \mathbf{r}
\end{equation*}

Now consider a particle in one dimension is subject to a constant force $f$.
The classical Hamiltonian is
\begin{equation*}
    \mathcal{H }=\frac{p^2 }{2m }-fx
\end{equation*}
Thus the quantum Hamiltonian
\begin{equation*}
    H=\frac{P^2 }{2m }-fX
\end{equation*}

Now consider particle of charge $q$ in an electromagnetic field.
The classical Hamiltonian is
\begin{equation*}
    \mathcal{H }=\frac{|\mathbf{p }-(q/c) \mathbf{A}(\mathbf{r},t)|^2 }{2m }+q\phi(\mathbf{r },t)
\end{equation*}
The Hamiltonian is constructed by using the symmetric form
\begin{equation*}
    H=\frac{P^2 }{2m }\left( \mathbf{P }\cdot \mathbf{P }-\frac{q }{c }\mathbf{P }\cdot \mathbf{A}-\frac{q }{c}\mathbf{A}\cdot \mathbf{P}+\frac{q^2 }{c^2}\mathbf{A }\cdot \mathbf{A}\cdot \mathbf{A} \right) +q\phi
\end{equation*}

\subsection{Parity}
Parity refers to the transformation of spatial inversion about the origin $x \mapsto -x$.
The corresponding operator is called the parity operator $\Pi$ defined by its action on the position eigenkets
\begin{equation*}
    \Pi \ket{x }=\ket{-x}
\end{equation*}
Given a state $\ket{\psi}$ and its position representation $\psi(x) = \braket{x|\psi}$, the action of the parity operator on this wavefunction is
\begin{equation*}
    \Pi\psi(x) = \psi(-x) .
\end{equation*}

If $\ket{\psi}$ is an eigenstate of the parity operator, then under spatial inversion it transforms as
\begin{equation*}
    \psi(-x) = \lambda \, \psi(x) ,
\end{equation*}
where $\lambda$ is the corresponding eigenvalue.
Since $\Pi^2 = I $ its eigenvalues can only be $\lambda = \pm 1$.
This leads to two possibilities: even parity (symmetric) and odd parity (antisymmetric)
\begin{equation*}
    \psi(-x) = +\psi(x) \qquad    \psi(-x) = -\psi(x)
\end{equation*}
In quantum mechanics parity means \enquote{eigenvalue under the inversion symmetry operator}, while mathematically it means \enquote{even} and \enquote{odd} function.

\subsubsection{Symmetric potential.}
If the potential satisfies
\begin{equation*}
    V(-x) = V(x) ,
\end{equation*}
then the Hamiltonian operator
\begin{equation*}
    H = -\frac{\hbar^2}{2m}\frac{d^2}{dx^2} + V(x)
\end{equation*}
commutes with the parity operator:
\begin{equation*}
    [H, \Pi] = 0
\end{equation*}
This can be easily seen  by considering that kinetic term and the potential are invariant.
Then, eigenfunctions of $H$ (stationary states) can be chosen to simultaneously be eigenfunctions of $\Pi$.
Thus, its eigenfunctions are exactly the even and odd function
\begin{equation*}
    \psi(-x) = +\psi(x) \qquad    \psi(-x) = -\psi(x)
\end{equation*}

\subsection{WKB Approximation}
Wentzel--Kramers--Brillouin (WKB) is a technique to obtain approximate solutions to time independent problems, mainly in 1D or where only $r$ matters in 3D.
The WKB method is valid when the potential varies slowly on the scale of the particle’s wavelength.

In classically allowed regions $V(x)<E$, WKB provides an oscillatory wavefunction of the form
\begin{equation*}
    \psi(x) \sim \frac{1}{\sqrt{p(x)}} \left[A\exp\left(\frac{i}{\hbar} \int^{x} p(x') dx'\right) + B\exp\left(-\frac{i}{\hbar} \int^{x} p(x') dx'\right)\right]
\end{equation*}
In classically forbidden regions $E<V(x)$, WKB provides an exponentially decaying or growing wavefunction
\begin{equation*}
    \psi(x) \sim \frac{C}{\sqrt{|p(x)|}} \left[A\exp\left( \frac{1}{\hbar} \int^{x} |p(x')| dx' \right) + B\exp\left( -\frac{1}{\hbar} \int^{x} |p(x')| dx' \right)\right]
\end{equation*}
The momentum is simply the classical momentum
\begin{equation*}
    p_{V<E}(x) = \sqrt{2m[E - V(x)]}\qquad
    p_{E<V}(x) = \sqrt{2m[ V(x)-E]}
\end{equation*}

\subsubsection{WKB quantization.}
The WKB quantization condition depends on the nature of the boundaries: for two smooth turning points
\begin{equation*}
    \int p(x) dx = (n + \frac{1}{2}) \pi \hbar
\end{equation*}
two hard walls (infinite well)
\begin{equation*}
    \int p(x) dx = n \pi \hbar
\end{equation*}
one hard wall and one smooth turning point
\begin{equation*}
    \int p(x) dx = (n + \frac{3}{4}) \pi \hbar
\end{equation*}
Note that a turning point is called smooth if, in a neighborhood of $x_t$, $V(x)$ is finite and differentiable, while $V'(x)$ finite and nonzero.

\subsection{Perturbation Theory}
Time-independent perturbation theory is an approximation scheme that applies in the following context: we know the solution to the eigenvalue problem of the Hamiltonian $H^0$, and we want the solution to
\begin{equation*}
    H=H^0 +\epsilon H^1
\end{equation*}
where $H^1$ is small compared to $H^0$.
Note that the assumption is not that $\epsilon$ is small, rather $H^1$ is small compared to $H^0$, or more accurately
\begin{equation*}
    \left|\frac{\left\langle m^0 | H | n^0 \right\rangle}{E_n^0 - E_m^0} \right| \ll 1
\end{equation*}

We assume that to every eigenket $|E_n^0\rangle \equiv |n^0\rangle$ of $H^0$ with eigenvalue $E_n^0$, there is an eigenket $|n\rangle$ of $H$ with eigenvalue $E_n$.
We then assume that the eigenkets and eigenvalues of $H$ may expanded in a perturbation series:
\begin{align*}
    |n\rangle & =
    |n^{0}\rangle +\epsilon |n^{1}\rangle +\epsilon^2 |n^{2}\rangle + \dots \\
    E_n       & =
    E_n^{0} + \epsilon E_n^{1} +\epsilon^2 E_n^{2} + \dots
\end{align*}
Although not physical states themselves, $\ket{n^k}$ have physical interpretation: $\ket{n^0}$ the unperturbed state;  $\ket{n^2}$ describes first-order mixing with other unperturbed states;  and $\ket{n^2}$ describes second-order mixing effects, including indirect coupling.

The result of zeroth order approximation is our previous assumption
\begin{equation*}
    H^0 \ket{n^0}=E_n^0 \ket{n ^0}
\end{equation*} 
The result of first order approximation are 
\begin{align*}
        \ket{n}
    &     =\ket{n^0}+\sum_{m \neq n} \frac{ \braket{m^{0} | H^{1} | n^{0} }}{E^{0}_n - E^{0}_m}\ket{m^0} \\
    E^1_n                                                             & =  \langle n^0 | H^1 | n^0 \rangle
\end{align*}
Using the result of first order approximation, the second order approximation can be obtained as follows
\begin{align*}
    E_n^{2} = \sum_{m \neq n} \frac{|\langle n^0 | H | m^0 \rangle|^2}{E^0_n - E^0_m}     
\end{align*}

\subsubsection{Derivation.}
We then substitute these into the eigenvalue equation
\begin{multline*}
    (H^0+\epsilon H^1) \left( |n^{0}\rangle +\epsilon |n^{1}\rangle +\epsilon^2 |n^{2}\rangle + \dots  \right) \\
    = \left( E_n^{0} + \epsilon E_n^{1} +\epsilon^2 E_n^{2} + \dots \right) \left( |n^{0}\rangle +\epsilon |n^{1}\rangle +\epsilon^2 |n^{2}\rangle + \dots  \right)
\end{multline*}
Then collect the same power of $\epsilon$.
The zeroth order comes from  $\epsilon^0$
\begin{equation*}
    H^0 \ket{n^0}=E_n^0 \ket{n ^0}
\end{equation*}
By assumption, this equation may be solved and, so we move on to the first-order terms, which comes from $\epsilon^1$
\begin{equation*}
    H^{0} | n^{1} \rangle + H^{1} | n^{0} \rangle = E^{0}_{n} | n^{1} \rangle + E^{1}_{n} | n^{0} \rangle
\end{equation*}

Dotting both side with $\bra{n^0}$
\begin{align*}
    \langle n^0 | H^1 | n^1 \rangle + \langle n^0 | H^1 | n^0 \rangle & =  E^0_n \langle n^0 | n^1 \rangle + E^1_n \langle n^0 | n^0 \rangle \\
    E^0_n \langle n^0 | n^1 \rangle + \langle n^0 | H^1 | n^0 \rangle & =  E^0_n \langle n^0 | n^1 \rangle + E^1_n                           \\
    E^1_n                                                             & =  \langle n^0 | H^1 | n^0 \rangle
\end{align*}
This result state the first-order change in energy is the expectation value of $H^1$ in the unperturbed state.

Let us next dot both sides with another eigenket of the same unperturbed Hamiltonian $\bra{m^0}$, with $m \neq n$
\begin{align*}
    \langle m^{0}|H^{0}|n^{1}\rangle + \langle m^{0}|H^{1}|n^{0}\rangle &= E^{0}_n\langle m^{0}|n^{1}\rangle + E^{1}_n\langle m^{0}|n^{0}\rangle\\
    E^{0}_m\langle m^{0}|n^{1}\rangle + \langle m^{0}|H^{1}|n^{0}\rangle & =  E^{0}_n\langle m^{0}|n^{1}\rangle\\
(E^{0}_n - E^{0}_m) \langle m^{0} | n^{1} \rangle & =  \langle m^{0} | H^{1} | n^{0} \rangle\\
\langle m^{0} | n^{1} \rangle & =  \frac{\langle m^{0} | H^{1} | n^{0} \rangle}{E^{0}_n - E^{0}_m}
\end{align*}
Also recall that the unperturbed eigenstates are orthonormal $\braket{m^0  | n^0 }=\delta_{mn}$.
This gives the projection of  $\ket{n^1}$ onto the unperturbed basis vector $\ket{m^0}$, except for the case of $m=n$, which correspond to the parallel of $\ket{n ^{1 }}$ with respect $\ket{m ^{1}}$.

To see this, consider the decomposition of $\ket{n ^{1 }}$ in terms of $\ket{m ^{0}}$
\begin{equation*}
    |n^{1}\rangle = \sum_{m} |m^{0}\rangle \langle m^{0}|n^{1}\rangle
\end{equation*}
However, as we have seen, the projection coefficient is undetermined for $m=n$, hence we split them.
\begin{equation*}
    |n^{1}\rangle = |n^{0}\rangle \langle n^{0}|n^{1}\rangle+\sum_{m \neq n} |m^{0}\rangle \langle m^{0}|n^{1}\rangle
\end{equation*}
Here the first term correspond to the parallel components, as mentioned, while the second to the perpendicular component.

With $\ket{n^1}=\ket{n_\parallel^1}+\ket{n_\perp^1}$ with respect to $\ket{n^0}$ and first order approximation $\ket{n}=\ket{n^0}+\ket{n ^{1}}$, normalization require 
\begin{align*}
    \braket{n  | n } & =  \braket{\bra{n^0}+\bra{n_\parallel^1}+\bra{n_\perp^1} | \ket{n^0}+\ket{n_\parallel^1}+\ket{n_\perp^1}}\\
    1 & =  \langle n^0 | n^0 \rangle + \langle n^1_{\parallel} | n^0 \rangle + \langle n^0 | n^1_{\parallel} \rangle + \text{higher order}
\end{align*}
Only the orthonormal has real value $\braket{n^0 | n^0 }=1$, so 
\begin{equation*}
    0 = \langle n^1 | n^0 \rangle + \langle n^0 | n^1 \rangle + \text{higher order} = 2 \mathrm{Re }\braket{n ^{0 } | n ^{1 }_{\parallel}}+ \text{higher order} 
\end{equation*}
This mean  that $\braket{n ^{0 } | n ^{1 }_{\parallel}}= i\alpha$.
By definition, parallel vector mean 
\begin{equation*}
    \ket{n_{\parallel} ^{1}} = \braket{n ^{0 } | n ^{1 }} \ket{n ^{0}}
    =\braket{n ^{0 } | n ^{1 }_\parallel} \ket{n ^{0}} + \braket{n ^{0 } | n ^{1 }_\perp} \ket{n ^{0}}
    = i \alpha \ket{n ^{0 }} = i\alpha  \ket{n ^{0 }}
\end{equation*}
where the inner product of $\ket{n ^{1}_\perp}$ is $\ket{n ^{0}}$ is zero.
Substituting this back into the first order approximation
\begin{align*}
    \ket{n}
    & = \ket{n^0}+\ket{n_\parallel^1}+\ket{n_\perp^1} 
    =\ket{n^0}+i\alpha\ket{n^0}+\ket{n_\perp^1} 
    =(1+i\alpha)\ket{n^0}+\ket{n_\perp^1} \\
    \ket{n}
    & =  e ^{i\alpha}\ket{n^0}+\sum_{m \neq n} \frac{ \braket{m^{0} | H^{1} | n^{0} }}{E^{0}_n - E^{0}_m}\ket{m^0} 
\end{align*} 
By multiplying with $e ^{-i\alpha}$ we can remove the phase factor to the first term, all while the second term being unaffected, since for first order approximation
\begin{equation*}
    (1 - i\alpha)(\text{first order}) = \text{first order} + \text{second order}
\end{equation*}
the second order term $-i\alpha (\text{second order})$  gets  discarded.
Calling the perturbed eigenket with the new phase also $\ket{n }$, we obtain the result to the first order
\begin{equation*}
    \ket{n}
    = \ket{n ^{0 }} + \ket{n ^{1 } } 
    = \ket{n _{\parallel}} +\ket{n _{\perp} } 
    =\ket{n^0}+\sum_{m \neq n} \frac{ \braket{m^{0} | H^{1} | n^{0} }}{E^{0}_n - E^{0}_m}\ket{m^0} 
\end{equation*}

To obtain the second order, we collect the coefficient for  $\epsilon^2$ term 
\begin{equation*}
H^0|n^2\rangle + H^1|n^1\rangle = E^0_n \ket{n^2} + E^1_n \ket{n^1} + E^2_n \ket{n^0}
\end{equation*}
Then dotting with $\ket{n ^{0}}$
\begin{align*}
    E^0_n \braket{n^0 |n^2 }+ \braket{n ^{0 } | H^1|n ^{1}} & =  E_n^{0} \langle n^{0} | n^{2} \rangle + E_n^{1} \langle n^{0} | n^{1} \rangle + E_n^{2} \langle n^{0} | n^{0} \rangle\\
    E_n^{2} & =      \braket{n ^{0 } | H^1|n ^{1}} \\
    & = \sum_{m \neq n} \frac{\langle n^0 | H | m^0 \rangle \langle m^0 | H | n^0 \rangle}{E^0_n - E^0_m} \\
    E_n^{2}
    & = \sum_{m \neq n} \frac{|\langle n^0 | H | m^0 \rangle|^2}{E^0_n - E^0_m} 
\end{align*}
\end{document}