\documentclass[../../../main.tex]{subfiles}
\begin{document}
\subsection{Dirac Equation}
The Dirac equation is
\begin{equation*}
    i \hbar \; \partial_t \Psi(\mathbf{r },t) = H \Psi(\mathbf{r },t)
\end{equation*}
with the Hamiltionian
\begin{equation*}
    H = c \hat{\boldsymbol{\alpha}} \cdot \mathbf{p} + \hat{\beta}mc^2
    = \begin{bmatrix}
        m c^{2} \mathbf{1}                        & c\,\boldsymbol{\sigma}\cdot\hat{\mathbf{p}} \\
        c\boldsymbol{\sigma}\cdot\hat{\mathbf{p}} & -m c^{2} \mathbf{1}
    \end{bmatrix}
\end{equation*}
and $\Psi(\mathbf{r },t)$ as the four-component spinor. 
It can also be written in this way 
\begin{equation*}
    i\hbar \;\partial_t \Psi(\mathbf{r},t)=\left(-i\hbar c\hat{\boldsymbol{\alpha}}\cdot\nabla + \hat{\beta}m c^{2}\right)\Psi(\mathbf{r},t)
\end{equation*}

The matrices $\hat{\alpha}_i$ and $\hat{\beta}$ defined as
\begin{equation*}
    {\hat{\alpha}}_i = \begin{bmatrix} \mathbf{0} & {\sigma}_i\\  {\sigma}_i & \mathbf{0} \end{bmatrix}\qquad
    \beta = \begin{bmatrix} \mathbf{1} & \mathbf{0}\\ \mathbf{0} & -\mathbf{1} \end{bmatrix}
\end{equation*}
and satisfies
\begin{equation*}
    \{\hat{\alpha}_i,\alpha_j\}=2\delta_{ij} \qquad
    \{\hat{\alpha}_i,\beta\}=\mathbf{0} \qquad
    \hat{\beta}^2=\mathbf{0}
\end{equation*}

The equation has the same structure with the Schrödinger equation, in fact this is the relativistic generalization of the Schrödinger equation.
This equation is constructed specifically to satisfy the relativistic energy $E= \sqrt{\mathbf{p }^2c^2+m^2c^4}$.

\subsubsection{Spinor-field.}
The four-components spinor encode two states of spin-$1/2$ particle and degenerate solution of relativistic dispersion relation $E^2 = p^2c^2+m^2c^4$.
The components can be grouped as 
\begin{equation*}
\Psi = \begin{bmatrix}\phi\\\chi\end{bmatrix} \qquad
\phi = \begin{bmatrix}\psi_1\\\psi_2\end{bmatrix} \qquad
\chi = \begin{bmatrix}\psi_3\\\psi_4\end{bmatrix}
\end{equation*}
$\phi$ component encode degrees of freedom at low energy; while $\chi$ encode relativistic correction responsible for spin–orbit coupling, magnetic moment, relativistic effects.
The coupling of $\phi$ and $\chi$
\begin{equation*}
 \begin{bmatrix}
        m c^{2}                         & c\,\boldsymbol{\sigma}\cdot\hat{\mathbf{p}} \\
        c\boldsymbol{\sigma}\cdot\hat{\mathbf{p}} & -m c^{2} 
    \end{bmatrix}
\begin{bmatrix}\phi\\\chi\end{bmatrix}
= \begin{bmatrix}
mc^{2}\phi + c\bigl(\boldsymbol{\sigma}\cdot\mathbf{p}\bigr)\chi\\
c\bigl(\boldsymbol{\sigma}\cdot\mathbf{p}\bigr)\phi - mc^{2}
\end{bmatrix}
\end{equation*}
via $\boldsymbol{\sigma}\cdot \mathbf{p}$  is what makes the theory relativistic.

\subsubsection{Klein-Gordon equation.}
The Klein-Gordon originaly interpreted to generalize the Schrödinger equation in relativistic.
It starts with the relativistic energy
\begin{equation*}
    E^2 = p^2c^2+ m^2c^4
\end{equation*}
then introduce the prescription $    \mathbf{p} \to -i\hbar\nabla \qquad$ and  $    H \to i\hbar \;\partial_t$
\begin{equation*}
    \bigg(\frac{1}{c^2}\frac{\partial^2}{\partial t^2} - \nabla^2 + \frac{m^2 c^2}{\hbar^2}\bigg)\psi(\mathbf r,t) = 0
\end{equation*}
The equation is also known as the generalization of Maxwell’s wave equation for massive particles.
Asidem, the equation suffer two problem.
\begin{enumerate}
    \item \textbf{Negative energy.}
    The equation was supposed to describe single relativistic particle $\psi(\mathbf{r},t)$, it however include both spectrum of $+E$ and $-E$, so the theory is unbounded below if interpreted as a single-particle system. 

    In relativistic quantum field theory, this is corrected by interpreting $\psi(\mathbf{r},t)$ as the quantum field, and the negative energy as antiparticle. 
    \item \textbf{Incorrect probability density.} 
    A probability density must satisfies conserved
    \begin{equation*}
        \frac{d }{dt } \int d^3 \mathbf{r} \rho(\mathbf{r},t) = 0
    \end{equation*} 
    and positive definite
    \begin{equation*}
        \rho(\mathbf{r},t) \geq  0
    \end{equation*}
    quantity.
    Single plane wave state $\rho(\mathbf{r},t) = |\psi|^2$ does produce time-independent $\rho(\mathbf{r})$, however superpositions of pure states cause interference term to appear and time dependence to be produced.
    There exists a conserved current
    \begin{equation*}
        \rho = \frac{i\hbar}{2 m c^{2}}\bigl(\psi^{*}\partial_{t}\psi - \psi\partial_{t}\psi^{*}\bigr)
    \end{equation*}
    that satisfies the time-independence.
    This probability density, however, is not positive definite, so it still invalidates its interpretation as a probability density.
\end{enumerate}

Dirac's equation able to produce the continuity equation
\begin{equation*}
    \partial_t \rho(\mathbf{r },t) + c \nabla \cdot \mathbf{j}(\mathbf{r },t)=0
\end{equation*}
with $\rho(\mathbf{r },t)$ and $\mathbf{j}(\mathbf{r },t)$ three-valued 
\begin{equation*}
    \rho  (\mathbf{r },t)= \Psi ^\dagger(\mathbf{r },t)\Psi(\mathbf{r },t) \qquad
    \mathbf{j}(\mathbf{r },t)=\Psi ^\dagger (\mathbf{r },t)\hat{\boldsymbol{\alpha } }\Psi(\mathbf{r },t)
\end{equation*}
which does not suffer from non-conserved probability density
\begin{equation*}
\partial_t \int d^3r\;\rho =0
\end{equation*}

\subsubsection{Derivation: Dirac approach.}
He considered a wave equation with only first derivatives with respect to time and space and introduced the classical energy
\begin{equation*}
    E = c\boldsymbol{\hat{\alpha}}\cdot\mathbf{p} + \hat{\beta}m c^2
\end{equation*}
such that squaring it one recovers the relativistic energy
\begin{equation*}
    E ^{2 } =  \mathbf{p }^2c^2 +m^2c^4
\end{equation*}
Since spatial translations are generated by momentum and time translations are generated by the Hamiltonian, we introduce quantization prescription
\begin{equation*}
    \mathbf{p} \to -i\hbar\nabla \qquad
    H \to i\hbar \;\partial_t
\end{equation*}
The classical energy now reads
\begin{equation*}
    i\hbar \;\partial_t \Psi(\mathbf{r},t)=\left(-i\hbar c\hat{\boldsymbol{\alpha}}\cdot\nabla + \hat{\beta}m c^{2}\right)\Psi(\mathbf{r},t)
\end{equation*}
Notice that the wavefunction $\Psi(\mathbf{r },t)$, has four components in the abstract space of Dirac matrices, as such
\begin{equation*}
    i\hbar\partial_t
    \begin{bmatrix}
        \psi_1(\mathbf{r},t) \\
        \psi_2(\mathbf{r},t) \\
        \psi_3(\mathbf{r},t) \\
        \psi_4(\mathbf{r},t)
    \end{bmatrix}
    =
    \hat{H}
    \begin{bmatrix}
        \psi_1(\mathbf{r},t) \\
        \psi_2(\mathbf{r},t) \\
        \psi_3(\mathbf{r},t) \\
        \psi_4(\mathbf{r},t)
    \end{bmatrix}
\end{equation*}

The first term of the Hamiltonian has the elements of 
\begin{align*}
    \boldsymbol{\sigma}\cdot \hat{\mathbf p}
     & = -i\hbar\left( \sigma_x \partial_x + \sigma_y \partial_y + \sigma_z \partial_z \right) \\
     & = -i\hbar \left(
    \begin{bmatrix}
            0          & \partial_x \\
            \partial_x & 0
        \end{bmatrix}
    +
    \begin{bmatrix}
            0           & -i\partial_y \\
            i\partial_y & 0
        \end{bmatrix}
    +
    \begin{bmatrix}
            \partial_z & 0 \\
            0          & -\partial_z
        \end{bmatrix}
    \right) \\
     & = -i\hbar
    \begin{bmatrix}
        \partial_z               & \partial_x - i\partial_y \\
        \partial_x + i\partial_y & -\partial_z
    \end{bmatrix}
\end{align*}
Along the second term being trivial, the Hamiltonian explicitly written as 
\begin{equation*}
    \begin{bmatrix}
        mc^2                                             & 0                                                & -i\hbar c\;\partial_z                            & -i \hbar c \left( \partial_x-i \;\partial_y \right) \\
        0                                                & mc^2                                             & -i\hbar c\left(\partial_x + i\;\partial_y\right) & i\hbar c\,\partial_z                                \\
        -i\hbar c\;\partial_z                            & -i\hbar c\left(\partial_x - i\;\partial_y\right) & -mc^2                                            & 0                                                   \\
        -i\hbar c\left(\partial_x + i\;\partial_y\right) & i\hbar c\;\partial_z                             & 0                                                & -mc^2
    \end{bmatrix}
\end{equation*}

\subsubsection{Derivation: continuity equation.}
Start from the Dirac equation and its conjugate
\begin{gather*}
    \partial_t \Psi(\mathbf{r},t)=-c\hat{\boldsymbol{\alpha}}\cdot\nabla \Psi(\mathbf{r},t) 
     + (i m c^{2}/\hbar )\hat{\beta} \Psi(\mathbf{r},t) \\
    \partial_t \Psi ^\dagger(\mathbf{r},t)=-c [\nabla \Psi ^\dagger(\mathbf{r},t)] \cdot \hat{\boldsymbol{\alpha}}
    -(i m c^{2}/\hbar )\Psi ^\dagger(\mathbf{r},t) \hat{\beta} 
\end{gather*}
Left multiply the Dirac equation with the Hermitian conjugate of the wavefunction
\begin{equation*}
    \Psi ^\dagger \partial_t \Psi=c\Psi ^\dagger\hat{\boldsymbol{\alpha}}\cdot\nabla \Psi 
    + (i m c^{2}/\hbar ) \Psi ^\dagger \hat{\beta} \Psi 
\end{equation*}
the right multiply the Hermitian conjugate of the Dirac equation with the wavefunction
\begin{equation*}
    (\partial_t \Psi ^\dagger) \Psi=c [\nabla \Psi ^\dagger] \cdot \hat{\boldsymbol{\alpha}}\Psi
    -(i m c^{2}/\hbar )\Psi ^\dagger \hat{\beta} \Psi
\end{equation*}
and add both 
\begin{equation*}
    \partial_t \Psi ^\dagger\Psi 
    = -c \left[     \Psi ^\dagger\hat{\boldsymbol{\alpha}}\cdot\nabla \Psi + (\nabla \Psi ^\dagger) \cdot \hat{\boldsymbol{\alpha}}\Psi \right] 
\end{equation*}

Noting that $\hat{\boldsymbol{\alpha}}$ is constant in space such that $\nabla \hat{\boldsymbol{\alpha}} = 0$, can write
\begin{align*}
    \nabla \cdot (\Psi ^\dagger \hat{\boldsymbol{\alpha } }\Psi) 
    & = \sum_{i } \partial_i\big(\Psi^\dagger\hat{\alpha}_i\Psi\big)\\
    & =  \sum_{i } (\partial_i\Psi^\dagger)\,\hat{\alpha}_i\,\Psi + \Psi^\dagger(\partial_i\hat{\alpha}_i)\Psi + \Psi^\dagger\hat{\alpha}_i(\partial_i\Psi)\\
    & = \sum_i\big[(\partial_i\Psi^\dagger)\hat{\alpha}_i\,\Psi + \Psi^\dagger\hat{\alpha}_i(\partial_i\Psi)\big]\\
    \nabla \cdot (\Psi ^\dagger \hat{\boldsymbol{\alpha } }\Psi) 
    & = (\nabla\Psi^\dagger)\cdot\boldsymbol{\hat{\alpha}}\Psi + \Psi^\dagger\big(\boldsymbol{\hat{\alpha}}\cdot\nabla\Psi\big)
\end{align*}
So we obtain the continuity equation
\begin{equation*}
    \partial_t \rho + c \nabla \cdot \mathbf{j}=0
\end{equation*}
where 
\begin{equation*}
    \rho  = \Psi ^\dagger\Psi \qquad
    \mathbf{j}=\Psi ^\dagger \hat{\boldsymbol{\alpha } }\Psi
\end{equation*}

Now integrate over all space
\begin{equation*}
\int d^3r\;\partial_t \rho + \int d^3r\;\nabla \cdot  \mathbf{j} = 0    
\end{equation*}
Using divergence theorem 
\begin{equation*}
\partial_t \int d^3r\;\rho + \oint d \mathbf{a}\cdot  \mathbf{j} = 0        
\end{equation*}
Applying vanishing current at infinity, we obtain the conserved probability density
\begin{equation*}
\partial_t \int d^3r\;\rho =0
\end{equation*}

\subsection{Pauli Equation}
The origin of spin can be traced back in the Pauli equation.
The standard form is
\begin{equation*}
    i\hbar \; \partial_t\psi 
     =  \left[\frac{1}{2m}(\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}-\frac{q \hbar}{2m }\mathbf{B }\cdot  \boldsymbol{\sigma} +q\phi\right]\psi    
\end{equation*}
Explicitly, the spin appear as 
\begin{equation*}
        i\hbar \; \partial_t\psi 
     =  \left[\frac{1}{2m}(\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}-\frac{q }{m }\mathbf{B }\cdot \mathbf{S} +q\phi\right]\psi        
\end{equation*}

\subsubsection{Derivation.}
Suppose the relativistic particle has the electric charge $q$, by using the Gauge-invariant substitution
\begin{equation*}
    E \to i\hbar\;\partial_t-q\phi(\mathbf r,t)  \qquad \mathbf{p} \to -i\hbar\nabla - q\mathbf{A}(\mathbf r,t)
\end{equation*}
We obtain the Dirac equation in the form 
\begin{equation*}
    i\hbar\;\partial_t\Psi(\mathbf r,t) = 
    \Big(c\hat{\boldsymbol\alpha}\cdot\big(\hat{\mathbf p}-q\mathbf{A}(\mathbf r,t)\big)+\beta\,mc^2+q\phi(\mathbf r,t)\Big)\Psi(\mathbf{ r},t)
\end{equation*}
The spinor then is set as 
\begin{equation*}
\Psi(\mathbf r,t)
\to e^{-imc^2t/\hbar}
\begin{bmatrix}
\psi(\mathbf r,t)\\ 
\chi(\mathbf r,t)
\end{bmatrix}
\end{equation*}
so that we obtain
\begin{align*}
    (    i\hbar \; \partial_t- mc^2)
\begin{bmatrix}
\psi\\
\chi
\end{bmatrix}
& = 
\begin{bmatrix}
q\phi+mc^2 & c\boldsymbol{\sigma}\cdot(\hat{\mathbf p}-q\mathbf{A})\\
c\boldsymbol{\sigma}\cdot(\hat{\mathbf p}-q\mathbf{A}) & q\phi-mc^2
\end{bmatrix}
\begin{bmatrix}
\psi\\
\chi
\end{bmatrix}
\\
    i\hbar \; \partial_t
\begin{bmatrix}
\psi\\
\chi
\end{bmatrix}
& = 
\begin{bmatrix}
q\phi & c\boldsymbol{\sigma}\cdot(\hat{\mathbf p}-q\mathbf{A})\\
c\boldsymbol{\sigma}\cdot(\hat{\mathbf p}-q\mathbf{A}) & q\phi-2mc^2
\end{bmatrix}
\begin{bmatrix}
\psi\\
\chi
\end{bmatrix}
\end{align*}

Consider non-relativistic approximation
\begin{equation*}
\bigl(i\hbar \; \partial_t - q\phi + 2mc^{2}\bigr)\chi \approx 2mc^{2}\chi
\end{equation*}
The term $i\hbar \; \partial_t - q\phi$ represent kinetic operator in this case, since it is equal to total energy $i\hbar \; \partial_t$ minus the potential $q\phi$ operator.
The non-relativistic condition reads $v \ll c$, which this approximation satisfies by $T \sim mv^2/2$.
Under this approximation, the equation reads 
\begin{equation*}
    i\hbar \; \partial_t
\begin{bmatrix}
\psi\\
0
\end{bmatrix}
=
\begin{bmatrix}
q\phi & c\boldsymbol{\sigma}\cdot(\hat{\mathbf p}-q\mathbf{A})\\
c\boldsymbol{\sigma}\cdot(\hat{\mathbf p}-q\mathbf{A}) & -2mc^2
\end{bmatrix}
\begin{bmatrix}
\psi\\
\chi
\end{bmatrix} 
\end{equation*}

We have then the lower equation
\begin{equation*}
    \chi = \frac{\hat{\boldsymbol{\sigma}}\cdot(\hat{\mathbf{p}}-qA)}{2mc}\psi
\end{equation*}
Inserting this expression in the upper equation 
\begin{equation*}
    i\hbar \; \partial_t\psi 
    = \left(\frac{\big[\hat{\sigma}\cdot(\hat{\mathbf{p}}-qA)\big]^2}{2m}+q\phi\right)\psi
\end{equation*}
Using
\begin{equation*}
    (\mathbf{a} \cdot \boldsymbol{\sigma})(\mathbf{b} \cdot \boldsymbol{\sigma}) = \mathbf{a} \cdot \mathbf{b} + i(\mathbf{a} \times \mathbf{b}) \cdot \boldsymbol{\sigma}
\end{equation*}
we can evaluate
\begin{align*}
    (\boldsymbol{\sigma}\cdot(\mathbf{{\hat{p}}}-q\mathbf{A}))^2 
    &= (\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}+ i\big((\mathbf{{\hat{p}}}-q\mathbf{A})\times(\mathbf{{\hat{p}}}-q\mathbf{A})\big)\cdot\boldsymbol{\sigma}\\
    &= (\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}+ i\big(    \mathbf{{\hat{p}}}\times\mathbf{{\hat{p}}} - q\mathbf{{\hat{p}}}\times\mathbf{A} \\
    &\qquad- q\mathbf{A}\times\mathbf{{\hat{p}}} + q^{2}\mathbf{A}\times\mathbf{A}\big)\cdot\boldsymbol{\sigma}\\
    &= (\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}+ iq\big(\mathbf{{\hat{p}}}\times\mathbf{A} + \mathbf{A}\times\mathbf{{\hat{p}}} \big)\cdot\boldsymbol{\sigma}\\
    (\boldsymbol{\sigma}\cdot(\mathbf{{\hat{p}}}-q\mathbf{A}))^2 
    &= (\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}+ q \hbar \mathbf{B}\cdot\boldsymbol{\sigma}
\end{align*}
The anticommutator is evaluated on test function as 
\begin{align*}
    \left\{ \mathbf{\hat{p },\mathbf{A }} \right\} \psi
    & =-i\hbar\nabla\times\mathbf{A}\psi - i \hbar\mathbf{A}\times\nabla\psi \\
    & = -i\hbar\big[(\nabla\times\mathbf{A}) \psi + (\nabla \psi) \times  \mathbf{A}+\mathbf{A}\times(\nabla\psi)\big]\\
    & = -i\hbar\big[(\nabla\times\mathbf{A}) \psi + (\nabla \psi) \times  \mathbf{A} - (\nabla \psi) \times  \mathbf{A} \big]\\
    \left\{ \mathbf{\hat{p },\mathbf{A }} \right\} \psi
    & = -i\hbar(\nabla\times\mathbf{A}) \psi = -i\hbar \mathbf{B} \psi 
\end{align*}
The spin naturally occur by design 
\begin{align*}
    i\hbar \; \partial_t\psi 
     =  \left[\frac{1}{2m}(\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}-\frac{q \hbar}{2m }\mathbf{B }\cdot  \boldsymbol{\sigma} +q\phi\right]\psi    \\
    i\hbar \; \partial_t\psi 
     =  \left[\frac{1}{2m}(\mathbf{{\hat{p}}}-q\mathbf{A}) ^{2}-\frac{q }{m }\mathbf{B }\cdot \mathbf{S} +q\phi\right]\psi    
\end{align*}
It is an unavoidable consequence of the Dirac algebra structure once the non-relativistic limit is taken.

\subsection{Spin wave}
The Heisenberg Hamiltionian
\begin{equation*}
    H = -\frac{J}{2}\sum_{\langle ij\rangle}\mathbf{S}_i\cdot\mathbf{S}_j
\end{equation*}
describes exchange interactions between localized spins on a lattice.
The sum runs over pair of neighboring sites $i$ and $j$ that are nearest neighbors on the lattice, and the factor $1/2$ there to prevent double counting.
By mapping spin operators to bosonic operators and retaining only quadratic terms, the Hamiltonian can be approximately diagonalized in momentum space
\begin{equation*}
    H = \text{const} + \sum_{\mathbf{k}} \hbar \omega_{\mathbf{k}}\, \hat{a}_{\mathbf{k}}^\dagger \hat{a}_{\mathbf{k}} 
\end{equation*}
with 
\begin{equation*}
    \hbar \omega_{\mathbf{k }} 
    = Js\left[z - g_\mathbf{k} \right] 
    \qquad  g_\mathbf{k} = \sum_{\boldsymbol{\delta}} e^{-i \mathbf{k}\cdot \boldsymbol{\delta}}
\end{equation*}
For spin chain, we have 
\begin{equation*}
g_\mathbf{k} = e^{-ika}+e^{ika}=2\cos(ka)
\end{equation*}
While for 2D graphene
\begin{equation*}
    g_{\mathbf{k}} = e^{-i a k_y } +\exp \left[ -i\left(\frac{\sqrt{3}}{2}k_x-\frac{1}{2}k_y\right)a \right] + \exp \left[ -i\left(-\frac{\sqrt{3}}{2}k_x-\frac{1}{2}k_y\right)a \right]        
\end{equation*}
The resulting eigenmodes are plane-wave superpositions of local spin deviations, created by $\hat{a }_\mathbf{k} ^\dagger$
The spin wave appears in the structure of the eigenmodes
\begin{equation*}
    a_{k}^ \dagger\lvert 0\rangle = \frac{1}{\sqrt{N}} \sum_{i} e^{-i\mathbf{k}\cdot\mathbf{R}_{i}}\,a_{i}^ \dagger\lvert 0\rangle
\end{equation*}
These modes correspond to collective excitations of the spin system, known as spin waves or magnons in the quantized description.

\subsubsection{Derivation.}
Even in this case, the spin operator satisfy the usual commutation relations
\begin{equation*}
\left[S_i^{\alpha}, S_j^{\beta}\right] = i\,\delta_{ij}\,\epsilon_{\alpha\beta\gamma}\,S_i^{\gamma}    
\end{equation*}
Here, $\delta_{ij }$ enforces that different sites commute.
As it the case with the ladder operator
\begin{equation*}
    S_i^{+} = S_i^{x} + iS_i^{y} 
    \qquad S_i^{-} = S_i^{x} - iS_i^{y}
\end{equation*}
This also satisfies the usual relation
\begin{equation*}
    [S_i^z, S_i^\pm] = \pm S_i^\pm\qquad
    [S_i^+, S_i^-] = 2S_i^z
\end{equation*}

We now introduce the Holstein–Primakoff transformation
\begin{gather*}
    S_i^+ = \sqrt{2s}\left(1-\frac{a_i^\dagger a_i}{2s}\right)^{1/2}a_i\qquad
    S_i^- = \sqrt{2s}a_i^\dagger\left(1-\frac{a_i^\dagger a_i}{2s}\right)^{1/2}\\
    S_i^z = s-a_i^\dagger a_i
\end{gather*}
The transformation is constructed so that the spin commutation relations, under bosonic transformation, are exactly preserved.

The third transformation arises from matching the spectrum of $S^z$ with a boson number operator.
It can be derived from this relation
\begin{equation*}
    (S_i^z)^2 = s(s+1) - (S_i^x)^2 - (S_i^y)^2
\end{equation*}
After computing the square of $x$ and $y$ components operator
\begin{equation*}
    (S_i^z)^2 = s(s+1) - \frac{1}{2}\bigl(S_i^+ S_i^- + S_i^- S_i^+\bigr)
\end{equation*}
The products of ladder operators are calculated as
\begin{align*}
    S_i^+ S_i^-  
    & =  2s\left(1-\frac{n_i}{2s}\right)^{1/2} a_i a_i^\dagger\left(1-\frac{n_i}{2s}\right)^{1/2} =  2s\left(n_i + 1\right)\left(1 - \frac{n_i}{2s}\right)\\
    S_i^+ S_i^-  
    & =   \left(2s - n_i\right) (n_i+1) = 2 s n_i + 2 s - n_i^2 - n_i,
\end{align*}
and
\begin{equation*}
        S_i^- S_i^+ 
 =  2s\, a_i^\dagger\left(1-\frac{n_i}{2s}\right) a_i  
=  a_i^\dagger\left(2s a_i - n_i a_i\right) \\
 =     2s n_i - n_i ^2 + n_i  
\end{equation*}
Substituting back
\begin{align*}
    (S_i^z)^2 
    & =  s^2 +s - (2s n_i + s - n_i ^2 ) = s^2 - 2s n_i + n_i^2\\
    (S_i^z)^2 
    & = (s - n_i)^2\\
    S_i^z = \pm s - n_i
\end{align*}
The vacuum $n_i=0$ must correspond to the fully polarized state $S_i^z=+s$.
So we take the positive side 
\begin{equation*}
    S_i^z = s - n_i = s - a_i ^\dagger a_i
\end{equation*}

The dot product is evaluated as 
\begin{align*}
    \mathbf{S}_i \cdot \mathbf{S}_j 
    & = S_i^z S_j^z + \frac{1}{2}\bigl(S_i^+ S_j^- + S_i^- S_j^+\bigr)\\
    \mathbf{S}_i \cdot \mathbf{S}_j 
    & = s^2 - s a_i^\dagger a_i - s  a_j^\dagger a_j + a_i^\dagger a_i a_j^\dagger a_j\\
    &\qquad+ s\Bigg[\left(1-\frac{a_i^\dagger a_i}{2s}\right)^{1/2} a_i a_j^\dagger \left(1-\frac{a_j^\dagger a_j}{2s}\right)^{1/2}\\
    &\qquad\qquad+ a_i ^\dagger\left(1-\frac{a_i ^\dagger a_i}{2s}\right)^{1/2}\left(1-\frac{a_j ^\dagger a_j}{2s}\right)^{1/2} a_j
    \Bigg]
\end{align*}
Use binomial expansion
\begin{equation*}
    (1-x)^{1/2} = \sum_{n=0}^{\infty} \binom{1/2}{n}(-x)^n = 1 - \frac{x}{2} - \frac{x^2}{8} + \cdots
\end{equation*}
to rewrite the result as 
\begin{align*}
    \mathbf{S}_i \cdot \mathbf{S}_j 
    & = s^2 - s a_i^\dagger a_i - s  a_j^\dagger a_j + a_i^\dagger a_i a_j^\dagger a_j\\
    &\qquad+ s\Bigg[\left(1-\frac{a_i^\dagger a_i}{4s} - \dots\right)  a_i a_j^\dagger \left(1-\frac{a_j^\dagger a_j}{4s} - \dots\right) \\
    &\qquad\qquad+ a_i ^\dagger\left(1-\frac{a_i ^\dagger a_i}{4s} - \dots\right) \left(1-\frac{a_j ^\dagger a_j}{4s} - \dots\right)  a_j
    \Bigg]
\end{align*}
Under second order approximation
\begin{equation*}
    \mathbf{S}_i \cdot \mathbf{S}_j  = s^2 - s\big(a_i^\dagger a_i + a_j^\dagger a_j\big) + s\big(a_i a_j ^\dagger+ a_i^\dagger a_j\big)
\end{equation*}

Inserting this into the Hamiltionian
\begin{align*}
        H 
    & = \frac{J }{2} \sum_{\braket{ij }} \left[ s^2 - s(n_i+n_j) + s\big(a_i a_j ^\dagger+ a_i^\dagger a_j \big) \right] \\
    H & =  C + J s z \sum_i a_i ^\dagger a_i - Js\sum_{\langle i j\rangle} a_i^\dagger a_j 
\end{align*}
with $C$ being constant and $z$ being the coordination number.
For a fixed  site $i$, the sum runs over all its neighbors site $j$, the number of which is $z$.
Therefore, $n_i$ is counted $z$ times in the sum.

Next insert the Fourier transform 
\begin{equation*}
a_{\mathbf{k}} = \frac{1}{\sqrt{N}}\sum_{i} e^{\,i\mathbf{k}\cdot\mathbf{R}_{i}}a_{i}\qquad
a_{\mathbf{k}}^{\dagger} = \frac{1}{\sqrt{N}}\sum_{i} e^{-\,i\mathbf{k}\cdot\mathbf{R}_{i}}\,a_{i}^{\dagger}.
\end{equation*}
or more precisely, we use its inverse in terms of displacement vector $\boldsymbol{\delta}$
\begin{equation*}
a_i^\dagger = \frac{1}{\sqrt{N}}\sum_\mathbf{k} e^{i\mathbf{k}\cdot\mathbf{R}_i} a_\mathbf{k}^\dagger\qquad
a_{i+\boldsymbol{\delta}} = \frac{1}{\sqrt{N}}\sum_\mathbf{k} e^{-i\mathbf{k}\cdot(\mathbf{R}_i+\boldsymbol{\delta})} a_\mathbf{k}
\end{equation*}
The product of creation and annihilation operator is 
\begin{align*}
       \sum_{\langle i j\rangle} a_i^\dagger a_j 
    & =  \frac{1}{N} \sum_{\langle i j\rangle} \sum_{\mathbf{k},\mathbf{k}'} e^{i\mathbf{k}\cdot\mathbf{R}_i}\,e^{-i\mathbf{k}'\cdot(\mathbf{R}_i+\boldsymbol{\delta})}\,a_{\mathbf{k}}^{\dagger}a_{\mathbf{k}'}\\
    & =  \frac{1}{N} \sum_{\mathbf{k},\mathbf{k}'}\sum_i\sum_{\boldsymbol{\delta}} e^{i(\mathbf{k}-\mathbf{k}')\cdot\mathbf{R}_i}\, e^{-i\mathbf{k}'\cdot\boldsymbol{\delta}}\, a_{\mathbf{k}}^{\dagger} a_{\mathbf{k}'}\\
    & =  \sum_{\mathbf{k}} \left(\sum_{\boldsymbol{\delta}} e^{-i \mathbf{k}\cdot \boldsymbol{\delta}}\right) a_{\mathbf{k}}^{\dagger} a_{\mathbf{k}}
\end{align*}
The Hamiltonian now reads 
\begin{equation*}
    H = C +  \sum_{\mathbf{k}} Js\left[z - \left(\sum_{\boldsymbol{\delta}} e^{-i \mathbf{k}\cdot \boldsymbol{\delta}}\right) \right] a_{\mathbf{k}}^\dagger a_{\mathbf{k}}
\end{equation*}
Defining 
\begin{equation*}
    \hbar \omega_{\mathbf{k }} = Js\left[z - g_\mathbf{k }  \right]
    \qquad
    g_\mathbf{k } = \sum_{\boldsymbol{\delta}} e^{-i \mathbf{k}\cdot \boldsymbol{\delta}} 
\end{equation*}
we can also write 
\begin{equation*}
    H = C +  \sum_{\mathbf{k}}\hbar \omega_{\mathbf{k }}a_{\mathbf{k}}^\dagger a_{\mathbf{k}}
\end{equation*}

In spin chain, each site has two nearest neighbors, so $\boldsymbol{\delta}= \pm a$ and 
\begin{equation*}
g_\mathbf{k} = e^{-ika}+e^{ika}=2\cos(ka)
\end{equation*}
For graphene, each site has three nearest neighbors which are not collinear.
Defining
\begin{equation*}
    \boldsymbol{\delta}_1 = a(0,1)\quad
    \boldsymbol{\delta}_2 = a\left(\frac{\sqrt{3}}{2},-\frac{1}{2}\right)\quad
    \boldsymbol{\delta}_3 = a\left(-\frac{\sqrt{3}}{2},-\frac{1}{2}\right)
\end{equation*}
and $\mathbf{k} = (k_x,k_y)$.  
Then 
\begin{equation*}
    g_{\mathbf{k}} = e^{-i a k_y } +\exp \left[ -i\left(\frac{\sqrt{3}}{2}k_x-\frac{1}{2}k_y\right)a \right] + \exp \left[ -i\left(-\frac{\sqrt{3}}{2}k_x-\frac{1}{2}k_y\right)a \right]
\end{equation*}
\end{document}