\documentclass[../../../main.tex]{subfiles}
\begin{document}
\subsection{Vector Potential}
The Coulomb gauge definition of vector potential $\nabla \cdot  \mathbf{A}=0$ constraint the vector to only the transversal (perpendicular) to the wave vector $\mathbf{k}$.
This can be seen by considering a complex monochromatic plane wave $\mathbf{A}(\mathbf{r},t)=\mathbf{A}_0 e^{i(\mathbf{k}\cdot \mathbf{r }-\omega t)}$.
Under Coulomb gauge
\begin{equation*}
  \nabla  \cdot \mathbf{A}=  \nabla \cdot  \mathbf{A}_0  e^{i(k \cdot \mathbf{r} - \omega t)} = \mathbf{A}_0 \cdot (i \mathbf{k}) e^{i(k \cdot \mathbf{r} - \omega t)} = \mathbf{k } \cdot \mathbf{A} = 0
\end{equation*}
This complex monochromatic plane wave is valid solution to wave equation that the vector potential obey.

We can expand the vector potential $\mathbf{A}(r, t)$ as a Fourier series of monochromatic plane waves.
\begin{equation*}
  \mathbf{A}(\mathbf{r}, t)
  = \sum_{\mathbf{k},s} A_{\mathbf{k} s}(t) \frac{e^{i \mathbf{k} \cdot \mathbf{r}}}{\sqrt{V}} \boldsymbol{\epsilon}_{\mathbf{k} s}
\end{equation*}
It follows from  classical electrodynamics that the vector potential is a real vector field $\mathbf{A} = \mathbf{A}^*$.
Choosing real polarization vectors $\boldsymbol{\epsilon}_{\mathbf{k} s}=\epsilon ^*_{\mathbf{k} s}$
\begin{equation*}
  \mathbf{A}(\mathbf{r},t) = \sum_{\mathbf{k},s} A^*_{\mathbf{k} s}(t)  \frac{e^{-i \mathbf{k} \cdot \mathbf{r}}}{\sqrt{V}}\boldsymbol{\epsilon}_{\mathbf{k} s}
  = \sum_{\mathbf{k},s} A^*_{-\mathbf{k} s}(t)  \frac{e^{i \mathbf{k} \cdot \mathbf{r}}}{\sqrt{V}}\boldsymbol{\epsilon}_{\mathbf{k} s}
\end{equation*}
where we relabel $\mathbf{k} \rightarrow -\mathbf{k}$.
Consequently $A_{-\mathbf{k},s}=A^*_{\mathbf{k},s}$.
Thus, we can sum the series over independent $\mathbf{k}$
\begin{equation*}
  \mathbf{A}(\mathbf{r}, t) = \sum_{\mathbf{k},s} \left[ A_{\mathbf{k}s}(t) \frac{e^{i\mathbf{k} \cdot \mathbf{r}}}{\sqrt{V}} + A_{\mathbf{k}s}^*(t) \frac{e^{-i\mathbf{k} \cdot \mathbf{r}}}{\sqrt{V}} \right] \boldsymbol{\epsilon}_{\mathbf{k}s}
\end{equation*}
where the complex plane waves $e^{i \mathbf{k } \cdot \mathbf{r}}$ normalized in a volume $V$ are the basis functions of the expansion, and $\boldsymbol{\epsilon}_{\mathbf{k}s}$ are mutually orthogonal real unit vectors of polarization which are also orthogonal to $\mathbf{k}$.
Note that the first representation count over all possible $\mathbf{k}$: both $\mathbf{k}$ and $-\mathbf{k}$ are included; meanwhile the second only the representation $\left\{ \mathbf{k},-\mathbf{k} \right\} $ are included.

Aside, it is called the Coulomb gauge because it would produce the Coulomb potential.
Start form the gauge $\nabla \cdot \mathbf{A}=0$, then consider the electric field enforced by the gauge
\begin{equation*}
  \mathbf{E}= -\nabla \phi+\frac{\partial \mathbf{A }}{\partial T}=-\nabla \phi
\end{equation*}
Then take the divergence
\begin{equation*}
  \nabla \cdot \mathbf{E }= -\nabla ^2 \phi
\end{equation*}
According to Gauss law
\begin{equation*}
  \nabla ^2 \phi=-\frac{\rho(\mathbf{r},t )}{\epsilon_0}
\end{equation*}
which is the Poisson equation whose solution is the Coulomb potential
\begin{equation*}
  \phi(\mathbf{r},t)=\frac{1}{4\pi \epsilon_0}\int\frac{1}{\rcurs}\rho(\mathbf{r}',t)d\tau'
\end{equation*}
where $\mathbf{r}$ is the field point (point in space where you are evaluating), $\mathbf{r}'$ is the source point (the location in space of an element of charge), and $\rcurs$ as the distance between source and field point.

\subsubsection{Wave equation.}
Each mode amplitude $A_{\mathbf{k}s}(t)$ behaves exactly like a classical harmonic oscillator due to $\mathbf{A}(\mathbf{r},t)$ obeying the wave equation that yield harmonic oscillator differential equation, whose solution is $A_{\mathbf{k}s}(t)=A_{\mathbf{k}s}(0)e^{i\omega_kt}$.
This can be proven by
\begin{align*}
  \left( \nabla^2 - \frac{1}{c^2} \frac{\partial^2}{\partial t^2} \right)    \sum_{\mathbf{k},s} A_{\mathbf{k} s}(t) \frac{e^{i \mathbf{k} \cdot \mathbf{r}}}{\sqrt{V}} \boldsymbol{\epsilon}_{\mathbf{k} s}
   & = 0  \\
  \sum_{\mathbf{k },s} \left[ -k^2 A_{\mathbf{k }s}(t) - \frac{1}{c^2} \frac{d^2 }{dt^2}A_{\mathbf{\mathbf{k}s}}(t) \right] \frac{e^{i \mathbf{k }\cdot \mathbf{r}}}{\sqrt{V} \epsilon_{\mathbf{k }s}}
   & =  0
\end{align*}
Each mode is independent, so
\begin{equation*}
  \frac{d^2 }{dt^2 }A_{\mathbf{k }s}(t)+\omega_k^2A_{\mathbf{A }s}(t)=0
\end{equation*}
with $\omega_k=ck$, which have the complex solutions
\begin{equation*}
  A_{\mathbf{k }s }(0)e^{-\omega_kt}
\end{equation*}

\subsection{Fock State}
The operators $\hat{a}_{\mathbf{k }s }$ and $\hat{a }_{\mathbf{k }s}$ act in Fock space $\mathcal{F}$.
A generic state of this Fock space F is given by
\begin{equation*}
  \ket{\left\{ n_{\mathbf{k }s} \right\} }
  = \ket{n_{\mathbf{k} s}n_{\mathbf{k}'s'}n_{\mathbf{k}''s''} \cdots }
  =\bigotimes_{\mathbf{k },s} \ket{n_{\mathbf{k }s}}
\end{equation*}
where there are \( n_{\mathbf{k} s} \) photons with wavevector \( \mathbf{k} \) and polarization \( s \), \( n_{\mathbf{k}'s'} \) photons with wavevector \( \mathbf{k}' \) and polarization \( s' \), \( n_{\mathbf{k}''s''} \) photons with wavevector \( \mathbf{k}'' \) and polarization \( s'' \), et cetera.
For example, the state $\ket{ 0_{\mathbf{k} s} 1_{\mathbf{k}'s'}  2_{\mathbf{k}''s''}}$.
Here, the entire mode $\mathbf{k},s$ is in vacuum or no photon exist; mode $\mathbf{k'},s'$ has one photon; and mode $\mathbf{k}'',s''$ has two.

The Fock space \( \mathcal{F} \) is given by
\begin{equation*}
  \mathcal{F} = \mathcal{H}_0 \oplus \mathcal{H}_1 \oplus \mathcal{H}_2 \oplus \mathcal{H}_3 \oplus \cdots = \bigoplus_{n=0}^{\infty} \mathcal{H}_n = \bigoplus_{n=0}^{\infty} \mathcal{H}^{\otimes n}
\end{equation*}
where 
\begin{equation*}
\mathcal{H}^{\otimes n}  =
\underbrace{\mathcal{H} \otimes \dots \otimes \mathcal{H}}_n = 
\bigotimes_n \mathcal{H}
\end{equation*}
is the Hilbert space of $n$ identical photons, which is $n$ times the tensor product of the single-photon Hilbert space $\mathcal{H}$.
The Fock subspace for boson and fermion does not contain all the space defined, rather its symmetrization and antisymmetrization respectively
\begin{equation*}
  \mathcal{F}_B = \bigoplus_{n=0}^{\infty} \mathrm{Sym}^n(\mathcal{H}) \qquad 
  \mathcal{F}_F = \bigoplus_{n=0}^{\infty} \wedge^n(\mathcal{H})
\end{equation*}
Notice that in the definition of the Fock space $\mathcal{F}$ one must include the space $\mathcal{H}_0 = \mathcal{H}^{\otimes 0}$, which is the Hilbert space of 0 photons, containing only the vacuum state
\begin{equation*}
  \ket{0}
  = \ket{0_{\mathbf{k} s}0_{\mathbf{k}'s'}\cdots }
  =\bigotimes_{\mathbf{k },s} \ket{0_{\mathbf{k }s}}
\end{equation*}

\subsubsection{Ladder operator.}
If there are exactly $n$ photons in this polarized monochromatic wave $\omega=\omega_k=c|\mathbf{k}|$ the Fock state of the system is given by
\begin{equation*}
  \ket{n }= \frac{1 }{\sqrt{n !}}\left( \hat{a }^\dagger \right) ^n \ket{0}
\end{equation*}
or more precisely
\begin{equation*}
  \ket{n_{\mathbf{k }s} }= \frac{1 }{\sqrt{n_{\mathbf{k }s}!}}\left( \hat{a }^\dagger_{\mathbf{k }s} \right) ^{n_{\mathbf{k }s}} \ket{0}
\end{equation*}
This can be generalized into  multimode state
\begin{equation*}
  \ket{\left\{ n_{\mathbf{k }s}  \right\} }
  =\prod_{\mathbf{k },s} \frac{1 }{\sqrt{n_{\mathbf{k }s}!}}\left( \hat{a }^\dagger_{\mathbf{k }s} \right) ^{n_{\mathbf{k }s}} \ket{0}
\end{equation*}

To prove this, we define unnormalized state
\begin{equation*}
  \ket{n'_{\mathbf{k }s}}=\hat{a}^\dagger_{\mathbf{k }s} \ket{0}
\end{equation*}
and use the relations
\begin{gather*}
  \hat{a}_{\mathbf{k }s} (\hat{a}^\dagger_{\mathbf{k }s} )^n
  = (\hat{a}^\dagger_{\mathbf{k }s} )^n a +n (\hat{a}^\dagger_{\mathbf{k }s} )^{n-1} \\
  \hat{a}_{\mathbf{k }s} ^n(\hat{a}^\dagger_{\mathbf{k }s}) ^n \ket{0}= n! \ket{0}
\end{gather*}

First let us use induction to prove said relation.
With both being the induction hypothesis, our base case $n$ is the commutator relation
\begin{equation*}
  \hat{a}_{\mathbf{k }s} \hat{a}^\dagger_{\mathbf{k }s} =\hat{a}^\dagger_{\mathbf{k }s} \hat{a}_{\mathbf{k }s} +1
\end{equation*}
We prove for $n+1$ by considering
\begin{align*}
  \hat{a}_{\mathbf{k }s} (\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}+1}
                                                                 &
  = \hat{a}_{\mathbf{k }s} (\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}} \hat{a}^\dagger_{\mathbf{k }s}
  =[(\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}} a +{n_{\mathbf{k }s}} (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}-1}]\hat{a}^\dagger_{\mathbf{k }s}                                                    \\
                                                                 &
  = (\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}} \hat{a}_{\mathbf{k }s} \hat{a}^\dagger_{\mathbf{k }s}+ {n_{\mathbf{k }s}} (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}-1}\hat{a}^\dagger_{\mathbf{k }s} \\
                                                                 &
  =  (\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}} (\hat{a}^\dagger_{\mathbf{k }s}  \hat{a}_{\mathbf{k }s} +1)+{n_{\mathbf{k }s}} (\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}}                             \\
  \hat{a}_{\mathbf{k }s} (\hat{a}^\dagger_{\mathbf{k }s} )^{n+1} & =
  (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}+1}\hat{a}_{\mathbf{k }s} + ({n_{\mathbf{k }s}}+1)(\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}}
\end{align*}
which is our hypothesis for ${n_{\mathbf{k }s}} \to {n_{\mathbf{k }s}}+1$.
The action of this relation is as follows
\begin{equation*}
  \hat{a}_{\mathbf{k }s} (\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}} \ket{0}
  =(\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}} a +{n_{\mathbf{k }s}} (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}-1}   \ket{0}= {n_{\mathbf{k }s}} (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}-1}\ket{0}
\end{equation*}
Next we use this relation, which has been proven, to prove the second relation.
Using induction again, we consider base case $n$ as
\begin{equation*}
  (\hat{a}_{\mathbf{k }s} )^0 (\hat{a}^\dagger_{\mathbf{k }s} )^0 \ket{0} = \ket{0}=0!\ket{0}
\end{equation*}
It holds, then for $n+1$ consider
\begin{equation*}
  \hat{a}_{\mathbf{k }s} (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}+1} \ket{0}
  = ({n_{\mathbf{k }s}}+1) (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}}\ket{0}
\end{equation*}
then apply $\hat{a}_{\mathbf{k }s} ^{n_{\mathbf{k }s}}$ along with the second hypothesis
\begin{align*}
  (\hat{a}_{\mathbf{k }s})^{{n_{\mathbf{k }s}}+1} (\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}+1} \ket{0}
   & =  ({n_{\mathbf{k }s}}+1) (\hat{a}_{\mathbf{k }s} )^{n_{\mathbf{k }s}}(\hat{a}^\dagger_{\mathbf{k }s} )^{{n_{\mathbf{k }s}}}\ket{0} \\
   & = ({n_{\mathbf{k }s}}+1){n_{\mathbf{k }s}}! \ket{0}=({n_{\mathbf{k }s}}+1)\ket{0}
\end{align*}
It holds once more.
We now back at normalizing the state $\ket{{n_{\mathbf{k }s}}'}$ by taking the inner product and inserting the normalizing constant
\begin{equation*}
  \alpha^2\braket{{n_{\mathbf{k }s}}' | {n_{\mathbf{k }s}}'}=\alpha \braket{0 | \hat{a}_{\mathbf{k }s} ^{n_{\mathbf{k }s}} (\hat{a}^\dagger_{\mathbf{k }s} )^{n_{\mathbf{k }s}}|0}={n_{\mathbf{k }s}}!\\
  \alpha=\frac{1 }{\sqrt{{n_{\mathbf{k }s}}!}}
\end{equation*}
Thus the normalized state
\begin{equation*}
  \ket{{n_{\mathbf{k }s}}}=\alpha \ket{{n_{\mathbf{k }s}}'}= \frac{1 }{\sqrt{{n_{\mathbf{k }s}}! }}(\hat{a}^\dagger_{\mathbf{k }s}   )^{n_{\mathbf{k }s}} \ket{0}
\end{equation*}

For the multimode state, we can start by
\begin{equation*}
  \ket{\left\{ n_{\mathbf{k }s} \right\} } = \bigotimes_{\mathbf{k }s}\ket{n_{\mathbf{k }s}}=\bigotimes_{\mathbf{k }s}\frac{1 }{\sqrt{{n_{\mathbf{k }s}}! }}(\hat{a}^\dagger_{\mathbf{k }s}   )^{n_{\mathbf{k }s}} \ket{0}
\end{equation*}
Using
\begin{equation*}
  \bigotimes_i c_i \ket{n_i}= \left( \prod_i c_i  \right) \bigotimes_i \ket{n_i}
\end{equation*}
yields
\begin{equation*}
  \ket{\left\{ n_{\mathbf{k }s}  \right\} }
  =\prod_{\mathbf{k },s} \frac{1 }{\sqrt{n_{\mathbf{k }s}!}}\left( \hat{a }^\dagger_{\mathbf{k }s} \right) ^{n_{\mathbf{k }s}} \bigotimes_{\mathbf{k }s}\ket{0}
  =\prod_{\mathbf{k },s} \frac{1 }{\sqrt{n_{\mathbf{k }s}!}}\left( \hat{a }^\dagger_{\mathbf{k }s} \right) ^{n_{\mathbf{k }s}} \ket{0}
\end{equation*}

\subsubsection{(In)Coherent state.}
By using the number operator, one obtain
\begin{equation*}
  \hat{N}_{\mathbf{k }s} | \cdots n_{\mathbf{k }s} \cdots \rangle = n_{\mathbf{k }s}  | \cdots n_{\mathbf{k }s}  \cdots \rangle
\end{equation*}
Viewed in this light, the Fock state is the eigenstate of number operator and has a definite photon number, read: eigenvalue.

Despite this, the Fock state has no coherent phase and thus unable to properly interference.
This result can be seen by considering the expectation value of electromagnetic field.
Notice that
\begin{equation*}
  \hat{\mathbf{E}} \propto \sum_{\mathbf{k},s} \left( \hat{a}_{\mathbf{k }s} -\hat{a}^\dagger_{\mathbf{k }s}  \right) \quad
  \hat{\mathbf{B}} \propto \sum_{\mathbf{k},s} \left( \hat{a}_{\mathbf{k }s} -\hat{a}^\dagger_{\mathbf{k }s}  \right)
\end{equation*}
However, the operators change the occupation number of that mode and produce a state orthogonal to the original one
\begin{align*}
  \braket{\left\{ n_{\mathbf{k }s} \right\}   | \hat{a}_{\mathbf{k }s} |\left\{ n_{\mathbf{k }s} \right\} }
   & =   \sqrt{n_{\mathbf{k }s}} \braket{\left\{ n_{\mathbf{k }s} \right\}  | \left\{ n_{\mathbf{k }s} \right\} -1_{\mathbf{k }s}} =0     \\
  \braket{\left\{ n_{\mathbf{k }s} \right\}  | \hat{a}^\dagger_{\mathbf{k }s}  |\left\{ n_{\mathbf{k }s} \right\} }
   & =   \sqrt{n_{\mathbf{k }s}+1} \braket{\left\{ n_{\mathbf{k }s} \right\}  | \left\{ n_{\mathbf{k }s} \right\} + 1_{\mathbf{k }s}} = 0
\end{align*}
Thus
\begin{equation*}
  \braket{\left\{ n_{\mathbf{k }s} \right\}  | \hat{\mathbf{E }}|\left\{ n_{\mathbf{k }s} \right\} }=0\qquad
  \braket{\left\{ n_{\mathbf{k }s} \right\}  | \hat{\mathbf{B }}|\left\{ n_{\mathbf{k }s} \right\} }=0
\end{equation*}
The vanishing result does not mean the field is absent, it means that the average electromagnetic field amplitude is zero and field fluctuates symmetrically about zero.
The vanishing result thus can be seen as a consequence of undefined phase of Fock space.

The square of the field is different case, however.
With the fields written as
\begin{align*}
  \hat{\mathbf{E}}^2 & \propto \sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \left( -\hat{a}_{\mathbf{k }s}\hat{a}_{\mathbf{k }'s'} +\hat{a}_{\mathbf{k }s} \hat{a}^\dagger_{\mathbf{k }'s'} +\hat{a}^\dagger_{\mathbf{k }s} \hat{a}_{\mathbf{k }'s'}  -\hat{a}^\dagger_{\mathbf{k }s} \hat{a}^\dagger_{\mathbf{k }'s'}  \right) \\
  \hat{\mathbf{B}}^2 & \propto \sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \left( -\hat{a}_{\mathbf{k }s}\hat{a}_{\mathbf{k }'s'} +\hat{a}_{\mathbf{k }s} \hat{a}^\dagger_{\mathbf{k }'s'} +\hat{a}^\dagger_{\mathbf{k }s} \hat{a}_{\mathbf{k }'s'}  -\hat{a}^\dagger_{\mathbf{k }s} \hat{a}^\dagger_{\mathbf{k }'s'}  \right)
\end{align*}
where we have inserted the factor $i$.
Along with
\begin{gather*}
  \sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \braket{\hat{a}_{\mathbf{k }s}   \hat{a}_{\mathbf{k }'s'} }=0                        \\
  \sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \braket{\hat{a}_{\mathbf{k }s}   \hat{a}^\dagger_{\mathbf{k }'s'} }=\sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \delta_{\mathbf{k}\mathbf{k'}}\delta_{ss'}(n_{\mathbf{k }s}+1)= \sum_{\mathbf{k},s}(n_{\mathbf{k }s}+1) \\
  \sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \braket{\hat{a}^\dagger_{\mathbf{k }s}=   \hat{a}_{\mathbf{k }'s'} } \sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \delta_{\mathbf{k}\mathbf{k'}}\delta_{ss'}n_{\mathbf{k }s}=\sum_{\mathbf{k},s} n_{\mathbf{k }s} \\
  \sum_{\mathbf{k},s}\sum_{\mathbf{k}',s'} \braket{\hat{a}^\dagger_{\mathbf{k }s}   \hat{a}^\dagger_{\mathbf{k }'s'} }=0
\end{gather*}
the expectation value now can be evaluated as
\begin{equation*}
  \braket{\left\{ n_{\mathbf{k }s} \right\}  | \hat{\mathbf{E }}^2|\left\{ n_{\mathbf{k }s} \right\} }\propto \sum_{\mathbf{k},s}(2 n_{\mathbf{k }s}+1)
  \qquad
  \braket{\left\{ n_{\mathbf{k }s} \right\}  | \hat{\mathbf{B }}^2|\left\{ n_{\mathbf{k }s} \right\} }\propto \sum_{\mathbf{k},s} (2 n_{\mathbf{k }s}+1)
\end{equation*}
or with all terms inserted
\begin{align*}
  \braket{\left\{ n_{\mathbf{k }s} \right\}  | \hat{\mathbf{E }}^2|\left\{ n_{\mathbf{k }s} \right\} } & =  \sum_{\mathbf{k},s} \frac{\hbar \omega_k }{\epsilon_0 V}\left( 2n_{\mathbf{k }s}+1\right)
  \\
  \braket{\left\{ n_{\mathbf{k }s} \right\}  | \hat{\mathbf{B }}^2|\left\{ n_{\mathbf{k }s} \right\} } & =  \sum_{\mathbf{k},s} \frac{\hbar \omega_k \mu_0}{V}\left( 2n_{\mathbf{k }s}+1 \right)
\end{align*}
\begin{equation*}
\end{equation*}
We can insert this into classical Hamiltonian
\begin{align*}
  H & =   \int d^3 \mathbf{r}  \left( \frac{\epsilon_0}{2} \mathbf{E}^2 + \frac{1}{2\mu_0} \mathbf{B}^2 \right)        \\
    & = \int d^3 \mathbf{r } \sum_{\mathbf{k},s} \left[ \frac{\hbar  \omega_k }{V }\left( n_{\mathbf{k }s}+\frac{1 }{2 } \right)  \right] \\
  H & = \sum_{\mathbf{k},s} \hbar \omega_k \left( n_{\mathbf{k }s}+\frac{1 }{2} \right)
\end{align*}
This result match the quantum Hamiltonian
\begin{align*}
  \braket{\left\{ n_{\mathbf{k }s} \right\} |H|\left\{ n_{\mathbf{k }s} \right\} }
   & =
  \left\langle \left\{ n_{\mathbf{k }s} \right\} \Bigg| \sum_{\mathbf{k},s} \hbar \omega_k \left( \hat{N }_{\mathbf{k} s }+ \frac{1 }{2} \right)\Bigg|\left\{ n_{\mathbf{k }s} \right\}  \right\rangle \\
  \braket{H}
   & =  \sum_{\mathbf{k},s} \hbar \omega_k \left( n_{\mathbf{k }s} +\frac{1 }{2} \right)
\end{align*}
\begin{equation*}
\end{equation*}
This mean that the field have definite energy despite not having definite phase.
The fact that the energy is definite despite the field fluctuates is because both energy and phase are conjugate variables in the quantum.
This field fluctuation reflects uncertainty in phase.

\subsection{Identical Particle}
Before imposing indistinguishability, an $N$-particle state is written as 
\begin{equation*}
  |k_1, k_2, \ldots, k_N\rangle = |k_1\rangle \otimes \cdots \otimes |k_N\rangle
\end{equation*}
This state is not symmetric in general. 
If we exchange two slots,
\begin{equation*}
  \mathcal{T}_{12}|k_1, k_2, \ldots \rangle = |k_2, k_1, \ldots \rangle
\end{equation*}
we obtain is a different vector.

Indistinguishability implies that the Hamiltonian cannot change if the degrees of freedom of two arbitrary particles $i$ and $j$ are exchanged
\begin{equation*}
  {H } = {H} (\dots,i\dots,j,\dots) = {H} (\dots,j\dots,i,\dots)
\end{equation*}
This can be seen by acting with the operator exchanging two arbitrary particles, $i$ and $j$, on a state of $N$ identical particles
\begin{equation*}
  \mathcal{T }_{ij} \ket{\dots, \phi_i,\dots,\phi_j,\dots} = \ket{\dots, \phi_j,\dots,\phi_i,\dots} 
\end{equation*}
which produces a state that may not be physically different from the original state, so that there can only be a phase factor $\nu_{ij }=e ^{i\alpha_{ij}}$
\begin{equation*}
  \mathcal{T }_{ij} \ket{\dots, \phi_i,\dots,\phi_j,\dots} = \nu_{ij }\ket{\dots, \phi_i,\dots,\phi_j,\dots} 
\end{equation*}
Moreover, because of $\mathcal{T}_{ij }=\mathcal{T}_{ji}$ we have
\begin{equation*}
  \mathcal{T}_{ij }^{2 }=1\qquad\nu_{ij }=\pm1
\end{equation*}
These results imply that there are only two types of quantum particles
\begin{equation*}
  \nu = \begin{cases}
    +1,& \text{ particles whose symmetrical under particle exchange}\\
    -1,& \text{ particles whose antisymmetrical under particle exchange}
  \end{cases}
\end{equation*}

\subsubsection{Boson.}
Consider the state
\begin{equation*}
  |k_1, \ldots, k_N\rangle = |k_1\rangle \otimes |k_2\rangle \otimes \cdots \otimes |k_N\rangle
\end{equation*}
The subscript in $\ket{k_n}$ labels the one-particle state in that tensor slot.
In order to produce physical multiparticle boson state, where the particles are truly indistinguishable, we introduce symmetrization $S$ for a fixed number $N$ of particles
\begin{equation*}
  S |k_1, \ldots, k_N \rangle = 
  \frac{1}{\sqrt{N!N_1! N_1! \ldots N_M!}}
  \sum_{p \in S_N} |k_{p(1)}, \ldots, k_{p(N)} \rangle 
\end{equation*}
which satisfy $\nu=1$.
The symmetrization operator  $S$ acts on the tensor-product slots, not on the physical particles themselves, where it rearranges the positions of the one-particle states in the tensor product
\begin{equation*}
  |k_1, k_2, \ldots, k_N\rangle \rightarrow |k_{p(1)}, k_{p(2)}, \ldots, k_{p(N)}\rangle
\end{equation*}

The is run over $p$ all permutations $p$ of the set $\mathcal{N}=\left\{ 1,\dots,N \right\} $, which are $N!$ element, hence the $1/\sqrt{N!}$ normalization constant.
The symmetric group on $N$ elements $S_N$ is defined as 
\begin{equation*}
  S_N = \left\{ \sigma:\mathcal{N} \rightarrow \mathcal{N} |\varsigma \text{ is bijective}  \right\} 
\end{equation*}
A function $f: A \to B$ is said to be bijective if $A$ goes to exactly one element of $B$ and $B$ is hit by exactly one element of $A$.

Now suppose that $N_l$ particle occupy $k_l$ state.
Many permutations now produce identical terms, since swapping two particles that are both in $k_l$  does not change the vector, hence $1/\sqrt{N_l!}$ normalization constant.

Each term is the original tensor-product state with tensor slots rearranged according to $p$, such that $\ket{\dots k_{p(n)}\dots}$ is placed in slot $n$.
For example, with $p(n)=n+1$, the state $S\ket{k_1}$ gets mapped into 
\begin{equation*}
  \ket{k_{{(1)}}\dots} \mapsto \ket{\dots \ket{k_2}\dots}
\end{equation*}

\subsubsection{Fermion.}
With the same state $|k_1, \ldots, k_N\rangle $, the antisymmetrization is defined as 
\begin{equation*}
A|k_1,k_2,\ldots,k_N\rangle = \frac{1}{\sqrt{N!}} \sum_{p} (-1)^{P} |k_{i_1},k_{i_2},\ldots,k_{i_N}\rangle
\end{equation*}
As the case with the symmetrization operator, the sum is run over $p$ all permutations $p$ of the set $\left\{ 1,\dots,N \right\} $.
The only difference is in the parity factor 
\begin{equation*}
  (-1) ^{P(p)} = 
  \begin{cases}
    +1& \text{ Even permutations}\\
    -1& \text{ Odd permutations}
  \end{cases}
\end{equation*}
This factor that the state antisymmetry under particle exchange.
Since any permutation $p$ of $N$ slots can be written as a product of transpositions
\begin{equation*}
  p = \mathcal{T}_{i_1j_1} \mathcal{T}_{i_2j_2} \ldots\mathcal{T}_{i_mj_m}.
\end{equation*}
the parity of the permutation is determined by the number of transpositions $m$ in this decomposition: even $m$ for $+1$ and odd $m$ for $-1$.

This parity is the origin of Pauli exclusion principle.
The probability for a many-particle state to contain two or more Fermions in the same single-particle state vanishes.
In another important contribution, Wolfgang Pauli (1940) proved by his famous spin-statistics theorem that Bosons carry integer spin, $s=1,\dots$ , while Fermions carry half-integer spin, $s = 1/2, \dots$.

|\subsubsection{The application.}
The symmetric and antisymmetrical operator is used to construct boson and fermion subspace from the $n $-particle Hilbert space
\begin{equation*}
\mathcal{H}^{\otimes n}  =
\underbrace{\mathcal{H} \otimes \dots \otimes \mathcal{H}}_n = 
\bigotimes_n \mathcal{H}
\end{equation*}
The symmetric subspace is defined as the set of all vectors invariant under permutation of slots
\begin{equation*}
  \mathrm{Sym}^n(\mathcal{H}) = \left\{ |\Psi\rangle \in \mathcal{H}^{\otimes n} \mid P|\Psi\rangle = |\Psi\rangle \text{ for all permutations } P \right\}
\end{equation*}
Equivalently,
\begin{equation*}
  \mathrm{Sym}^n(\mathcal{H}) = S\mathcal{H}^{\otimes n}
\end{equation*}
where the symmetrization projector action is
\begin{equation*}
  S = \frac{1}{n!} \sum_{p \in S_n} P
\end{equation*}
Meanwhile, the antisymmetrical subspace is defined as the set of vectors that change sign under odd permutations
\begin{equation*}
  \wedge^n(H) = \left\{ |\Psi\rangle \in \mathcal{H}^{\otimes n} \,|\, P |\Psi\rangle = \mathrm{sgn}(P) |\Psi\rangle \right\}
\end{equation*}
Equivalently,
\begin{equation*}
  \wedge^n(H) = A \mathcal{H}^{\otimes n}
\end{equation*}
with the action of antisymmetrization as 
\begin{equation*}
A = \frac{1}{n!} \sum_{p \in S_n} \text{sgn}(p) P
\end{equation*}

With these in mind, the Fock subsspace for both boson and fermion can be derived from the full Fock space as 
\begin{equation*}
  \mathcal{F}_B = \bigoplus_{n=0}^{\infty} \mathrm{Sym}^n(\mathcal{H}) \qquad 
  \mathcal{F}_F = \bigoplus_{n=0}^{\infty} \wedge^n(\mathcal{H})
\end{equation*}
\end{document}