\documentclass[../../../main.tex]{subfiles}
\begin{document}
In framework of many-body system, the fundamental object is the many-body wavefunction
\[
  \Psi(x_1,\ldots,x_N)
  =\Psi(\mathbf{r}_1,\sigma_1\dots,\mathbf{r}_N,\sigma_N)
\]
where the generalized coordinate $x = (\mathbf{r}, \sigma)$ not only takes into account the spatial coordinate $\mathbf{r}$ but also the intrinsic spin $\sigma$ pertaining to the particle.
The state of the system therefore lives in the tensor product Hilbert space $\mathcal{H}^{\otimes N}$.
For identical particles, the wavefunction must satisfy permutation symmetry,
\begin{equation*}
  \Psi(\ldots, x_i, \ldots, x_j, \ldots) = \pm \Psi(\ldots, x_j, \ldots, x_i, \ldots)
\end{equation*}

When the particle number becomes macroscopic $  N \rightarrow O(10^{23})$ and the system is described only through macroscopic observable rather than the full wavefunction, one replaces the pure state description $\Psi(x_1,\ldots,x_N)$ with an ensemble or density operator
\begin{equation*}
  \rho = \frac{e^{-\beta H}}{Z}, \quad Z = \text{Tr} \; e^{-\beta H}.
\end{equation*}
This quantum statistical mechanics step corresponds to assuming statistical equilibrium with a reservoir (canonical ensemble) or fixed energy (microcanonical ensemble).

Thermodynamics emerges when an additional limit is taken
\begin{equation*}
  N \to \infty, \quad V \to \infty, \quad \frac{N}{V} = \text{const.}
\end{equation*}
In this regime microscopic fluctuations become negligible compared with macroscopic averages.
Observables become smooth functions of intensive variables such as \(T, P,\) and \(\rho\).
Thermodynamic relations follow from derivatives of the free energy
\begin{equation*}
  F = -k_B T \ln Z, \quad U = -\frac{\partial}{\partial \beta} \ln Z
\end{equation*}
For example
\begin{equation*}
  S = -\left( \frac{\partial F}{\partial T} \right)_V, \quad P = -\left( \frac{\partial F}{\partial V} \right)_T
\end{equation*}
Thermodynamic quantities are obtained from the partition function,

Solid-state theory arises when the many-body system satisfies essential conditions
\begin{enumerate}
  \item The particles form a dense phase (typically electrons and ions).
  \item The ions form an approximately periodic lattice
        \begin{equation*}
          V(\mathbf{r} + \mathbf{R}) = V(\mathbf{r})
        \end{equation*}
        where \(\mathbf{R}\) is a Bravais lattice vector. In this condition, eigenstates satisfy Bloch's theorem $\psi_{nk}(\mathbf{r}) = e^{i \mathbf{k} \cdot \mathbf{r}} u_{nk}(\mathbf{r})$
  \item The electronic states can be treated in an effective single-particle framework due to screening and mean-field approximations.
\end{enumerate}

The many-body problem is then approximated by quasiparticles (electrons, phonons, magnons) moving in effective potentials.
Techniques such as Hartree–Fock, density functional theory, or Fermi liquid theory implement this reduction.

\subsection{One-particle Operator}
A one-particle operator  is an operator acting independently on each particle in a many-particle system.
For a system of $N$ particles with generalized coordinates $\mathbf{x}_i$ a general one-particle operator $\hat{O}_1$ has the form of sum over operators $\hat{o } ^{(1)}$, which acts on one particle
\begin{equation*}
  \hat{O}_1 = \sum_{i } \hat{o } ^{(1)}_{i}(\mathbf{x}_i)
\end{equation*}
For a system with many particles, this representation becomes inconvenient because every term must refer to a specific particle coordinate $\mathbf{x_i}$.
Second quantization introduce
\begin{equation*}
  \hat{O}_1 = \sum_{ij} \langle 1_i | \hat{o } ^{(1)} | 1_j \rangle \hat{a}_i^\dagger \hat{a}_j
\end{equation*}
with $\ket{\left\{ 1_i \right\}  }$ as one-particle basis whose creation and annihilation operators are related to other of the one-particle basis $\ket{\left\{ 1_j \right\} }$.
In the position basis, the matrix element can be written as
\begin{equation*}
  \langle 1_i|\hat{o } ^{(1)}|1_j\rangle = \int d^3 \mathbf{r} d^3 \mathbf{r}' u^*_{i}(\mathbf{r}) \langle \mathbf{r}|\hat{o } ^{(1)}|\mathbf{r}'\rangle u_j(\mathbf{r}')
\end{equation*}
As such, the representation in position basis reads 
\begin{equation*}
  \hat{O}_1 
  = \int d^3r\;d^3r'\; \psi^\dagger(\mathbf{r}) \langle \mathbf{r}|\hat{o}^{(1)}|\mathbf{r}'\rangle \psi(\mathbf{r}')
\end{equation*}

Assuming the operator $\hat{o} ^{(1)}$ is local
\begin{equation*}
  \langle \mathbf{r}|\hat{o}^{(1)}|\mathbf{r}'\rangle  = \hat{o } ^{(1)}(\mathbf{r },\mathbf{p})\delta(\mathbf{r }-\mathbf{r}')
\end{equation*}
the matrix elements turns diagonal
\begin{equation*}
  \langle 1_i|\hat{o } ^{(1)}|1_j\rangle = \int d^3 \mathbf{r} \;u^*_{i}(\mathbf{r}) \hat{o }^{1}(\mathbf{r},\mathbf{p}) u_j(\mathbf{r}')
\end{equation*}
and the representation is 
\begin{equation*}
  \hat{O}_1 = \int d^3r\;\psi^\dagger(\mathbf{r}) \langle \mathbf{r}|\hat{o}^{(1)}|\mathbf{r}\rangle \psi(\mathbf{r})
\end{equation*}

This representation has the following advantage.
\begin{enumerate}
  \item \textbf{Number particle independence.} The indices $(i,j)$ label single-particle basis states, computations are therefore performed in the space of orbitals. Consequently the complexity is controlled by the size of the one-particle basis rather than by the dimensionality of the $N$-particle wavefunction.
  \item \textbf{Straightforward basis transformation.} Changing the single-particle basis corresponds simply to a unitary transformation of the operators.
\end{enumerate}

\subsubsection{Example: particle density}
The particle density
\begin{equation*}
  \rho(\mathbf{r}) = \psi^\dagger(\mathbf{r})\psi(\mathbf{r}) = \sum_{\mathbf{k},\mathbf{k}'} \braket{\mathbf{k}|\mathbf{r} }\braket{\mathbf{r}|\mathbf{k}'} \hat{a}_\mathbf{k}^\dagger \hat{a}_{\mathbf{k'}}
\end{equation*}
has the Fourier transform of
\begin{equation*}
  \rho(\mathbf{q}) = \sum_{\mathbf{k}} \hat{a}_\mathbf{k}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}}= \sum_{\mathbf{k}} \hat{a}_{\mathbf{k}-\mathbf{q}/2}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}/2}
\end{equation*}
The many-body definition of this operator is 
\begin{equation*}
  \rho(\mathbf{r}) = \sum_{i=1}^{N} \delta\bigl(\mathbf{r}-\mathbf{r}'_{i}\bigr)
\end{equation*}
Its action can by considering the spatial integral of the function, which is expected to give value only if $\mathbf{r} $ is at particle position $\mathbf{r}'$.
In the momentum eigenstate, the second quantization reads
\begin{equation*}
  \rho (\mathbf{r}) = \frac{1 }{V }\sum_{\mathbf{q }} e ^{i \mathbf{q }\cdot \mathbf{r }}n _{\mathbf{q}} 
\end{equation*}

The transformation is as follows.
\begin{align*}
  \rho(\mathbf{q})
   & = \int d^3r\;e^{-i\mathbf{q}\cdot\mathbf{r}}\;\rho(\mathbf{r})                                                                                                          \\
   & =  \sum_{\mathbf{k},\mathbf{k}'}\left(\int d^3r\;e^{i(\mathbf{k}'-\mathbf{k})\cdot\mathbf{r}}e^{-i\mathbf{q}\cdot\mathbf{r}}\right) \hat{a}_\mathbf{k}^\dagger \hat{a}_{\mathbf{k}'} \\
   & =  \sum_{\mathbf{k},\mathbf{k}'} \delta (\mathbf{k}'-\mathbf{k}-\mathbf{q})   \hat{a}_\mathbf{k}^\dagger \hat{a}_{\mathbf{k}'} \\
   & = \sum_{\mathbf{k}} \hat{a}_\mathbf{k}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}}= 
   \sum_{\mathbf{k}} \hat{a}_{\mathbf{k}-\mathbf{q}/2}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}/2}
\end{align*}
Where the last line is obtained by index relabelling $\mathbf{k} \rightarrow \mathbf{k}-\mathbf{q}/2$.

Next is the quantization.
The matrix elements reads
\begin{equation*}
  \braket{\mathbf{k }' | \delta(\mathbf{r }-\mathbf{r }) |\mathbf{k}}
  =\frac{1}{V}\int d^3r'\; e^{-i\mathbf{k}'\cdot\mathbf{r}'}\delta(\mathbf{r}-\mathbf{r}')e^{i\mathbf{k}\cdot\mathbf{r}'} = \frac{1 }{V } e ^{i(\mathbf{k }'-\mathbf{k  })\cdot \mathbf{r}}
\end{equation*}
Then  substituting back 
\begin{equation*}
  \rho(\mathbf{r})
  = \frac{1 }{V } \sum_{\mathbf{k},\mathbf{k}'}  e ^{i(\mathbf{k }'-\mathbf{k  })\cdot \mathbf{r}} a ^\dagger _{\mathbf{k }' } a_{\mathbf{k}} 
 =\frac{1 }{V }\sum_{\mathbf{q }} e ^{i \mathbf{q }\cdot \mathbf{r }}n _{\mathbf{q}} 
\end{equation*}

\subsubsection{Example: particle current.}
The particle current, defined as
\begin{equation*}
  \mathbf{j}(\mathbf{r}) = -\frac{i}{2m}\left[\psi^\dagger(\mathbf{r})[\nabla\psi(\mathbf{r})] - [\nabla\psi^\dagger(\mathbf{r})]\;\psi(\mathbf{r})\right]
\end{equation*} 
has the Fourier transform of 
\begin{equation*}
  j(\mathbf{q}) 
= \frac{1}{m}\sum_{\mathbf{k}} \left( \mathbf{k}+\frac{\mathbf{q } }{2} \right)  \hat{a}_{\mathbf{k}}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}} 
= \frac{1}{m}\sum_{\mathbf{k}} \mathbf{k}\; \hat{a}_{\mathbf{k}-\mathbf{q}/2}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}/2}
\end{equation*}

The derivation is as follows
\begin{align*}
\mathbf{j}(\mathbf{r}) 
&= -\frac{i}{2m}\sum_{\mathbf{k},\mathbf{k}'}\Big[ \hat{a}_\mathbf{k}^\dagger e^{-i\mathbf{k}\cdot\mathbf{r}}\nabla \hat{a}_{\mathbf{k}'} e^{i\mathbf{k}'\cdot\mathbf{r}}-\big(\nabla  \hat{a}_\mathbf{k}^\dagger e^{-i\mathbf{k}\cdot\mathbf{r}}\big)\cdot \hat{a}_{\mathbf{k}'}e^{i\mathbf{k}'\cdot\mathbf{r}}\Big] \\
&= -\frac{i}{2m}\sum_{\mathbf{k},\mathbf{k}'}\Big[ \hat{a}_\mathbf{k}^\dagger e^{-i\mathbf{k}\cdot\mathbf{r}}\big(i\mathbf{k}'\;a_{\mathbf{k}'}e^{i\mathbf{k}'\mathbf{r}}\big)
-\big(-i\mathbf{k}\;a_\mathbf{k}^\dagger e^{-i\mathbf{k}\cdot\mathbf{r}}\big)\cdot \hat{a}_{\mathbf{k}'}e^{i\mathbf{k}'\cdot\mathbf{r}}\Big] \\
&= \frac{1}{2m}\sum_{\mathbf{k},\mathbf{k}'}(\mathbf{k}+\mathbf{k}')\;a_\mathbf{k}^\dagger \hat{a}_{\mathbf{k}'}\;e^{i(\mathbf{k}'-\mathbf{k})\cdot\mathbf{r}}
\end{align*}
Then apply the transformation
\begin{align*}
j(\mathbf{q}) &= \int d^3r\; e^{-i\mathbf{q}\cdot\mathbf{r}}\; j(\mathbf{r})
= \frac{1}{2m}\sum_{\mathbf{k},\mathbf{k}'} (\mathbf{k}+\mathbf{k}')\; \hat{a}_{\mathbf{k}}^\dagger \hat{a}_{\mathbf{k}'} \int d^3r\; e^{i(\mathbf{k}'-\mathbf{k}-\mathbf{q})\cdot\mathbf{r}}\\
& =  \frac{1}{2m}\sum_{\mathbf{k},\mathbf{k}'} (\mathbf{k}+\mathbf{k}')\; \hat{a}_{\mathbf{k}}^\dagger \hat{a}_{\mathbf{k}'} \delta(\mathbf{k}'-\mathbf{k }-\mathbf{q})\\
&= \frac{1}{2m}\sum_{\mathbf{k}} (\mathbf{k}+(\mathbf{k}+\mathbf{q}))\; \hat{a}_{\mathbf{k}}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}} 
= \frac{1}{2m}\sum_{\mathbf{k}} (2\mathbf{k}+\mathbf{q})\; \hat{a}_{\mathbf{k}}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}} \\
j(\mathbf{q}) 
&= \frac{1}{m}\sum_{\mathbf{k}} \left( \mathbf{k}+\frac{\mathbf{q } }{2} \right)  \hat{a}_{\mathbf{k}}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}} 
= \frac{1}{m}\sum_{\mathbf{k}} \mathbf{k}\; \hat{a}_{\mathbf{k}-\mathbf{q}/2}^\dagger \hat{a}_{\mathbf{k}+\mathbf{q}/2}
\end{align*}
where the last line is obtained by index shift $\mathbf{k}\rightarrow \mathbf{k}-\mathbf{q}/2$.

\subsubsection{Example: position operator.}
Position operator, defined as $\hat{o }^{(1)}=\mathbf{\hat{r}}$, has the one-particle operator form of $\mathbf{R} = \hat{O}_1$.
We evaluated the expression in position basis
\begin{equation*}
  \mathbf{R} = \int d^3r\;d^3r'\; \langle \mathbf{r}|\hat{\mathbf{r}} |\mathbf{r}'\rangle\psi^\dagger(\mathbf{r})\psi(\mathbf{r}')
  = \int d^3r\;\mathbf{r}\;\psi^\dagger(\mathbf{r})\psi(\mathbf{r}) 
\end{equation*}

\subsubsection{Example: linear momentum operator.}
The one-particle operator of linear momentum $P$ has the representation in momentum eigenstate $\ket{\left\{ \mathbf{k} \right\} }$ and position eigenstate $\ket{\left\{ \mathbf{r} \right\} }$ as
\begin{equation*}
  \mathbf{P}
  = \sum_{\mathbf{k }} \mathbf{k}  \hat{a}^\dagger_{\mathbf{k }} \hat{a}_{\mathbf{k }}    
  =-i \int d^{3}r\; \psi^{\dagger}(\mathbf{r})[\nabla\psi(\mathbf{r})]
\end{equation*}

The derivation in momentum eigenstate is
\begin{equation*}
  \mathbf{P} = \sum_{\mathbf{k },\mathbf{k}'} \braket{\mathbf{k } | \mathbf{p }|\mathbf{k}'} \hat{a}^\dagger_{\mathbf{k }} \hat{a}_{\mathbf{k }'}    
  = \sum_{\mathbf{k },\mathbf{k}'} \mathbf{k}' \delta_{\mathbf{k}\mathbf{k}'} \hat{a}^\dagger_{\mathbf{k }} \hat{a}_{\mathbf{k }'}    
  = \sum_{\mathbf{k }} \mathbf{k}  \hat{a}^\dagger_{\mathbf{k }} \hat{a}_{\mathbf{k }}    
\end{equation*}
while in position eigenstate
\begin{equation*}
  \mathbf{P}
  = \int d^3r\;\psi^\dagger(\mathbf{r}) \langle \mathbf{r}| \mathbf{p} |\mathbf{r}\rangle \psi(\mathbf{r})
 =-i   \int d^3r\;d^3r'\;\psi^\dagger(\mathbf{r})\delta(\mathbf{r}-\mathbf{r'}) [\nabla   \psi(\mathbf{r}')]
\end{equation*}
and the Dirac function collapse the primed integral.

\subsubsection{Example: one-particle Hamiltonian.}
Consider the one–particle Hamiltonian
\begin{equation*}
  \hat{h} = \frac{\hat{\mathbf{p}}^{2}}{2m} + V(\mathbf{r})
\end{equation*}
In the momentum eigenbasis, the one-particle operator reads
\begin{equation*}
  H = \sum_{\mathbf{k}} \frac{\mathbf{k}^{2}}{2m} a_{\mathbf{k}}^{\dagger} a_{\mathbf{k}}    + \sum_{\mathbf{k} \mathbf{k}'} V_{\mathbf{q}} a_{\mathbf{k} + \mathbf{q}}^{\dagger} a_{\mathbf{k}}
\end{equation*}
with $V_{\mathbf{q}}$ as Fourier component of the spatial potential that scatters a particle from momentum $\mathbf{k}'$ to $\mathbf{k}$ with momentum transfer $\mathbf{q}=\mathbf{k}-\mathbf{k}'$
\begin{equation*}
  V_\mathbf{q} = \frac{1 }{V } \int d^3r\; e^{- i\mathbf{q }\cdot \mathbf{r}} V(\mathbf{r})
\end{equation*}
From the action of annihilation and creation operator, it can also be interpreted that $a_{\mathbf{k}} $ annihilate particle with momentum $\mathbf{k }$, then particle with momentum $\mathbf{k}+\mathbf{q}$ is created by $a_{\mathbf{k }+\mathbf{q}}$.
In the position eigenbasis
\begin{equation*}
  H = \int d^3r\; \psi^\dagger(\mathbf r)\left(-\frac{1}{2m}\nabla^2 + V(\mathbf r)\right)\psi(\mathbf r)
\end{equation*}

The derivation in position eigenstate is quite straightforward since the Hamiltonian is local in position representation.
For the momentum eigenstate, the kinetic term  reads  
\begin{equation*}
    K=\frac{1 }{2m} \sum_{\mathbf{k},\mathbf{k}'} \langle k|\hat{\mathbf{p}}^2 |k'\rangle a^\dagger_{\mathbf{k}} a_{\mathbf{k}'} = \sum_{\mathbf{k}} \frac{k^2}{2m} a^\dagger_{\mathbf{k}} a_{\mathbf{k}}
\end{equation*}
For the potential term 
\begin{equation*}
  V = \sum_{\mathbf{k},\mathbf{k}'} \langle \mathbf{k}|V(\mathbf{r})|\mathbf{k}'\rangle  a_{\mathbf{k}}^\dagger a_{\mathbf{k}'}
\end{equation*}
We evaluate the element in position representation, since the wavefunction is known to be the plane wave 
\begin{align*}
    \langle \mathbf{k}|V(\mathbf{r})|\mathbf{k}'\rangle &= \frac{1}{V}\int d^3r\;e^{-i(\mathbf{k}-\mathbf{k}')\cdot\mathbf{r}}V(\mathbf{r})\\
    V_{\mathbf{k} - \mathbf{k}'} = V_{\mathbf{q}} &= \frac{1}{V}\int d^3r\;e^{-i\mathbf{q}\cdot\mathbf{r}}V(\mathbf{r})
\end{align*}
This is just Fourier transform of the potential.

\subsubsection{Example: Spin operator.}
For a system of $N$ electrons
\begin{equation*}
  \mathbf{S} = \sum_{i=1}^{N} \mathbf{S}_i
\end{equation*}
where $\mathbf{S }$ act on particle $i$.
Let $\mathbf{S}=(S_x,S_y,S_z)$, then the second quantization version is 
\begin{equation*}
  \mathbf{S} = \frac{\hbar}{2}\sum_{k}\Bigl(\bigl[c_{\mathbf{k}\uparrow}^\dagger c_{\mathbf{k}\downarrow}+c_{\mathbf{k}\downarrow}^\dagger c_{\mathbf{k}\uparrow}\,\bigr],
i\bigl[c_{\mathbf{k}\downarrow}^\dagger c_{\mathbf{k}\uparrow}-c_{\mathbf{k}\uparrow}^\dagger c_{\mathbf{k}\downarrow}\bigr], 
\bigl[c_{\mathbf{k}\uparrow}^\dagger c_{\mathbf{k}\uparrow}-c_{\mathbf{k}\downarrow}^\dagger c_{\mathbf{k}\downarrow}\bigr]\Bigr)
\end{equation*}
More generally
\begin{equation*}
  \mathbf{\hat{S}} = \frac{\hbar}{2}\sum_{\mathbf{k}}\sum_{\sigma,\sigma'} a^\dagger_{\mathbf{k}\sigma}\boldsymbol{\sigma}_{\sigma\sigma'}a_{\mathbf{k}\sigma'}
\end{equation*}
where $\boldsymbol{\sigma}_{\sigma\sigma'} = \braket{\sigma  | \boldsymbol{\sigma }|\sigma'}$ is the matrix element in $\ket{\mathbf{k }\sigma}$ basis.

The derivation start with recognizing $\mathbf{S }= \hbar \boldsymbol{\sigma }/2$.
Insert into the general one-body operator formula to obtain the general form
\begin{equation*}
  \mathbf{\hat{S} } 
  = \sum_{\mathbf{k}\sigma} \sum_{\mathbf{k}'\sigma'}  \langle \mathbf{k}\sigma|\mathbf{\hat{S}}|\mathbf{k}'\sigma'\rangle a^\dagger_{\mathbf{k}\sigma} a_{\mathbf{k}'\sigma'} 
  = \sum_{\mathbf{k}}\sum_{\sigma,\sigma'} \frac{\hbar}{2}\boldsymbol{\sigma}_{\sigma\sigma'} a^\dagger_{\mathbf{k}\sigma} a_{\mathbf{k}\sigma'}
\end{equation*}
The explicit component is evaluated using these components of Pauli matrices
\begin{equation*}
    \sigma_1 =
    \begin{bmatrix}
        0 & 1 \\
        1 & 0
    \end{bmatrix}
    \quad
    \sigma_2 =
    \begin{bmatrix}
        0 & -i \\
        i & 0
    \end{bmatrix}
    \quad
    \sigma_3    =
    \begin{bmatrix}
        1 & 0  \\
        0 & -1
    \end{bmatrix}
\end{equation*}a
In spin $1/2$, all elements is evaluated as 
\begin{equation*}
  \sigma_n = 
\begin{bmatrix}
\langle\uparrow|\sigma_n|\uparrow\rangle & \langle\uparrow|\sigma_n|\downarrow\rangle\\[6pt]
\langle\downarrow|\sigma_n|\uparrow\rangle & \langle\downarrow|\sigma_n|\downarrow\rangle
\end{bmatrix}.
\end{equation*}
and the rest is trivial.

\subsubsection{Derivation: second quantization representation.}
First consider the action of $\hat{o} ^{1}$ on one-particle basis $\ket{\left\{ 1_\alpha \right\} }$, which we assume as its eigenstate
\begin{equation*}
  \hat{o } ^{(1)}\ket{1_\alpha } =  \omega_\alpha \ket{1_\alpha}
\end{equation*}
Recall that the one-particle operator $\hat{O }_1$ is defined as the sum of this operator.
Hence, its action on this basis is
\begin{equation*}
  \hat{O }_1 =  \sum_{\alpha } \omega_\alpha n_\alpha = \sum_{\alpha } \omega_\alpha \hat{a}_\alpha ^\dagger \hat{a}_\alpha
\end{equation*}
The one-particle operator is also diagonal in its basis, hence we can write the eigenvalue as the matrix element
\begin{equation*}
  \hat{O }_1
  = \sum_{\alpha } \braket{1_\alpha  | \hat{o } ^{(1)}| 1_\alpha} \hat{a}_\alpha ^\dagger \hat{a}_\alpha
\end{equation*}
Transform into arbitrary one-particle basis by using the completeness relations
\begin{multline*}
    \hat{o }_1
  =\sum_{i,j}  \sum_{\alpha } \braket{1_\alpha  | 1_i} \braket{1_i | \hat{o } ^{(1)}|1_j   } \braket{1_j  | 1_\alpha} \hat{a}_\alpha ^\dagger \hat{a}_\alpha\\
  =\sum_{i,j}  \sum_{\alpha } \braket{1_i | \hat{o } ^{(1)}|1_j   } \delta_{\alpha i} \hat{a}_\alpha ^\dagger \delta_{\alpha j}a_\alpha
  =\sum_{i,j}  \ \braket{1_i | \hat{o } ^{(1)}|1_j   }  \hat{a}_i ^\dagger a_j
\end{multline*}
\begin{equation*}
\end{equation*}
The $\alpha$ index collapse, then the representation is obtained.

\subsection{Two-particle operator}
A general two-particle operator is
\begin{equation*}
  \hat{O }_2 = \sum_{ij } \hat{o }_{ij }^{(2)}
\end{equation*}
where the sum runs over all pairs of particles.
The second quantized act in the abstract two-particle basis
\begin{equation*}
  \hat{O}_2 = \sum_{i,j,m,n} \braket{1_i 1_j  | \hat{o} ^{(2)}| 1_m 1_n } \hat{a}^\dagger_{i}  \hat{a}^\dagger_{j} \hat{a}_n \hat{a}_m
\end{equation*}
Note the reversed order of the indices $n$ and $m$ of the pair of annihilation operators as compared to their order in the matrix elements, which we adopt that due to Fermions antisymmetry.
This is imposed to enforce that the operator ordering $a_na_m$ exactly removes the particles in states $m$ and $n$ without producing an additional minus sign.

In the position basis, the expression reads
\begin{equation*}
  \hat{O}_2 = \int d^3 \mathbf{r}_1 \; d^3 \mathbf{r}_1' \; d^3 \mathbf{r}_2 \; d^3 \mathbf{r}_2' \; \psi^\dagger(\mathbf{r}_1) \psi(\mathbf{r}_1') \langle \mathbf{r}_1, \mathbf{r}_1' | \hat{o}^{(2)} | \mathbf{r}_2, \mathbf{r}_2' \rangle \psi(\mathbf{r}_2') \psi(\mathbf{r}_2)
\end{equation*}
If $\hat{O }_2$ is diagonal
\begin{equation*}
  \langle \mathbf{r}_1, \mathbf{r}_1' | \hat{O}^{(2)} | \mathbf{r}_2, \mathbf{r}_2' \rangle = \hat{O}^{(2)}(\mathbf{r}_1, \mathbf{r}_1') \delta(\mathbf{r}_1 - \mathbf{r}_2) \delta(\mathbf{r}_1' - \mathbf{r}_2')
\end{equation*}
the expression reduces further
\begin{equation*}
  \hat{O}_2 = \int d^3 \mathbf{r} d^3 \mathbf{r}' \; \psi^\dagger(\mathbf{r}) \psi(\mathbf{r}') \hat{o}^{(2)}(\mathbf{r}, \mathbf{r}') \psi(\mathbf{r}') \psi(\mathbf{r})
\end{equation*}

Imposing translational invariance $\hat{o}^{(2)}(\mathbf{r}, \mathbf{r}') = \hat{o}^{(2)}(\mathbf{r} - \mathbf{r}')$, we obtain
\begin{align*}
  \hat{O}_2
   & =  \sum_{\mathbf{k}_1 \mathbf{k}_2 } \sum_{\mathbf{q}} \hat{o}^{(2)}(\mathbf{q}) \hat{a}_{\mathbf{k}_1}^\dagger \hat{a}_{\mathbf{k}_2}^\dagger \hat{a}_{\mathbf{k}_2+\mathbf{q}} \hat{a}_{\mathbf{k}_1-\mathbf{q}} \\
  \hat{O}_2
   & = \sum_{\mathbf{k}_1 \mathbf{k}_2 } \sum_{\mathbf{q}} \hat{o}^{(2)}(\mathbf{q}) \hat{a}_{\mathbf{k}_1+\mathbf{q}}^\dagger \hat{a}_{\mathbf{k}_2-\mathbf{q}}^\dagger \hat{a}_{\mathbf{k}_2} \hat{a}_{\mathbf{k}_1}
\end{align*}
where \( \hat{o}^{(2)}(\mathbf{q}) \) is the Fourier transform of \( \hat{o}^{(2)}(\mathbf{r}) \)
\begin{equation*}
  \hat{o}^{(2)}(\mathbf{q}) = \int d^3 \mathbf{r}\; \hat{o}^{(2)}(\mathbf{r}) e^{-i\mathbf{q} \cdot r}
  \qquad
  \begin{cases}
    \mathbf{r} = \mathbf{r}_1-\mathbf{r}_2\\
    \mathbf{q} = \mathbf{k}_1 + \mathbf{k}_1' \\
    \mathbf{q}= \mathbf{k}_2' - \mathbf{k}_2
  \end{cases}
\end{equation*}

\subsubsection{State order reversal.}
As stated before, the purpose of the reversed ordering is to ensure that the annihilation operators remove the particles in the ket in the same order in which they were created, thereby avoiding an additional fermionic sign.
To see this, consider the correctly ordered operators
\begin{align*}
a_n a_m \lvert 1_m 1_n\rangle 
&= a_n a_m a_m^\dagger a_n^\dagger \lvert 0\rangle,\\
& =  a_n(1 - a_m^\dagger a_m) a_n^\dagger \lvert 0\rangle \\
& =  (a_n a_n^\dagger -  a_m^\dagger a_m a_n^\dagger )  \lvert 0\rangle \\
& =  a_n a_n^\dagger   \lvert 0\rangle + a_m^\dagger a_n^\dagger a_m  \lvert 0\rangle \\
a_n a_m \lvert 1_m 1_n\rangle 
&= \lvert 0\rangle
\end{align*}
If the order was reversed, however
\begin{align*}
a_m a_n|1_m1_n\rangle 
&= a_m a_n a_m^\dagger a_n^\dagger |0\rangle\\
&= -a_m a_m^\dagger a_n a_n^\dagger|0\rangle\\
&= -\big(1-a_m^\dagger a_m\big)a_n a_n^\dagger|0\rangle\\
&= - a_n a_n^\dagger|0\rangle + a_m^\dagger a_m a_n a_n^\dagger|0\rangle\\
a_m a_n|1_m1_n\rangle&= -|0\rangle
\end{align*}
an extra negative sign was produced

\subsubsection{Example: Coulomb potential.}
Two-particle Coulomb interaction is 
\begin{equation*}
  \hat{o}^{(2)} 
  = \frac{e^2}{4\pi\varepsilon_0}\frac{1}{|{\mathbf r}_1-{\mathbf r}_2|} 
\end{equation*}
Then the second quantization of Coulomb potential is 
\begin{equation*}
  \hat{V}
  = \frac{1}{2}\sum_{i,j,m,n}V_{ijmn} a_i^\dagger a_j^\dagger a_n a_m 
\end{equation*}
with $u_i(\mathbf{r}_n) = \braket{\mathbf{r}_n  | 1_i}$ as the single particle orbital and factor $1/2$ to avoid double counting.
The derivation is quite straightforward, with the integral term 
\begin{equation*}
  V_{ijmn}
  = \int d^3r_1\;d^3r_2 u_i^*({\mathbf r}_1)u_j^*({\mathbf r}_2)\frac{e^2}{4\pi\varepsilon_0|{\mathbf r}_1-{\mathbf r}_2|}u_m({\mathbf r}_1)u_n({\mathbf r}_2)
\end{equation*}
as the matrix element of the Coulomb potential in that basis.

Writing in the momentum space, yields
\begin{align*}
  \hat{V } 
  & = \frac{1}{2V} \sum_{\mathbf{k}_1,\mathbf{k}_2,\mathbf{q}} V(\mathbf{q}) a_{\mathbf{k}_1+\mathbf{q}}^\dagger a_{\mathbf{k}_2-\mathbf{q}}^\dagger a_{\mathbf{k}_2} a_{\mathbf{k}_1}\\
  \hat{V } 
  & = \frac{1}{2V} \sum_{\mathbf{k}_1,\mathbf{k}_2,\mathbf{q}} \frac{e^2 }{\epsilon_0 q^2} a_{\mathbf{k}_1+\mathbf{q}}^\dagger a_{\mathbf{k}_2-\mathbf{q}}^\dagger a_{\mathbf{k}_2} a_{\mathbf{k}_1}
\end{align*}
\begin{equation*}
\end{equation*}
with $V(\mathbf{q})$ as the Fourier transform of the spatial Coulomb potential
\begin{equation*}
V(\mathbf{q }) 
= \int d^3r\;    \frac{e^2}{4\pi\varepsilon_0}\frac{1}{|{\mathbf r}_1-{\mathbf r}_2|}   
=\frac{e^2}{4\pi\varepsilon_0} \int d^3r\;    \frac{e ^{i \mathbf{q }\cdot \mathbf{r}}}{r}   
= \frac{e^2 }{\epsilon_0 q^2}
\end{equation*}

The integral evaluation is as follows
\begin{align*}
    I(q) & =  \int d^3 r \; \frac{e^{i \mathbf{q }\cdot \mathbf{ r }}}{r } \\
  & = \int_{0}^{\infty}dr\;r^{2}\int_{0}^{\pi}d\theta\;\sin\theta\int_{0}^{2\pi}d\phi\;\frac{1}{r}e^{iqr\cos\theta} \\
  I(q) & =  2\pi\int_{0}^{\infty}dr\;r\int_{0}^{\pi}d\theta\sin\theta e^{iqr\cos\theta}
\end{align*}
The second term can be evaluated by substituting $u = \cos \theta$ and $du = -\sin \theta\;d\theta$
\begin{equation*}
\int_{0}^{\pi} d\theta\;\sin\theta\;e^{iqr\cos\theta}
= \int_{-1}^{1} du\; e^{iqru}
= \frac{e^{iqr}-e^{-iqr}}{iqr}
= \frac{2\sin(qr)}{qr}
\end{equation*}
The integral now reads
\begin{equation*}
  I(q) 
  = \frac{4\pi}{q}\int_{0}^{\infty}dr\;\sin(qr)
\end{equation*}
This can be evaluated using Feynman's method of parameterization 
\begin{equation*}
  I(\epsilon) 
  = \int_{0 }^{\infty}dr\; e ^{(iq -\epsilon )r}
\end{equation*}
with real $e ^{-\epsilon r}$. 
Then, to evaluate the integral, we simply have to 
\begin{equation*}
  \int_{0}^{\infty}dr\;\sin(qr)  
  = \lim_{\epsilon \rightarrow 0} \mathrm{Im} \left(\int_{0 }^{\infty}dr\; e ^{(iq -\epsilon )r}\right) 
\end{equation*}
Evaluate the function
\begin{equation*}
  I(\epsilon)  
  =\left[-\frac{1}{\epsilon-iq}e^{-(\epsilon-iq)r}\right]_{0}^{\infty}
  =\frac{1}{\epsilon-iq}
  = \frac{\epsilon+iq }{\epsilon^2 + q^2}
\end{equation*}
Taking the imaginary component we obtain the integral value 
\begin{equation*}
  I(q) \frac{2\pi }{q }\frac{1 }{q } = \frac{4\pi }{q^2}
\end{equation*}
Multiplying this with the other Coulomb constant, we obtain the Fourier transform of the Coulomb potential. 


\subsubsection{Derivation: momentum representation.}
Translational invariance requires that shifting the entire system by a vector $\mathbf{a}$ leaves the interaction unchanged
\begin{equation*}
  V(\mathbf{r}_1+\mathbf{a},\mathbf{r}_2+\mathbf{a})=
  V(\mathbf{r}_1,\mathbf{r}_2)
\end{equation*}
The only functions satisfying this condition depend solely on the relative coordinate
\begin{equation*}
  V(\mathbf{r}_1,\mathbf{r}_2)
  =   V(\mathbf{r}_1-\mathbf{r}_2)
\end{equation*}
If the interaction is a pair potential depending only on the separation
\begin{equation*}
  \langle \mathbf{r}_1,\mathbf{r}_2 | \hat{o}^{(2)} | \mathbf{r}_1', \mathbf{r}_2' \rangle
  = \hat{o}^{(2)}(\mathbf{r}_1 - \mathbf{r}_2) \delta(\mathbf{r}_1 - \mathbf{r}_1') \delta(\mathbf{r}_2 - \mathbf{r}_2')
\end{equation*}
First we start with
\begin{equation*}
  \hat{O}_2 = \sum_{\mathbf{k}_1, \mathbf{k}_2} \sum_{\mathbf{k}_1' \mathbf{k}_2'}  \langle \mathbf{k}_1 \mathbf{k}_2 | \hat{o}^{(2)} | \mathbf{k}_2' \mathbf{k}_1' \rangle a ^\dagger _{\mathbf{k}_1} a ^\dagger _{\mathbf{k}_2 } a _{\mathbf{k}_2'} a _{\mathbf{k}_1'}
\end{equation*}
The element can be evaluated as
\begin{multline*}
  \langle \mathbf{k}_1 \mathbf{k}_2 | \hat{o}^{(2)} | \mathbf{k}_1' \mathbf{k}_2' \rangle \\
  = \int d^3 \mathbf{r}_1\; d^3 \mathbf{r}_2\; d^3 \mathbf{r}_{1}'\; d^3 \mathbf{r}_{2}'\; \langle \mathbf{k}_1 \mathbf{k}_2 | \mathbf{r}_1, \mathbf{r}_2 \rangle \langle \mathbf{r}_1, \mathbf{r}_2 | \hat{o}^{(2)} | \mathbf{r}_1', \mathbf{r}_2'\rangle\langle \mathbf{r}_1',\mathbf{r}_2' | \mathbf{k}_1' \mathbf{k}_2' \rangle
\end{multline*}
Then the integral reduces
\begin{multline*}
  \langle \mathbf{k}_1 \mathbf{k}_2 | \hat{o}^{(2)} | \mathbf{k}_1' \mathbf{k}_2' \rangle \\
  = \int d^3 \mathbf{r}_1\; d^3 \mathbf{r}_2\; \langle \mathbf{k}_1 \mathbf{k}_2 | \mathbf{r}_1, \mathbf{r}_2 \rangle \langle \mathbf{r}_1, \mathbf{r}_2 | \hat{o}^{(2)} | \mathbf{r}_1, \mathbf{r}_2\rangle\langle \mathbf{r}_1,\mathbf{r}_2 | \mathbf{k}_1' \mathbf{k}_2' \rangle
\end{multline*}
In this composite state,  the plane wave representation reads as
\begin{equation*}
  \langle \mathbf{r}_1,\mathbf{r}_2 | \mathbf{k}_1 \mathbf{k}_2 \rangle
  = \frac{1 }{\sqrt{V}}  e ^{i(\mathbf{k}_1 \cdot  \mathbf{r}_1+\mathbf{k}_2 \cdot  \mathbf{r}_2)}
\end{equation*}
Substituting back
\begin{equation*}
  \frac{1}{V} \int d^3 \mathbf{r}_1 d^3 \mathbf{r}_2 \hat{o}^{(2)}(\mathbf{r}_1 -\mathbf{r}_2) e^{-i(\mathbf{k}_1 - \mathbf{k}_1') \cdot \mathbf{r}_1} e^{-i(\mathbf{k}_2 -\mathbf{k}_2') \cdot \mathbf{r}_2}
\end{equation*}
Introduce new coordinates
\begin{equation*}
  \begin{cases}
    \mathbf{R }=\mathbf{r }_1 +\mathbf{r}_2 \\
    \mathbf{r }=\mathbf{r }_1 -\mathbf{r}_2
  \end{cases}
  \qquad
  \text{or}
  \qquad
  \begin{cases}
    \mathbf{r}_1=\mathbf{R } +\mathbf{r} \\
    \mathbf{r}_2=\mathbf{R } -\mathbf{r}
  \end{cases}
\end{equation*}
Rewrite the exponent as
\begin{align*}
  (\mathbf{k}_1 - \mathbf{k}_1') \cdot \mathbf{r}_1 + (\mathbf{k}_2 - \mathbf{k}_2') \cdot \mathbf{r}_2
   & =  (\mathbf{k}_1 + \mathbf{k}_2 - \mathbf{k}_1' - \mathbf{k}_2') \cdot \mathbf{R }                     \\
   & \qquad+ \left[ (\mathbf{k}_1 - \mathbf{k}_1') - (\mathbf{k}_2 - \mathbf{k}_2') \right]\cdot \mathbf{r} \\
  (\mathbf{k}_1 - \mathbf{k}_1') \cdot \mathbf{r}_1 + (\mathbf{k}_2 - \mathbf{k}_2') \cdot \mathbf{r}_2
   & = \mathbf{p }\cdot \mathbf{R }+ \mathbf{q }\cdot \mathbf{r}
\end{align*}
such that the integral separates
\begin{align*}
  \langle \mathbf{k}_1 \mathbf{k}_2 | \hat{o}^{(2)} | \mathbf{k}_1' \mathbf{k}_2' \rangle
   & = \frac{1 }{V}  \int d^3 R \; e^{-i \mathbf{p}\cdot \mathbf{R}} \int d^3 \mathbf{r}\; \hat{o}^{(2)}(\mathbf{r}) e^{-i \mathbf{q} \cdot \mathbf{r}} \\
  \langle \mathbf{k}_1 \mathbf{k}_2 | \hat{o}^{(2)} | \mathbf{k}_1' \mathbf{k}_2' \rangle
   & =  \delta (\mathbf{p}) \int d^3 \mathbf{r}\; \hat{o}^{(2)}(\mathbf{r}) e^{-i \mathbf{q} \cdot \mathbf{r}}
\end{align*}
The delta function enforce $\mathbf{k }_1+\mathbf{k }_2=\mathbf{k }_1'+\mathbf{k }_2'$, so the definition of $\mathbf{q}$ simplifies and the integral reads
\begin{equation*}
  \langle \mathbf{k}_1 \mathbf{k}_2 | \hat{o}^{(2)} | \mathbf{k}_1' \mathbf{k}_2' \rangle
  =
  \int d^3 \mathbf{r}\; \hat{o}^{(2)}(\mathbf{r}) e^{-i \mathbf{q} \cdot \mathbf{r}}
  \qquad
  \begin{cases}
    \mathbf{q} = \mathbf{k}_1 +\mathbf{k}_1' \\
    \mathbf{q}= \mathbf{k}_2' - \mathbf{k}_2
  \end{cases}
\end{equation*}

\subsection{Identical Particle}
Before imposing indistinguishability, an $N$-particle state is written as
\begin{equation*}
  |\mathbf{k}_1, \mathbf{k}_2, \ldots, \mathbf{k}_N\rangle = |\mathbf{k}_1\rangle \otimes \ldots \otimes |\mathbf{k}_N\rangle
\end{equation*}
This state is not symmetric in general.
If we exchange two slots,
\begin{equation*}
  \mathcal{T}_{12}|\mathbf{k}_1, \mathbf{k}_2, \ldots \rangle = |\mathbf{k}_2, \mathbf{k}_1, \ldots \rangle
\end{equation*}
we obtain a different vector.

Indistinguishability implies that the Hamiltonian cannot change if the degrees of freedom of two arbitrary particles $i$ and $j$ are exchanged
\begin{equation*}
  {H } = {H} (\dots,i\dots,j,\dots) = {H} (\dots,j\dots,i,\dots)
\end{equation*}
This can be seen by acting with the operator exchanging two arbitrary particles, $i$ and $j$, on a state of $N$ identical particles
\begin{equation*}
  \mathcal{T }_{ij} \ket{\dots, \phi_i,\dots,\phi_j,\dots} = \ket{\dots, \phi_j,\dots,\phi_i,\dots}
\end{equation*}
which produces a state that may not be physically different from the original state, so that there can only be a phase factor $\nu_{ij }=e ^{i\alpha_{ij}}$
\begin{equation*}
  \mathcal{T }_{ij} \ket{\dots, \phi_i,\dots,\phi_j,\dots} = \nu_{ij }\ket{\dots, \phi_i,\dots,\phi_j,\dots}
\end{equation*}
Moreover, because of $\mathcal{T}_{ij }=\mathcal{T}_{ji}$ we have
\begin{equation*}
  \mathcal{T}_{ij }^{2 }=1\qquad\nu_{ij }=\pm1
\end{equation*}
These results imply that there are only two types of quantum particles
\begin{equation*}
  \nu = \begin{cases}
    +1, & \text{ particles whose symmetrical under particle exchange}     \\
    -1, & \text{ particles whose antisymmetrical under particle exchange}
  \end{cases}
\end{equation*}

\subsubsection{Boson.}
Consider the state
\begin{equation*}
  |k_1, \ldots, k_N\rangle = |k_1\rangle \otimes |k_2\rangle \otimes \ldots \otimes |k_N\rangle
\end{equation*}
The subscript in $\ket{k_n}$ labels the one-particle state in that tensor slot.
In order to produce physical multiparticle boson state, where the particles are truly indistinguishable, we introduce symmetrization $S$ for a fixed number $N$ of particles
\begin{equation*}
  S |k_1, \ldots, k_N \rangle =
  \frac{1}{\sqrt{N!N_1! \ldots N_M!}}
  \sum_{p \in S_N} |k_{p(1)}, \ldots, k_{p(N)} \rangle
\end{equation*}
which satisfy $\nu=1$.
The symmetrization operator  $S$ acts on the tensor-product slots, not on the physical particles themselves, where it rearranges the positions of the one-particle states in the tensor product
\begin{equation*}
  |k_1, k_2, \ldots, k_N\rangle \rightarrow |k_{p(1)}, k_{p(2)}, \ldots, k_{p(N)}\rangle
\end{equation*}

The is run over $p$ all permutations $p$ of the set $\mathcal{N}=\left\{ 1,\dots,N \right\} $, which there are $N!$ element, hence the $1/\sqrt{N!}$ normalization constant.

Now suppose that $N_l$ particle occupy $k_l$ state.
Many permutations now produce identical terms, since swapping two particles that are both in $k_l$  does not change the vector, hence $1/\sqrt{N_l!}$ normalization constant.

Each term is the original tensor-product state with tensor slots rearranged according to $p$, such that $\ket{\dots k_{p(n)}\dots}$ is placed in slot $n$.
For example, with $p(n)=n+1$, the state $S\ket{k_1}$ gets mapped into
\begin{equation*}
  \ket{k_{{(1)}}\dots} \mapsto \ket{\dots \ket{k_2}\dots}
\end{equation*}

\subsubsection{Fermion.}
With the same state $|k_1, \ldots, k_N\rangle $, the antisymmetrization is defined as
\begin{equation*}
  A|k_1,k_2,\ldots,k_N\rangle = \frac{1}{\sqrt{N!}} \sum_{p \in S_N} \mathrm{sgn}(P) |k_{i_1},k_{i_2},\ldots,k_{i_N}\rangle
\end{equation*}
As the case with the symmetrization operator, the sum is run over $p$ all permutations $p$ of the set $\left\{ 1,\dots,N \right\} $.
The only difference is in the parity factor
\begin{equation*}
  \mathrm{sgn}(p) =
  \begin{cases}
    +1 & \text{ Even permutations} \\
    -1 & \text{ Odd permutations}
  \end{cases}
\end{equation*}
This factor express that the state antisymmetry under particle exchange.
Since any permutation $p$ of $N$ slots can be written as a product of transpositions
\begin{equation*}
  p = \mathcal{T}_{i_1j_1} \mathcal{T}_{i_2j_2} \ldots\mathcal{T}_{i_mj_m}.
\end{equation*}
the parity of the permutation is determined by the number of transpositions $m$ in this decomposition: even $m$ for $+1$ and odd $m$ for $-1$.

This parity is the origin of Pauli exclusion principle.
The probability for a many-particle state to contain two or more Fermions in the same single-particle state vanishes.
In another important contribution, Wolfgang Pauli (1940) proved by his famous spin-statistics theorem that Bosons carry integer spin, $s=1,\dots$, while Fermions carry half-integer spin, $s = 1/2, \dots$.

\subsubsection{The application.}
The symmetric and antisymmetrical operator is used to construct boson and fermion subspace from the $n $-particle Hilbert space
\begin{equation*}
  \mathcal{H}^{\otimes n}  =
  \underbrace{\mathcal{H} \otimes \dots \otimes \mathcal{H}}_n =
  \bigotimes_n \mathcal{H}
\end{equation*}
The symmetric subspace is defined as the set of all vectors invariant under permutation of slots
\begin{equation*}
  \mathrm{Sym}^n(\mathcal{H}) = \left\{ |\Psi\rangle \in \mathcal{H}^{\otimes n} \mid P|\Psi\rangle = |\Psi\rangle \text{ for all permutations } P \right\}
\end{equation*}
with $P_p$ as the linear operator representing $\mathcal{H}^{\otimes n}$.
Equivalently,
\begin{equation*}
  \mathrm{Sym}^n(\mathcal{H}) = S\mathcal{H}^{\otimes n}
\end{equation*}
where the symmetrization projector action is
\begin{equation*}
  S = \frac{1}{n!} \sum_{p \in S_n} P_p
\end{equation*}
Note that the normalization constant is $1/n!$ instead of $1/\sqrt{n!}$ to satisfy idempotency $S^2=S$ for subspace projection.
Meanwhile, the antisymmetrical subspace is defined as the set of vectors that change sign under odd permutations
\begin{equation*}
  \wedge^n(H) = \left\{ |\Psi\rangle \in \mathcal{H}^{\otimes n} \;|\; P |\Psi\rangle = \mathrm{sgn}(P) |\Psi\rangle \right\}
\end{equation*}
Equivalently,
\begin{equation*}
  \wedge^n(H) = A \mathcal{H}^{\otimes n}
\end{equation*}
with the action of antisymmetrization as
\begin{equation*}
  A = \frac{1}{n!} \sum_{p \in S_n} \text{sgn}(p) P
\end{equation*}

With these in mind, the Fock subsspace for both boson and fermion can be derived from the full Fock space as
\begin{equation*}
  \mathcal{F}_B = \bigoplus_{n=0}^{\infty} \mathrm{Sym}^n(\mathcal{H}) \qquad
  \mathcal{F}_F = \bigoplus_{n=0}^{\infty} \wedge^n(\mathcal{H})
\end{equation*}

\subsection{Identical Particle Wavefunction}
The arbitrary product state $  |k_1, \ldots, k_N\rangle$, which do not in general obey symmetrization nor antisymmetrization condition, can be projected into boson or fermion subspace using symmetrization and antisymmetrization operator
\begin{gather*}
  S |k_1, \ldots, k_N \rangle =
  \frac{1}{\sqrt{N!N_1! N_1! \ldots N_M!}}
  \sum_{p \in S_N} |k_{p(1)}, \ldots, k_{p(N)} \rangle  \\
  A|k_1,k_2,\ldots,k_N\rangle = \frac{1}{\sqrt{N!}} \sum_{p \in S_N} \mathrm{sgn}(P) |k_{i_1},k_{i_2},\ldots,k_{i_N}\rangle
\end{gather*}
To determine the wavefunction of boson and fermion, one construct $N \times N$ matrix
\begin{equation*}
  M =
  \begin{bmatrix}
    \phi_1(x_1) & \ldots & \phi_1(x_N) \\
    \vdots      & \ddots & \vdots      \\
    \phi_N(x_1) & \ldots & \phi_N(x_N)
  \end{bmatrix}
\end{equation*}
where $\phi_i $ denote quantum state and $\phi(x_j)$ labels the particle coordinate.

\subsubsection{Boson.}
The wavefunction  in boson subspace is represented as
\begin{equation*}
  \Psi_B(x_1, \ldots, x_N) = \frac{1}{\sqrt{N!N_1! \ldots N_M!}} \;\mathrm{perm}(M)
\end{equation*}
Written explicitly,
\begin{equation*}
  \Psi_B(x_1, \ldots, x_N)
  = \frac{1}{\sqrt{N!\prod_i N_i!}} \sum_{P \in S_N} \prod_{i=1}^N \phi_i(x_{P(i)})
\end{equation*}

In the Bose–Einstein condensate, all $N$ particles occupy the same single–particle ground orbital $\phi_0(x)$, hence permutation produces the same term
\begin{equation*}
  \prod_{j=1}^{N} \phi_0(x_{P(j)}) = \phi_0(x_1)\phi_0(x_2)\ldots\phi_0(x_N)
\end{equation*}
Since there are $N!$ permutations
\begin{equation*}
  \sum_{P\in S_N} \prod_{j=1}^{N} \phi_0(x_{P(j)}) = N! \phi_0(x_1)\phi_0(x_2)\ldots\phi_0(x_N)
\end{equation*}
The normalization factor becomes
\begin{equation*}
  \frac{1}{\sqrt{N!N!}} = \frac{1}{N!}
\end{equation*}
Hence the many-body wavefunction reduces to
\begin{equation*}
  \Psi(x_1,\ldots,x_N) = \phi_0(x_1)\phi_0(x_2)\ldots\phi_0(x_N)
\end{equation*}

\subsubsection{Fermion.}
Rather with permanent, we use determinant, also called Slater determinant
\begin{equation*}
  \Psi_F(x_1, \ldots, x_N) = \frac{1}{\sqrt{N!}} \det(M)
  = \frac{1}{\sqrt{N!}} \begin{bmatrix}
    \phi_1(x_1) & \ldots & \phi_1(x_N) \\
    \vdots      & \ddots & \vdots      \\
    \phi_N(x_1) & \ldots & \phi_N(x_N)
  \end{bmatrix}
\end{equation*}
Expanding the determinant gives
\begin{equation*}
  \Psi_F(x_1, \ldots, x_N) = \frac{1}{\sqrt{N!}} \sum_{P \in S_N} \text{sgn}(P) \prod_{i=1}^N \phi_i(x_{P(i)})
\end{equation*}
The determinant will enforce sign change under particle exchange and vanishing upon particle occupying the same state.

\subsection{Non-interacting Identical Particles}
The quantum Hamiltonian of \( N \) identical non-interacting particles is given by
\begin{equation*}
  \hat{H}_0 = \sum_{i=1}^{N} \hat{h}(x_i)
\end{equation*}
where \( \hat{h}(x) \) is the single-particle Hamiltonian.
Usually the single-particle Hamiltonian is given by
\begin{equation*}
  \hat{h}(x) = -\frac{\hbar^2}{2m} \nabla^2 + U(\mathbf{r})
\end{equation*}
with \( U(\mathbf{r}) \) the external confining potential.
In general the single-particle Hamiltonian \( \hat{h} \) satisfies the eigenvalue equation
\begin{equation*}
  \hat{h}(x) \phi_n(x) = \epsilon_n \phi_n(x)
\end{equation*}
where $\epsilon_n $ are the single-particle eigenenergies and $\phi_n(x)$ the single-particle eigenfunctions.

\subsubsection{Uniform gas of non-interacting fermions.}
The term uniform refers to  the fact that particle density is spatially constant
\begin{equation*}
  n (\mathbf{r }  ) = \frac{N }{V }= \text{const.}
\end{equation*}
such that the system is translationally invariant and is no external potential nor spatial structure.
The term non-interacting gas imply that only kinetic term contribute to the Hamiltonian
\begin{equation*}
  \hat{H}_0 = \sum_{i=1}^{N} \frac{\hbar ^2 \mathbf{k }_i ^{2 }}{2m}
\end{equation*}
This is equivalent to setting the temperature into zero.
The term fermion obviously refers to the fact that we are considering fermion case.
Since the eigenstates of free particle is a plane wave, the eigenstates of fermion is this case include extra spinor $\chi_\sigma$ factor
\begin{equation*}
  \psi(x) = \frac{1}{\sqrt{V}} e^{i \mathbf{k } \cdot \mathbf{r}} \chi_\sigma
\end{equation*}
Without any boundary condition, the spectrum of $\mathbf{k }$ is continuous.
Further consideration include periodic boundary condition, not periodic potential, which quantize the wavevector.
The results of this include the Fermi energy
\begin{equation*}
  \epsilon_F = \frac{\hbar^2 k_F^2}{2m} = \frac{\hbar^2 }{2m} \left( 3\pi^2 \rho \right)^{2/3}
\end{equation*}
which is defined as the energy of maximum occupation state at zero temperature, and energy density
\begin{equation*}
  \mathcal{E} = \frac{E}{V} = \frac{3}{5} \rho \varepsilon_F = \frac{3}{5} \cdot \frac{h^2}{2m} \left( 3\pi^2 \right)^{2/3} \rho^{5/3}
\end{equation*}

\subsubsection{Derivation.}
We start by imposing periodic boundary of cube with side $L$, such that the wavefunction satisfy
\begin{equation*}
  e ^{i \mathbf{k }(\mathbf{r }+\mathbf{L })}
  +e ^{i \mathbf{k }\mathbf{r }}
\end{equation*}
This imply $  e ^{i \mathbf{k } \mathbf{L }}=1$ or
\begin{equation*}
  \mathbf{k }=\frac{2\pi }{L }\mathbf{n}
\end{equation*}
Summing over the integers or summing over the corresponding discrete $\mathbf{k}$-values is equivalent
\begin{equation*}
  \sum_{\mathbf{k }f(\mathbf{k } )} \to
  \sum_{\mathbf{n}}f(\mathbf{k }(\mathbf{n} ))
\end{equation*}
since allowed $k$-state corresponds to a unique integer triple $\mathbf{n}$.
We are still counting over still counting discrete states exactly, each integer corresponds exactly to one allowed $k$.
In other hand, for continuous case
\begin{equation*}
  \int d^3 \mathbf{n }\to
  \frac{V }{(2\pi)^3}\int d^3 \mathbf{k}
\end{equation*}
the same case does not apply.
Here, the factor $V/(2\pi)^3$ denote a volume discrete state occupies in $k$-space  $d^3\mathbf{k}$, and is related by $  \mathbf{k }=2\pi\mathbf{n}/L$.

In the thermodynamic limit $L \rightarrow \infty$, this meant that the number of Fermion can be approximated as
\begin{equation*}
  \sum_{\mathbf{k }} \to
  \frac{V }{(2\pi)^3} \int d^3 \mathbf{k} f(\mathbf{k } )
\end{equation*}
The distribution for arbitrary temperature is given by the Fermi function
\begin{equation*}
  f(\epsilon_\mathbf{k},T)=\frac{1}{\exp\left[(\epsilon_\mathbf{k}-\mu)/k_BT\right]+1}
\end{equation*}
In the zero temperature, this function simplify into step function
\begin{equation*}
  f(\epsilon_\mathbf{k},T) \equiv\Theta(\epsilon_F-\epsilon_\mathbf{k}) =
  \begin{cases}
    1 & \epsilon_k<\mu=\epsilon_F \\
    0 & \mu<\epsilon_k
  \end{cases}
\end{equation*}
or in terms of wavevector
\begin{equation*}
  \Theta(k_F-k) =
  \begin{cases}
    1 & k<\epsilon_F \\
    0 & \epsilon_F<k
  \end{cases}
\end{equation*}
which is obtained by dividing both argument by $\hbar ^2/2m$.

With this in mind, the total number of fermion can now be evaluated as
\begin{equation*}
  N = \sum_{\sigma} \frac{V }{(2\pi)^3 } \int d^3\mathbf{k} \; \Theta \left( \epsilon_F - \frac{\hbar ^2 \mathbf{k}^2 }{2m} \right)
\end{equation*}
This best be evaluated in spherical coordinate
\begin{align*}
  N & =   \frac{2V }{(2\pi)^3 }     \int_{0}^{2\pi} \int_{0}^{ \pi} \int_{0}^{\infty}dk\;d\Omega \;\Theta \left( k_F-k \right)   k^2 \sin \theta        \\
  N & =  \frac{2 V}{(2\pi)^{3}} \int_{0}^{k_{F}}dk\;  4\pi k^{2} = \frac{2 V}{(2\pi)^{3}} \cdot \frac{4\pi}{3} k_{F}^{3} = \frac{V}{3\pi^{2}} k_{F}^{3} \\
\end{align*}
Alternatively, without using $k_F$ and solving in terms of Fermi energy
\begin{equation*}
  N =  c \int\displaylimits_{0}^{\sqrt{2m\epsilon_F}/\hbar }dk\;  k^{2} = \frac{2 V}{(2\pi)^{3}} \frac{4\pi}{3} \left( \frac{\sqrt{2m\epsilon_F} }{\hbar } \right) ^{3} =  \frac{V}{3\pi^{2}} \left( \frac{2m\epsilon_F }{\hbar^2 } \right)^{3/2}
\end{equation*}
This ultimately yields
\begin{equation*}
  \epsilon_F = \frac{\hbar ^2 k_F^2}{ 2m} = \frac{\hbar ^2 }{2m }\left( 3\pi^2 \frac{N }{V } \right)^{1/3}
\end{equation*}
As a uniform gas, the density is constant
\begin{equation*}
  \rho = \frac{1}{3\pi^{2}} k_{F}^{3} = \frac{1}{3\pi^{2}} \left( \frac{2m\epsilon_F }{\hbar ^2 } \right) ^{3/2}
\end{equation*}

The total energy could be evaluated in the same method
\begin{align*}
  E & =  \sum_{\sigma,\mathbf{k }}  \epsilon_{\mathbf{k}} \Theta \left(k_F-k\right)
  =\sum_{\sigma} \frac{V}{(2\pi)^3} \int d^3 \mathbf{k}\; \frac{\hbar^{2}k^{2}}{2m} \Theta \left( \epsilon_{F} - \frac{\hbar^{2}k^{2}}{2m} \right) \\
    & =  \frac{4\pi V \hbar ^2}{(2\pi)^{3}m} \int_{0}^{k_{F}}dk\;  k^{4}
  = \frac{V \hbar ^2}{10\pi^{2}m} k_{F}^{5}
  = \frac{V \hbar ^2}{10\pi^{2}m} \left( 3\pi^2 \rho\right) \frac{2m\epsilon_F }{\hbar ^2}                                                         \\
  E & = \frac{3 }{5 }V \rho \epsilon_F = \frac{3 }{5 }\frac{\hbar ^2 }{2m }V(3\pi^2  )^{2/3}\rho^{5/3}
\end{align*}
On dividing by $V$ we obtain the energy density.

\subsection{Many-electron Atom}
The quantum Hamiltonian of $N$ identical interacting particles is given by
\begin{equation*}
  \hat{H} = \sum_{i=1}^{N} \hat{h}(x_i) + \frac{1}{2} \sum_{\substack{i,j=1 \\ i \neq j}}^{N} V(x_i, x_j) = \hat{H}_0 + \hat{H}_1
\end{equation*}
where $\hat{h}$ is the single-particle Hamiltonian and $V(x_i, x_j)$ is the inter-particle potential of the mutual interaction.
In the case of non-relativistic quantum mechanics of $N$ electrons bound to a nucleus of charge $+Ze$, the Hamiltonian reads
\begin{equation*}
  \hat{H} = \sum_{i=1}^{N} \left( -\frac{\hbar^2}{2m} \nabla_i^2 - \frac{Ze^2}{4\pi \epsilon_0 r_i} \right) + \sum_{i<j} \frac{e^2}{4\pi\epsilon_0 |\mathbf{r}_i - \mathbf{r}_j|}
\end{equation*}
The single particle Hamiltonian consist of the kinetic energy of electron $i$ and Coulomb attraction between that electron and the nucleus.
The inter-particle Hamiltonian represents the Coulomb repulsion between pairs of electrons.
It uses summation range $i<j$ so that each pair is counted once, which is equivalent to the factor $1/2$ in the more symmetric form.
\begin{equation*}
  \hat{H}_1=\frac{1}{2} \sum_{\substack{i,j=1 \\ i \neq j}}^{N} V(x_i, x_j)
\end{equation*}
The key difficulty of the many-electron problem arises from the second term, because it couples the coordinates of all electrons and prevents the Schrödinger equation from separating into independent single-particle equations.

\subsubsection{Non-interacting Hamiltonian.}
Suppose assumption that each electron moves independently in the electrostatic field of the nucleus, and that electrons do not repel one another.
This crude assumption of non-interacting electrons is equivalent to ignoring the inter-particle Hamiltonian
\begin{equation*}
  \hat{H} = \hat{H}_0 = \sum_{i=1}^{N} \hat{h}(x_i)
\end{equation*}

Despite that, the model predicts correctly the following results.
\begin{enumerate}
  \item \textbf{Electrons occupy discrete orbitals.} The wavefunction satisfy
        \begin{equation*}
          \hat{h}(\mathbf{r }) \phi_{nlm_lm_s}(\mathbf{r},\sigma) = \epsilon_{n}(Z) \phi_{nlm_lm_{s}}(\mathbf{r},\sigma)
        \end{equation*}
        where the wavefunction factorizes into
        \begin{equation*}
          \phi_{nlm_lm_{s}}(\mathbf{r},\sigma) = R_{nl}(\mathbf{r}) Y_{l}^{m_l}(\theta, \phi)\chi_{\sigma}
        \end{equation*}
        The spatial part consist of radial
        \begin{multline*}
          R_{nl }^{(Z)}(\mathbf{r}) = \sqrt{ \left( \frac{2Z}{na_0} \right)^{3} \frac{(n - l  - 1)!}{2n[(n + l )!]} } e^{-Zr/(na_0)} \\ \times\left( \frac{2Zr}{na_0} \right)^{l } L_{n}^{2l  + 1 - n - l  - 1} \left( \frac{2Zr}{na_0} \right)
        \end{multline*}
        and angular wavefunction
        \begin{equation*}
          Y_{l }^{m}(\theta, \phi) = (-1)^{m} \sqrt{\frac{(2l  + 1)(l  - m)!}{4\pi(l  + m)!}} P_{l }^{m}(\cos \theta) e^{im\phi}
        \end{equation*}
        The spin part of the wavefunction belongs to a two–dimensional Hilbert space describing a spin-$1/2$ particle, with $\sigma=(+1/2,-1/2)$.
        These stationary eigenfunctions are what are called atomic orbitals, defined by quadruple of quantum numbers
        \begin{equation*}
          n = 1,\ldots \quad l = 0, \ldots, n - 1, \quad m_{l } = -l , \ldots, l , \quad m_{s} = \pm \frac{1}{2}
        \end{equation*}
        An electron bound to the nucleus can only exist in one of these allowed eigenstates rather than in an arbitrary spatial distribution.

  \item \textbf{Orbitals group into shells.} Solving the eigenvalue problem gives the eigenenergies
        \begin{equation*}
          \epsilon_n = - 13.6\frac{Z^2}{n^2}  \; \text{eV}
        \end{equation*}
        which independent of $(l, \; m_l,  m_s)$.
        The number of spatial orbitals for a fixed $\ell$ is $2l+1$, so the degeneracy in $n$ is
        \begin{equation*}
          g_l =\sum_{\ell=0}^{n-1} (2\ell + 1)
          = 2 \sum_{\ell=0}^{n-1} \ell + \sum_{\ell=0}^{n-1} 1
          = 2 \frac{n(n-1)}{2} + n = n^2.
        \end{equation*}
        Each spatial orbital can be combined with two spin states
        \begin{equation*}
          g_n = 2g_s=2n^2
        \end{equation*}

        Hamiltonian possesses degenerate eigenstates labeled by the same principal quantum number $n$ and that these degenerate orbitals form a shell.
        The experimental data suggest that the true number of electrons in each experimental shell are $(2, 8, 8, 18, 18, 32, \ldots)$ instead of the predicted $(2,8,18,32,\ldots)$.
        This reflects subshell energy splitting caused by electron–electron interaction which is ignored in this consideration.

  \item \textbf{Chemical properties repeat periodically with atomic number.}
        Each atom with $Z$ electrons fills the available spin–orbitals in order of increasing energy (subject to the Pauli exclusion principle).
        Because the orbitals $2n^2 $, adding electrons sequentially produces a repeating pattern of:   filled shell, such as noble gasses, which produce stable, low-energy configurations; and partial filled shell, such as alkali metal, which produce more chemically reactive configurations.
\end{enumerate}

\subsection{Variational Principle}
For any normalized many-body state $|\Psi\rangle$, not necessarily an eigenstate, which belongs to the Hilbert space on which acts the Hamiltonian $\hat{H}$, one finds
\begin{equation*}
  \langle \Psi | \hat{H} | \Psi \rangle \geq E_{gs}
\end{equation*}
where $E_{gs}$ is the ground-state energy of the system and the equality holds only if $|\Psi\rangle = |\Psi_{gs}\rangle$ with $|\Psi_{gs}\rangle$ ground-state of the system, such that
\begin{equation*}
  \hat{H} |\Psi_{gs}\rangle = E_{gs} |\Psi_{gs}\rangle
\end{equation*}

\subsubsection{Derivation.}
The many-body Hamiltonian $\hat{H}$ satisfies the exact eigenvalue problem
\begin{equation*}
  \hat{H}|\Psi_\alpha\rangle = E_\alpha |\Psi_\alpha\rangle
\end{equation*}
where $E_\alpha$ are the ordered eigenvalues, such that $E_0 < E_1 < \ldots$; and $|\Psi_\alpha\rangle$ the corresponding orthonormalized eigenstates, such that $\langle \Psi_\alpha|\Psi_\beta \rangle = \delta_{\alpha,\beta}$.
The generic many-body state $|\Psi\rangle$ can be written as
\begin{equation*}
  |\Psi\rangle = \sum_{\alpha} c_\alpha |\Psi_\alpha\rangle
\end{equation*}
where $c_\alpha$ are the complex coefficients of the expansion such that the normalization condition is satisfied.
Then one finds
\begin{align*}
  \langle \Psi | \hat{H} | \Psi \rangle
   & =  \sum_{\alpha,\beta} c_\alpha^* c_\beta E_\beta \langle \Psi_\alpha | \Psi_\beta \rangle = \sum_{\alpha} |c_\alpha|^2 E_\alpha \\
   & \geq \sum_{\alpha} |c_\alpha|^2 E_0                                                                                              \\
  \langle \Psi | \hat{H} | \Psi \rangle
   & \geq E_0
\end{align*}

\subsection{Hartree for Bosons}
Hartree method assumes the total wavefunction is a simple product of single-particle orbitals
\begin{equation*}
  \Psi(\mathbf{r}_1, \ldots, \mathbf{r}_N) = \prod_{i=1}^{N} \phi(\mathbf{r}_i)
\end{equation*}
where the single-particle wavefunction $\phi(x)$ is unknown.
In the variational spirit of the Hartree approach the unknown wavefunction $\phi(x)$ is determined by minimizing the expectation value of the total Hamiltonian, given by
\begin{equation*}
  \langle \Psi | \hat{H} | \Psi \rangle = \int dx_1 dx_2 \ldots dx_N \Psi^*(x_1, x_2, \ldots, x_N) \hat{H} \Psi(x_1, x_2, \ldots, x_N)
\end{equation*}
with respect to $\phi(x)$.
In fact, by using $\hat{H }=\hat{H}_0+\hat{H }_I$ one finds the single-orbital Hartree functional for bosons
\begin{multline*}
  \langle \Psi | \hat{H} | \Psi \rangle = N \int dx \; \phi^*(x) \hat{h}(x) \phi(x) \\
  + \frac{1}{2} N(N - 1) \int dx \; dx' |\phi(x)|^2 V(x, x') |\phi(x')|^2
\end{multline*}

This functional is to be minimized with the normalization constraint to obtain the Hartree equation
\begin{equation*}
  \left[   \hat{h }(x  )+   U_\text{mf }\right] \phi(x)    = \epsilon\phi(x)
\end{equation*}
where $U_\text{mf}$ is the mean-field potential
\begin{equation*}
  U_\text{mf}=
  (N-1)\int dx' \;V(x,x') |\phi(x')|^2
\end{equation*}

The algorithm of this method are as follows.
\begin{enumerate}
  \item \textbf{Initial guess.} Following the variational principle, choose initial guess for normalized orbital $\phi ^{(0)}(x)$.
  \item \textbf{Construct the mean-field.} Using previous orbital, construct the following potential
        \begin{equation*}
          U_\text{mf} ^{(n)}=
          (N-1)\int dx' \;V(x,x') |\phi(x') ^{(n)}|^2
        \end{equation*}
  \item \textbf{Solve Hartree equation.} Solve the Hartree equation to obtain next iteration of orbital $\phi ^{(1)}(x)$
        \begin{equation*}
          \left[   \hat{h }(x  )+   U_\text{mf } ^{(n)}\right] \phi(x)^{(n+1)}    = \epsilon ^{(n+1)}\phi(x)  ^{(n+1)}
        \end{equation*}
  \item \textbf{Repeat.} Use the new orbital to recompute the density and the potential, then repeat until the change between successive orbitals becomes negligible $\phi ^{(n+1)}(x)\approx \phi((n))(x)$.
\end{enumerate}

\subsubsection{Derivation: single-orbital Hartree functional for bosons.}
The expectation value of non-interacting Hamiltonian $\hat{H}_0$ is
\begin{equation*}
  \langle \Psi | \hat{H}_0 | \Psi \rangle =\sum_{i=1}^{N}  \int dx_1 \ldots dx_N \; \Psi^*(x_1, \ldots, x_N) \hat{h}(x_i) \Psi(x_1, \ldots, x_N)
\end{equation*}
For fixed $i$, we write
\begin{equation*}
  \Psi^*\hat{h}(x_i) \prod_{j=1}^{N} \phi(x_j) = \Psi^*\left[ \phi(x_1) \ldots \hat{h}(x_i) \ldots \phi(x_N) \right]
\end{equation*}
since $\hat{h}(x_i)$ acts only on the $i$-th factor $\phi(x_i)$ and leaves all others unchanged.
For a fixed $i$, the integral over all coordinates also factorizes
\begin{multline*}
  \int dx_1 \ldots dx_N \prod_{j=1}^{N} \phi^*(x_j) \phi(x_1) \ldots \hat{h }(x_i) \phi(x_i)\ldots\phi(x_N) \\
  = \int dx_i \phi^*(x_i) \hat{h}(x_i) \phi(x_i) \prod_{j \neq i} \int dx_j |\phi(x_j)|^2\\
  = \int dx_i \phi^*(x_i) \hat{h}(x_i) \phi(x_i)
\end{multline*}
and each $i$ term contribute exactly that.
Since there are $N$  terms
\begin{equation*}
  \langle \Psi | \hat{H}_0 | \Psi \rangle
  = N \int dx_i \phi^*(x) \hat{h}(x) \phi(x)
\end{equation*}

The expectation value of interacting Hamiltonian $\hat{H}_I$ is
\begin{equation*}
  \langle \Psi | \hat{H}_I | \Psi \rangle = \frac{1 }{2}\sum_{i \neq j}  \int dx_1 \cdots dx_N  \Psi ^*(x_1, \ldots, x_N) V(x_i, x_j)  \Psi(x_1, \ldots, x_N)
\end{equation*}
For a pair \( (i, j) \), we write
\begin{equation*}
  \prod_{k=1}^{N} \phi^{*}(x_k) V(x_i, x_j) \prod_{l=1}^{N} \phi(x_l)
  =
  \prod_{k=1}^{N} |\phi(x_k)|^2 V(x_i, x_j)
\end{equation*}
For this term, the integral factorizes into
\begin{multline*}
  \int dx_1 \cdots dx_N |\prod_{k=1}^{N} \phi(x_k)|^2 V(x_i, x_j) \\
  = \int dx_i dx_j |\phi(x_i)|^2 V(x_i, x_j) |\phi(x_j)|^2 \prod_{k \neq i,j} \int dx_k |\phi(x_k)|^2\\
  = \int dx dx' |\phi(x)|^2 V(x,x') |\phi(x')|^2
\end{multline*}
and each $i$ term contribute exactly that.
To count how many terms we have, consider $N \times N$ matrix.
The summation range of $i \neq j$ exclude the diagonal elements, hence all that remains are the off-diagonal elements, giving us $N(N-1)$ elements.
Hence
\begin{equation*}
  \langle \Psi | \hat{H}_I | \Psi \rangle
  =\frac{1}{2}N(N-1 ) \int dx dx' |\phi(x)|^2 V(x,x') |\phi(x')|^2
\end{equation*}

\subsubsection{Derivation: minimizing single-orbital Hartree functional.}
We normalized the single-orbital Hartree functional with respect to normalization constraint
\begin{equation*}
  \int dx \; |\phi(x)|^2 = 1
\end{equation*}
For the non-interacting Hamiltonian, we construct functional
\begin{equation*}
  \mathcal{L}_1+\mathcal{L}_c = N \int dx\; \phi ^*(x)\hat{h }(x)\phi(x) + \lambda \left( \int dx \left| \phi (x)\right|^2 - 1 \right)
\end{equation*}
Minimizing with respect to $\phi ^*$ yields
\begin{equation*}
  \delta{\mathcal{L}_1}+\delta \mathcal{L}_c 
  = N \int dx \; \delta \phi^{*} (x)\hat{h}(x) \phi(x) + \lambda \int  d x \; \delta\phi^{*} \phi(x)
\end{equation*}
For the case of interacting Hamiltonian, the functional reads
\begin{equation*}
  \mathcal{L}_2 = \frac{1}{2} N (N - 1) \int d{x} \; dx' \; |\phi(x)|^2 V(x,x') |\phi(x')|^2 
\end{equation*}
Again, we vary $\phi ^*$ 
\begin{multline*}
  \delta \mathcal{L}_2 = \frac{1}{2} N(N-1) \bigg[ \int dx\;dx' \; \delta \phi ^*(x)  \phi(x)V(x,x') |\phi(x')|^2 \\+ \int dx\;dx' \; |\phi(x)|^2  V(x,x')  \delta\phi ^*(x ) \phi(x)\bigg]\\
  = N (N-1)\int dx\;dx' \; \delta \phi ^*(x)  \phi(x)V(x,x') |\phi(x')|^2
\end{multline*}
where both integral contribute the same value.
Combining both
\begin{multline*}
  \delta F 
  = N \int dx \; \delta \phi^{*} (x)\hat{h}(x) \phi(x) \\
  +  N (N-1)\int dx\;dx' \; \delta \phi ^*(x)  \phi(x)V(x,x') |\phi(x')|^2 \\
  +\lambda \int  d x \; \delta\phi^{*} \phi(x)
\end{multline*}

For arbitrary variational $\delta\phi ^*$, in order to make sure that the integral is zero, the other integrand factor must be zero, thus
\begin{align*}
  \left(   N \hat{h }(x  )+   N (N-1)\int dx' \;V(x,x') |\phi(x')|^2 \right) \phi(x)
  +\lambda\phi(x)                                                                & = 0               \\
  \left(   \hat{h }(x  )+   (N-1)\int dx' \;V(x,x') |\phi(x')|^2 \right) \phi(x) & = \epsilon\phi(x)
\end{align*}
where the second term is the mean-field potential.

\subsection{Hartree-Fock for Fermion}
Rather than simple product, the Hartree-Fock method assumes the wavefunction using Slater determinant
\begin{equation*}
  \Psi_F(x_1, \ldots, x_N) 
  = \frac{1}{\sqrt{N!}} \sum_{P \in S_N} \text{sgn}(P) \prod_{i=1}^N \phi_i(x_{P(i)})
\end{equation*}
or the second quantization representation
\begin{equation*}
  \ket{\Phi }= \prod_{i \in \text{occ}} c ^\dagger_i \ket{0}
\end{equation*}
with $i$ as the occupied state.
The expectation value of the total Hamiltonian
\begin{equation*}
  \langle \Psi | \hat{H} | \Psi \rangle = \int dx_1 dx_2 \ldots dx_N \Psi^*(x_1, x_2, \ldots, x_N) \hat{H} \Psi(x_1, x_2, \ldots, x_N)
\end{equation*}
using the fermion wavefunction yields the Hartree-Fock functional
\begin{multline*}
      \langle \Psi | \hat{H} | \Psi \rangle 
  = \sum_{i=1}^N \int dx\phi_i^*(x)\hat h(x)\phi_i(x) \\
  + \frac{1}{2}\sum_{\substack{i,j=1\\i\neq j}}^N \int dx\;dx' \Bigg[ |\phi_i(x)|^2V(x,x')|\phi_j(x')|^2 \\
  - \phi_i^*(x)\phi_j(x)V(x,x')\phi_j^*(x')\phi_i(x') \Bigg]
\end{multline*}
In abstract basis, this expression reads
\begin{equation*}
      \langle \Psi | \hat{H} | \Psi \rangle 
  = \sum_{i=1}^{N}\langle i|\hat{h}|i\rangle + \frac{1}{2}\sum_{i,j=1}^{N}\big(\langle ij|\hat{V}|ij\rangle - \langle ij|\hat{V}|ji\rangle\big)
\end{equation*}

Enforcing the normalization constraint yields the Hartree-Fock equation
\begin{equation*}
  \left[\hat{h}(x)+\hat{V}_{\mathrm{mf}}(x)\right]\phi_i(x) =\epsilon_i\phi_i(x)
\end{equation*}
where $\epsilon_i$ are the Lagrange multipliers ﬁxed by the normalization and $\hat{V}_\text{mf}$ is a nonlocal mean-ﬁeld operator
\begin{equation*}
  \hat{V}_\text{mf}(x) \phi_i(x)
  =  V_d(x) \phi_i(x) - \sum_{j=1}^N V^{ji}_\text{ex}(x) \phi_j(x)
\end{equation*}
where the direct mean-ﬁeld ${V}_d(x)$ and exchange mean-field ${V}_\text{ex} ^{ji}(x)$ read as 
\begin{align*}
  V_\text{d}(x) & =  \sum_{j\neq i}^N \int dx'\; V(x,x')\left|\phi_j(x')\right|^2\\\
  V_\text{ex}^{ji}(x) & =  \int dx'\; \phi_j^*(x')V(x,x')\phi_i(x')
\end{align*}

\subsubsection{Derivation: Hartree-Fock.}
The following derivation shall use the second quantization formalism.
The expectation value of single particle in this formalism is written as 
\begin{equation*}
  \braket{\Phi  | \hat{H}_1|\Phi} = \sum_{j}   \langle i|\hat{h}|j\rangle \braket{\Phi  | c_i^\dagger c_j|\Phi}
\end{equation*}
with the fermion wavefunction written as
\begin{equation*}
  \ket{\Phi }= \prod_{k \in \text{occ}} c ^\dagger_k \ket{0}
\end{equation*}
and $k$ as the occupied state.
We can evaluate the expectation value of fermion creation and annihilation operator on the fermion wavefunction as
\begin{equation*}
  \bra{\Phi} c ^\dagger_i  c_j \prod_{k \in \text{occ}} c ^\dagger_k \ket{0} = \delta_{ij}n_i 
\end{equation*}
with $n_i\in \left\{ 0,1 \right\} $ as the number occupation of state $i$.
The interpretation of this result is as follows.
If $j \neq \text{occ}$, then the annihilation $c_i$ act on vaccum
\begin{equation*}
  c_j \ket{\Phi} =0
\end{equation*}
If $j \in \text{occ}$, the result generally not zero
\begin{equation*}
  c_j \ket{\Phi} = (\pm) \ket{\Phi^{(j)}}
\end{equation*}
There are two further possible subcase after this.
If $i \neq j$, then creation $c ^\dagger_i$ creates particle in already occupied state, 
\begin{equation*}
  c ^\dagger_i \ket{\Phi^{(j)}} = 0
\end{equation*}
or it creates particle in different orbital $\ket{\Phi^{(j \to i)}}$ such that the resulting state is orthogonal with $\bra{\Phi}$
\begin{equation*}
  \braket{\Phi  | \Phi^{(j \to i)}} = 0
\end{equation*}
The result is zero overall.
Second possibilities are that $i =j$, which meant that creation $c_i$ re-create the particle that the annihilation $c_j$ annihilate, thus the state is again identical to $\ket{\Phi}$.
Hence, the expectation value reads 
\begin{equation*}
  \braket{\Phi  | \hat{H}_1|\Phi} 
  = \sum_{i \in \text{occ}}   \langle i|\hat{h}|i\rangle   
\end{equation*}
To obtain the desired form, we insert the completeness relation 
\begin{equation*}
   \braket{\Phi  | \hat{H}_1|\Phi} 
  = \sum_{p \in \text{occ}}    \int dx\;dx'\;\phi^*(x)\langle x | \hat{h} | x' \rangle\phi(x')
\end{equation*}
The Hamiltonian is local, so $\langle x | \hat{h} | x' \rangle = \hat{h}(x)\delta(x-x')$ and the integral turns 
\begin{equation*}
   \braket{\Phi  | \hat{H}_1|\Phi} 
  = \sum_{i=1}^N \int dx\phi_i^*(x)\hat h(x)\phi_i(x) 
\end{equation*}
where we relabel the orbital such that $\left\{ i,\dots,N \right\} $ is the occupied orbital.

Now for the two-particle Hamiltonian
\begin{equation*}
  \braket{\Phi  | \hat{H}_2|\Phi} = \sum_{i,j}\sum_{k,l}   \langle ij|\hat{h}|kl \rangle \braket{\Phi  | c_i^\dagger c ^\dagger_j c_l c_k|\Phi}
\end{equation*}
Note the order of the annihilation operators are swapped.
The expectation value of the annihilation and creation term in the Slater determinant is 
% ij kl
% pq rs
\begin{equation*}
  \braket{\Phi  | c ^\dagger_i c ^\dagger_j c _l c_k|\Phi }=\delta_{ik }\delta_{jl } -\delta_{il }\delta_{jk }
\end{equation*}
This is obtained by considering the fact that the annihilation operators yields non-zero result if they act on occupied state
\begin{equation*}
  c_l c_k \ket{\Phi} \neq 0,
  \qquad k,l \in \text{occ}
\end{equation*}
As before, in order to produce non-zero inner product, the creation operators must re-create the annihilated fermion.
There are two possible way to achieve this.
First is the direct reconstruction $i=k$ and $j=l$, where the operators re-create the fermion in the same order they were annihilated
\begin{equation*}
 c_i^\dagger c ^\dagger_j c_l c_k \ket{\Phi} 
 \to c_i^\dagger c ^\dagger_j c_j c_i \ket{\Phi} 
 =c_i^\dagger (1-c_jc ^\dagger_j ) c_i \ket{\Phi} 
 = c ^\dagger_i c_i \ket{\Phi}
\end{equation*}
since $c ^\dagger_j$ acts on occupied state $q$.
Second is the exchange reconstruction $i=l$ and $j=k$, where their order are swapped
\begin{equation*}
 c_i^\dagger c ^\dagger_j c_l c_k \ket{\Phi} 
 \to c_i^\dagger c ^\dagger_j c_i c_j \ket{\Phi} 
 = -c_i^\dagger c_i c ^\dagger_j c_j  \ket{\Phi} 
\end{equation*}
Enforcing this result, the expectation value reads 
\begin{equation*}
  \braket{\Phi  | \hat{H}_2|\Phi} = 
  \frac{1 }{2}\sum_{p,q\in \text{occ}}   \langle ij|\hat{V}|ij \rangle -\langle ij|\hat{V}|ji \rangle 
\end{equation*}

Again, we insert the completeness relation to express it in position representation.
For the direct term 
\begin{multline*}
   \langle ij|\hat{V}|ij \rangle  \\
= \int dx_1\;dx_2\;dx_1'\;dx_2'\; \phi_i^*(x_1)\phi_j^*(x_2)\langle x_1 x_2|\hat{V}|x_1' x_2'\rangle \phi_i(x_1')\phi_j(x_2')
\end{multline*}
The operators also local $\langle x_1 x_2|\hat{V} |x_1' x_2'\rangle = V(x_1,x_2)\delta(x_1-x_1')\delta(x_2-x_2')$
\begin{equation*}
 \langle ij|\hat{V}|ij \rangle  
= \int dx_1\;dx_2\; \phi_i^*(x_1)\phi_j^*(x_2) V(x_1,x_2) \phi_i(x_1)\phi_j(x_2)
\end{equation*}
As for the exchange term 
\begin{multline*}
   \langle ij|\hat{V}|ji \rangle  \\
= \int dx_1\;dx_2\;dx_1'\;dx_2'\; \phi_i^*(x_1)\phi_j^*(x_2)\langle x_1 x_2|\hat{V}|x_1' x_2'\rangle \phi_j(x_1')\phi_i(x_2')
\end{multline*}
and with locality
\begin{equation*}
 \langle ij|\hat{V}|ji \rangle  
= \int dx_1\;dx_2\; \phi_i^*(x_1)\phi_j^*(x_2) V(x_1,x_2) \phi_j(x_1)\phi_i(x_2)
\end{equation*}

\subsubsection{Derivation: Hartree-Fock state functional minimization.}
With the orbital orthonormality, we construc the functional
\begin{equation*}
  \mathcal{L}
  = \sum_{i=1}^{N}\langle i|\hat{h}|i\rangle
+ \frac{1}{2}\sum_{i,j=1}^{N}\big(\langle ij|\hat{V}|ij\rangle-\langle ij|\hat{V}|ji\rangle\big)
+ \sum_{i,j=1}^{N}\epsilon_{ij}\big(\langle i| j\rangle-\delta_{ij}\big)
\end{equation*}
For one-particle and the constraint term, we vary $\ket{i}$ 
\begin{equation*}
  \delta \mathcal{L }_1+\mathcal{L }_c
  = \sum_{i=1}^{N}\langle\delta i|\hat{h}|i\rangle + \sum_{i,j=1}^{N}\epsilon_{ij}\langle \delta i| j\rangle
\end{equation*} 
Same goes for the two-particle term, only we vary for the set of $\left\{ \ket{i} \right\} $
\begin{align*}
  \mathcal{L }_2
  & =  \frac{1}{2}\sum_{i,j=1}^{N}\big(\langle\delta i,j|\hat{V}|ij\rangle +\langle i,\delta j|\hat{V}| i, j\rangle-\langle\delta i,j|\hat{V}|ji\rangle - \langle i, \delta j|\hat{V}|ji\rangle\big)\\
  \mathcal{L }_2
  & = \sum_{i,j=1}^{N}\big(\langle\delta i,j|\hat{V}|ij\rangle -\langle\delta i,j|\hat{V}|ji\rangle \big)
\end{align*}
Combining both 
\begin{equation*}
  \delta\mathcal{L }
  = \sum_{i=1}^{N}\langle\delta i|\hat{h}|i\rangle + \sum_{i,j=1}^{N}\big(\langle \delta i,j|\hat{V}|ij\rangle -\langle\delta i,j|\hat{V}|ji\rangle \big)+ \sum_{i,j=1}^{N}\epsilon_{ij}\langle \delta i| j\rangle  
\end{equation*}

We now want to define operator that express the idea 
\begin{equation*}
  \braket{ij  | \hat{V}|ij} \to \bra{i } \braket{j  | \hat{V}|j }\ket{i}
\end{equation*}
The realization is as the part of $\hat{V}$ that acts on $\ket{i}$ when $j$ is fixed. 
First we project particle $j$ onto $\ket{j}$, then apply $\hat{V}$ to represent the part of that operator $\hat{V}$ which act on $i$.
This still lives on $\mathcal{H}_i \otimes \mathcal{H}_j$, so tracing over $j$ reduce the operator into the $\mathcal{H}_i$ only.
We define this by the direct operator
\begin{equation*}
  \hat{J }_j = \mathrm{Tr}_j[\hat{V}(\mathbf{1 }_i \otimes \ket{j}\bra{j})]
\end{equation*}
With the same logic we can define the exchange operator, only we want to encodes the particle exchange.
Instead of leaving $\ket{i}$ on $i$ unchanged, we want $\ket{i}$ on $i$ and $\ket{j}$ on $j$ in the ket of $\hat{V}$ become $\ket{j}$ on $i$ and $\ket{i}$ on $j$ in the bra.
Order exchange in other words.
With this, we define the exchange operator as 
\begin{equation*}
  \hat{K }_j = \mathrm{Tr}_j[\hat{V}(\ket{j} \bra{i} \otimes \ket{i}\bra{j})]  
\end{equation*}
With this in mind, we can write
\begin{equation*}
  \delta\mathcal{L }
  = \sum_{i=1}^{N}\langle\delta i|\hat{h}|i\rangle 
  + \sum_{i,j=1}^{N} \langle \delta i| (\hat{J}_j-\hat{K }_j)|i\rangle 
  + \sum_{i,j=1}^{N}\epsilon_{ij}\langle \delta i| j\rangle  
\end{equation*}

For arbitrary variation for $\left\{ \bra{\delta i} \right\} $, it is obvious that 
\begin{equation*}
  \hat{h}\lvert i\rangle + \sum_{j=1}^{N}\big(\hat{J}_j - \hat{K}_j\big)\lvert i\rangle - \sum_{j=1}^{N}\epsilon_{ij}\lvert j\rangle =0
\end{equation*}
To simplify even further, we can choose an orthonormal orbital basis that can diagonalize $\epsilon_{ij}$
\begin{equation*}
  \hat{h}\lvert i\rangle + \sum_{j=1}^{N}\big(\hat{J}_j - \hat{K}_j\big)\lvert i\rangle = \epsilon_i \ket{i}
\end{equation*}

Next we evaluate the position representation.
It is trivial for the one-particle and the constraint term, as for the direct term 
\begin{align*}
  \hat{J}_j & =  \operatorname{Tr}_j \big[\hat{V}\big(\mathbf{1}_i\otimes |j\rangle\langle j|\big)\big]
   = \sum_n \left( \mathbf{1 }_i \otimes \bra{n_j} \right) \hat{V}(\mathbf{1 }_i \otimes \ket{j}\bra{j}) \left( \mathbf{1 }_i \otimes \ket{n_j} \right)  \\
  & = \sum_n \left( \mathbf{1 }_i \otimes \bra{n_j} \right) \hat{V}(\mathbf{1 }_i \otimes \ket{j}\braket{j|n_j})  \\
  & = \sum_n \left( \mathbf{1 }_i \otimes \bra{n_j} \right) \hat{V}(\mathbf{1 }_i \otimes \ket{j} )\delta_{j,n_j}  \\
& = \left( \mathbf{1 }_i \otimes \bra{j} \right) \hat{V}(\mathbf{1 }_i \otimes \ket{j} )
\end{align*}
The position representation for the operator is expressed as 
\begin{equation*}
  (\hat{J}_j\phi)(x) = \int dx'\,\langle x|\hat{J}_j|x'\rangle\,\phi(x')
\end{equation*}
All that matter is to compute the kernel then 
\begin{equation*}
  \langle x|\hat{J}_j|x'\rangle 
  = (\langle x|\otimes\langle j|)\hat{V} (|x'\rangle\otimes|j\rangle) 
   =  \int dy\;dy'\;\phi^*(y)\,\langle x,y|\hat{V}|x',y'\rangle\phi(y')
\end{equation*}
Assuming the operator being local
\begin{equation*}
  \langle x|\hat{J}_j|x'\rangle 
  =\delta(x-x')\int dy\,V(x,y)\,\lvert\phi_j(y)\rvert^2.
\end{equation*}
Substituting 
\begin{align*}
    (\hat{J}_j\phi)(x) 
  &= \int dx'\;\delta(x-x')\Bigg[\int dy\;V(x,y)|\phi_j(y)|^2\Bigg]\phi(x)\\
  (\hat{J}_j\phi)(x) 
&= \Bigg[\int dy\;V(x,y)|\phi_j(y)|^2\Bigg]\phi(x)
\end{align*}

As for the exchange term
\begin{align*}
  \hat{K }_j & =  \mathrm{Tr}_j[\hat{V}(\ket{j} \bra{i} \otimes \ket{i}\bra{j})]  
  = \sum_n \left( \mathbf{1 }_i \otimes \bra{n_j} \right) \hat{V } \left( \ket{j }\bra{i }\otimes \ket{i }\bra{j } \right) \left( \mathbf{1 }_i \otimes \ket{n_j} \right)  \\
  \hat{K }_j
  & =  \sum_n \delta_{j,nj}\left( \mathbf{1 }_i \otimes \bra{n_j} \right) \hat{V } \left( \ket{j }\bra{i }\otimes \ket{i }\right)   
  =  \left( \mathbf{1 }_i \otimes \bra{j} \right) \hat{V } \left( \ket{j }\bra{i }\otimes \ket{i }\right)
\end{align*}
By inserting the completeness relation
\begin{equation*}
  \mathbf{1}_i\otimes \mathbf{1}_j = \int dx_i\,dx_j\,\ket{x_i x_j} \bra{x_i x_j} 
\end{equation*}
one obtain the 
\begin{align*}
  \hat{K }_{j} 
  & =   \int dx_i\;dx_j\;dx_i'\;dx_j'\;(\mathbf{1}_i\otimes\langle j|)|x_i x_j\rangle\langle x_i x_j|\hat{ V}|x_i' x_j'\rangle\langle x_i' x_j'|\big(|j\rangle\langle i|\otimes|i\rangle\big)\\
  & =   \int dx_i\;dx_j\;dx_i'\;dx_j'\;\lvert x_i \rangle \otimes \langle j \rvert x_j \rangle \langle x_i x_j|\hat{ V}|x_i' x_j'\rangle \langle x_i'|j\rangle\langle i|\otimes\langle x_j'|i\rangle\\
  & =   \int dx_i\;dx_j\;dx_i'\;dx_j'\;\phi_j ^*(x_j) \ket{x_i}\langle x_i x_j|\hat{ V}|x_i' x_j'\rangle \phi_j(x_i')\phi_i(x_j')\langle i|
\end{align*}
Using locality
\begin{equation*}
  \hat{K }_{j}   
   =   \int dx_i\;dx_j\; \phi_j ^*(x_j) V(x_i,x_j) \phi_j(x_i)\phi_i(x_j)\ket{x_i} \bra{i}
\end{equation*}
From the position representation
\begin{equation*}
  (\hat{K}_j\phi_i)(x_i) = \int dx_i'\;\langle x_i|\hat{K}_j|x_i'\rangle\phi_i(x_i')
\end{equation*}

To avoid confusion, we define 
\begin{equation*}
  \hat{K }_{j}   
   =   \int d\xi_i\;dx_j\; \phi_j ^*(x_j) V(\xi_i,x_j) \phi_j(\xi_i)\phi_i(x_j)\ket{\xi_i} \bra{i}
\end{equation*}
The kernel evaluate as 
\begin{align*}
   \langle x_i|\hat{K}_j|x_i'\rangle 
   & =    \int d\xi_i\;dx_j\; \phi_j ^*(x_j) V(\xi_i,x_j) \phi_j(\xi_i)\phi_i(x_j)\braket{x_i  | \xi_i} \braket{i  | x_i'}\\
   \langle x_i|\hat{K}_j|x_i'\rangle 
   & = \phi_i ^*(x_i')\int dx_j\; \phi_j ^*(x_j) V(x_i,x_j) \phi_j(x_i)\phi_i(x_j) 
\end{align*}
Substituting
\begin{align*}
  (\hat{K}_j\phi_i)(x_i) &= \int dx_i'\, \phi_i^*(x_i')\, \phi_i(x_i') \int dx_j\, \phi_j^*(x_j)\, V(x_i,x_j)\, \phi_j(x_i)\, \phi_i(x_j)\\
  (\hat{K}_j\phi_i)(x_i) &= \int dx_j\, \phi_j^*(x_j)\, V(x_i,x_j)\, \phi_j(x_i)\, \phi_i(x_j)
\end{align*}
\end{document}